\documentclass[12pt,a4paper,openany]{book}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{textcomp}
\usepackage{xifthen}
\usepackage{tabularx}

%Alignment
\usepackage[skip=10mm]{parskip}
\raggedbottom

%Title
\title{Neon Pen and Paper}
\author{Fr0sty \thanks{Special thanks to others}}
\date{\today}

%Custom Environments
\newenvironment{exampleblock}[1][1]
{\hfill\begin{minipage}{\dimexpr\textwidth-#1cm}}
{\end{minipage}\par}

%Custom Commands
\newcommand{\ul}[1]{\underline{\smash{#1}}}
\newcommand{\breakline}{\vspace{.5cm} \hrule width \textwidth \relax}
\newcommand{\specialrule}[2]{
	\begin{minipage}{\textwidth/2}
		\textbf{\ul{#1:}}\\
		#2\\
	\end{minipage}
}
\newcommand{\supply}[5]{
	\begin{minipage}{\textwidth/2}
		\textbf{\ul{#1}} (#2)\\
		Price: #4\\
		Weight: #5\\
		#3\\
	\end{minipage}
}

\newcommand{\statuseffect}[2]{
	\begin{minipage}{\textwidth}
		\textbf{\ul{#1:}}\\
		#2\\
	\end{minipage}
}
\newcommand{\skill}[4][Basic]{
	\begin{minipage}{\textwidth}
		\textbf{\ul{#2}}\\
		Difficulty: #1\\
		Common Characteristic: #3\\
		Description:\\
		#4\\
	\end{minipage}
}
\newcommand{\ability}[4]{
	\begin{minipage}{\textwidth}
		\textbf{\ul{#1}} (#2 XP)\\
		Prerequisites: #3\\
		Effect:\\
		#4\\
	\end{minipage}
}
\newcommand{\maneuver}[3]{
	\begin{minipage}{\textwidth}
		\textbf{\ul{Maneuver: #1}} (#2 XP)\\
		Prerequisites: #3\\
		Effect:\\
		Allows the use of the maneuver #1 at normal penalties.\\
	\end{minipage}
}
\newcommand{\boon}[4][]{
	\begin{minipage}{\textwidth}
		\textbf{\ul{\smash{#2}}} (#4 GP\ifthenelse{\isempty{#1}}{}{ }#1)\\
		#3
	\end{minipage}
	\par
}
\newcommand{\bane}[4]
{\boon[#4]{#1}{#2}{#3}}
\newcommand{\weaponmod}[5]{
	\textbf{\ul{#1}}:\\
	#3; #4; #5\\
	#2
	\par
}
\newcommand{\meleecomponent}[6]{
	\begin{minipage}{\textwidth}
		\textbf{\ul{#1:}}\\
		#2\\
		\textit{Weight}: #4; \textit{Price}: #5\ifthenelse{\isempty{#6}}{}{; \textit{Requirement}: #6}\\
		\textit{Effect}: #3
	\end{minipage}
	\par
}
\newcommand{\ammo}[6]{
	\begin{minipage}{\textwidth}
		\textbf{#1:} #2\\
		\textit{Price: #3; Unit of sale: #4}\\
		\textit{Weight/Bulk: #5 per #6}
	\end{minipage}
	\par
}

\begin{document}
	\maketitle
	\tableofcontents
	
	\chapter{The Foundation}
	\section{Basics}
	This booklet will not provide an introduction into tabletop roleplaying in general. If you have never before played a tabletop roleplaying game, there are many great resources out there. It is however not required to have played a game yourself, much less in a D100 system. All game mechanics will be provided on the following pages.
	\section{Scenario}
	\begin{exampleblock}\textit{
		The year 2113 is coming to an end. After many, many price cuts last year people forgot how to handle their money responsibly, dividing society into \emph{very} different classes. \\
		Money is power, more than ever. The only thing stopping riots and insurgencies against weakened governments are private security providers - be that gangs and desperate people trying to survive or humanoid robots, unstoppable, unbreakable, of unknown origin. \\
		The future really has everything.
	}\end{exampleblock}
	
	\chapter{Dice Checks and Stats}
	\section{Dice}
	This system uses D100 to make its decisions. To achieve a Success you have to reach or undershoot a Target Value, which is composed of a Base Value (usually a characteristic or skill, more on those later) and Situational Modifiers. Example:
	
	\begin{exampleblock}
		\textit{Alice is doing reconnaissance. Trying to spot something far away she is asked to make an Investigation check. Her Investigation of 55 (Perception of 45 + 10 for being trained in Investigation) is modified by -15 for low light and -10 for slightly misty weather. Her target value therefore becomes 35, so rolling 35 or below would have her succeed.}
	\end{exampleblock}

	The required dice will be a D10 and a percentile dice, which essentially is also a D10 with an additional 0 (00, 10, 20 and so on). If a D100 roll is requested, both dice are rolled simultaneously. Both dice are added to each other and that will be the result, so a 4 and a 70 will become 74. The one exception to this is rolling all zeros - this will become 100.
	\section{Degrees of success/failure}
	Success can mean a lot of things. Hitting a target and hitting dead center are both successes but they clearly differ in how successful they are. Enter Degrees of Success (or DoS for short). You gain one degree of success for just general success and every full 10 points there are between the eyes on the dice and the target value gives you one additional degree of success. Depending on how many are achieved, the GM describes the result accordingly.
	Another example:
	
	\begin{exampleblock}\textit{
	Alice tries to throw a can of foam at a fire to put it out. Her ranged base value is 28 and she is well-versed in throwing weapons, giving her +20 and because of the large target size she is granted another +30, making her target value 78.\\
	In the first scenario she rolls a 76, which does result in a success but without any additional degrees of success beyond the first, making this a bare hit. Only the outermost part of the fire is quenched and it continues to spread to the other side but her way might be passable now.\\
	In the second scenario she rolls a 34, making this 5 degrees of success. She hits dead center and the foam spreads over almost the entire flames, essentially having it die out.\\
	In the third scenario she rolls an 87, barely failing but with only a single degree of failure. The can might hit something and return, hit the wrong parts of the fire or fail to pop.\\
	And finally in the fourth scenario she rolls a 99, scoring 3 degrees of failure. The can could slip, pop too early or spread the foam in the wrong direction. Details are up to the GM's discretion.
		}
	\end{exampleblock}
	\section{Opposed checks}
	We went over success, we went over types of success, now the last thing to go over is direct opposition. Rather straightforward the DoS are compared; if they are the same, then the result was so close that the natural skill of the opponents is decisive. Compare the two target values with the higher one getting a very small success over the other. If even these two are the same, usually nothing happens. Three more examples depicting the different situations:
	
	\begin{exampleblock}\textit{
	Alice is stopped from entering a building by Bob, a cautious bouncer. Since she does not want to cause a ruckus that could alert her target inside, she tries to smooth-talk her way through him. To determine the result her game master asks for a Persuasion check, opposed by Bob’s Interrogation check.\\
	Bob, being a naturally perceptive and cautious guy, has 55 Instinct and being trained in Interrogation grants him a further +10 bonus for a target value of 65. Alice is only slightly less naturally charming, having a Charisma of 45, but since she’s also experienced in persuasion granting her a +20, her target value is also 65.\\
	In scenario one Alice rolls a 34, Bob rolls a 42, meaning Alice gains 3 degrees of success and Bob gains 2. Therefore Alice has achieved a very slight victory that might just be enough for her to achieve her desired result.\\
	In scenario two Alice rolls a 26 and Bob rolls a 24. Alice gains 3 degrees of success, Bob gains 4. Therefore Alice suffers slight loss here. Whether she may not enter or she enters but is noticed, is up to the GM’s ruling and narration.\\
	In scenario three Alice rolls a 78 and Bob rolls an 82. Therefore Alice scores a degree of failure, so does Bob. The fact both failed their checks is irrelevant for their opposed checks. Since they both passed equally good or bad, Bob, having the stronger natural inclination, wins the opposition only very slightly. This might just make him more suspicious or completely aware but not hostile, depending on GM narration.\\
		}
	\end{exampleblock}
	\section{Characteristics}
	We now know how to perform dice checks but how do we determine our target values? Most basic to the target value is the character’s Characteristic. These are the most basic features that define a creature. Usually one of these values will be the basis for most dice checks:
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \textbf{Courage (Cr)} describes the creature’s strength of will and the creature’s ability to overcome emotional impulses like the obvious fear but also e.g. anger.
		\item \textbf{Intelligence (Int)} describes the creature’s capability to remember old as well as to understand and learn new things. It also encompasses drawing conclusions from things the creature knows.
		\item \textbf{Instinct (Ins)} describes the creature’s reaction speed in situations that don’t allow for time to think. Also encompasses general perception.
		\item \textbf{Charisma (Ch)} describes the creature’s presence. The more charisma the more self-confident and persuasive the creature appears.
		\item \textbf{Dexterity (Dex)} describes the creature’s finesse with very fine tools such as profane lockpicks or a blowtorch.
		\item \textbf{Agility (Ag)} describes the creature’s body control and flexibility. 
		\item \textbf{Constitution (Con)} describes the creature’s bodily sturdiness, endurance and pain tolerance.
		\item \textbf{Strength (Str)} describes the creature’s bodily, physical strength and ability to use it effectively.
	\end{itemize}
	Each characteristic can be increased 5 times by 5 points each by spending XP. Said advancements cost 200, 400, 800, 1200 and 1600XP respectively. These have to be bought in order for any one given characteristic.
	\section{Characteristic bonuses}
	Sometimes a mechanic will require a characteristic bonus. This is the characteristic divided by 10 and rounded down - a characteristic of 31 would mean a characteristic bonus of 3 while a characteristic of 49 would result in a bonus of 4. A theoretical characteristic of 125 would result in a characteristic bonus of 12.
	\section{Derived values}
	A few additional values are directly derived from the set of characteristics. They include the attributes that define limits for augmentation:
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \textbf{Rayleigh Index \textlangle(Cr+Int+Con)/20\textrangle:} Cybernetic augmentation puts a massive strain on the human body. This number indicates the body’s limit for nerve load. It must never be surpassed or the character is at immediate, high risk of vital organ failure, brain and nerve damage and more.
		\item \textbf{Medical Toughness \textlangle(Ag+Con+Str)/20\textrangle:} This simplified measurement represents all factors that allow or disallow further bio-engineered parts to be accepted by the character’s body. This must also never be surpassed, though the exact consequences are dependent on the body part that is being installed and range from organ activation failure over inhibited circulation up to spontaneous fatal cardiac arrest.
	\end{itemize}
	
	They also encompass combat-related values:
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \textbf{Base Initiative \textlangle(Cr+Ins+Ag)/10\textrangle:} The base value for the character’s initiative. While it can be modified by circumstances and abilities later, only this is what “base initiative” refers to.
		\item \textbf{Base Melee Combat \textlangle(Cr+Ins+Ag+Str)/3\textrangle:} The value representing the character’s basic skill in melee combat, armed or unarmed. This serves as the foundation for proper combat training.
		\item \textbf{Base Ranged Combat \textlangle(Int+Ins+Dex+Str)/3\textrangle:} The value representing the character’s basic skill in ranged combat, be that thrown weapons or firearms. This serves as the foundation for proper combat training.
	\end{itemize}

	Two values are special, in that they are recalculated if temporary modifiers impact the characteristics that make them up:
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \textbf{Injury Threshold \textlangle ConB\textrangle:} The amount of damage the character can take before he is actually injured to the point of pain, bleeding and weakening. All damage taken is reduced by this and it is not ignored by an attack’s armor penetration.
		\item \textbf{Melee Damage Bonus \textlangle(Ag+Str)/10\textrangle:} Not only technique but also raw ability can increase a person’s damage dealt with a vicious slash or crushing blow in melee combat.
	\end{itemize}

	Lastly there are values that are not necessarily restricted solely to combat:
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \textbf{Movement Speed \textlangle((Ag+Ag+Str)/40)+5\textrangle:} A character’s total sprint speed, explained in more detail in the chapter Movement.
		\item \textbf{Standing Leap \textlangle(Ag+Str)/40\textrangle:} The length a character can pass while jumping forward, explained in more detail in the chapter Movement.
		\item \textbf{Standing Jump \textlangle StandingLeap/4\textrangle:} The height a character can jump up, explained in more detail in the chapter Movement.
	\end{itemize}
	\section{Skills}
	Likely being the most common modifier on dice checks, skills represent training in a field. This training ranges through:
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \textbf{unknown:} The character has never had any contact with this very advanced subject. This infers at least a -40 penalty to according skill checks or might also make checks completely impossible.
		\item \textbf{unskilled:} The character has had very little contact with this complex field or barely touched this simple field. This infers a -20 penalty to according skill checks.
		\item \textbf{known:} The character has a grasp of this field’s basics. No modifier is applied.
		\item \textbf{trained:} The character had either some formal training or a natural knack for this field. This grants a +10 bonus to associated skill checks.
		\item \textbf{experienced:} The character had extensive training in this field. This grants a +20 bonus to associated skill checks.
		\item \textbf{mastered:} The character learned everything in this field. This grants a +30 bonus to associated skill checks. If specified or determined by the GM, this may have other prerequisites. 
	\end{itemize}
	Basic skills start unskilled, advanced skills start unknown. The first increase costs 200 XP, the second one (taking a basic skill from known to trained for example) will cost 400, the third 600 and so on. That means increasing a basic skill from unskilled to mastered will cost 2000 XP and taking an advanced skill from unknown to mastered will cost 3000 XP overall.
	\section{Educations}
	\label{eds-explanation}
	In addition to directly applicable fields characters may be trained in, they also have general knowledge. While this might not replace a skill, it might assist them in many different fields. Educations are extremely diverse, so this is just a small list of examples:\\ \\
	\begin{tabular*}{\textwidth}{|l|@{\extracolsep{\fill}}l|}
		\hline
		Education               & Example Skills \\
		\hline
		Armoring                & Security, Survival, Technology \\
		Ground Vehicle Dynamics & Drive, Technology \\
		Psychology              & Appeal, Commerce, Deceive, Interrogation \\
		\hline
	\end{tabular*}
	An education has two potential levels, granting +5 modifiers each and costing 200 and 300 XP respectively.
	\section{Situational Modifiers}
	Some things become easier or harder in certain situations. Potential situational modifiers are vast and always up to GM discretion. Some common circumstances include lighting and the weather for sight based checks or mood, relationship and general disposition for social checks. Tables from page \pageref{situationalmodifiers} onward contain more potential circumstances and their respective modifiers. Obviously those lists are not exhaustive.
	\section{Critical successes and failures}
	Independently of modifiers and target values rolling a 1 always counts as a critical success. In such a case the degrees of success are equal to the characteristic bonus and ties are always won.\\
	Conversely rolling a 100 (00:0 on the percentile dice) always counts as a critical failure. The degrees of failure are 14 minus the characteristic bonus and ties are always lost.
	\section{Skill check examples}
	To give a better overview of how different modifiers add up, here are two somewhat extraordinary examples for each of the classic pillars of tabletop roleplaying. In general these amounts of modifiers might come up in play but situations like these are rare and sometimes hard to keep track of. 
	It should be the table’s collective decision how many different modifiers and which of them in particular are being included. 
	\subsection*{Combat}
	\ul{Situation:}\par
	\begin{exampleblock}
		\textit{Storm hits Eric’s face, the cold rain almost cutting up his face. The faint moonlight is barely visible through the densely clouded night sky. His old, trusty scope had long since broken down and the barrel was damaged, yet he had to take this chance for it might be the last he’d ever get.}
	\end{exampleblock}
	\ul{Mechanical Solution:}\par
	\begin{exampleblock}
		Both strong winds as well as heavy rain infer a -10 each and low light conditions bring another -20 penalty for a -40 from environmental effects. Taking aim would grant him a bonus of up to +20, yet due to his broken scope and assuming he does not have a functioning backup for this distance, only a +10 is granted. Assuming again that he is shooting over a long distance as to not be noticed, this infers another -20 penalty that is more than made up for by the fact that his target is now unaware, granting a +30 to hit.\\
		In total the shot is at a -20 penalty and the target may not dodge.
	\end{exampleblock}
	\breakline
	\ul{Situation:}\par
	\begin{exampleblock}
		\textit{Within the haze, the noise, the people there he is, trying to flee the scene. Jenny has her target in her sight, a chance to sneak up - and a chance to strike. Just before she embeds the blade in his spine, he notices, making her job just that much harder.}
	\end{exampleblock}
	\ul{Mechanical Solution:}\par
	\begin{exampleblock}
		The attack within a hazy, cramped environment is marginally more difficult for a -10. She snuck up but was noticed last minute, making the target surprised for a +20 bonus; resulting in a +10 bonus overall.\\
		The unnamed defender is impaired by the same environmental effects. Additionally he is unarmed but defends against a knife, which adds a penalty of -10. In total the defense roll gains a -20.
	\end{exampleblock}
	\subsection*{Exploration}
	*TODO: trailing, sneaking, eavesdropping*
	*TODO: chase scene*
	\subsection*{Social}
	*TODO: Steve's grenade story*
	*TODO: a riling situation*
	
	\chapter{Movement}
	\section{Walking, running, sprinting}
	Characters move at different speeds, starting with a casual stroll and ending in a full-power short distance sprint.\\
	\textbf{Walking speed} is about 3-4km/h, 1m/s or 6m per turn for a normal human being. Being larger or smaller might affect this but to a generally negligible degree. It is not exhausting and most things are not impaired at this speed.\\
	\textbf{Running speed} is half a character’s movement speed in meters per second. At this speed most things and most notably combat actions take a -20 penalty. It is also exhausting after a while, so every ~5 minutes a jogging character takes a level of exhaustion.\\
	A normal character’s \textbf{sprint speed} in meters per second is given by their derived value movement speed. At this speed most actions and most notably all combat actions take a -40 penalty or might, as per GM discretion, be completely impossible. Firing machine guns while sprinting might be difficult due to bulk for example. A running character takes a level of exhaustion every other round.
	\section{Marching}
	For the most part getting access to vehicular transport is easy enough. In some instances though it might be necessary to take longer marches on foot. Normal groups travel at roughly 30 kilometers a day or 40 if they push themselves. Marching is exhausting and every traveler will gain levels of exhaustion depending on their journey.
	\section{Climbing, jumping, leaping}
	Sometimes getting from point A to point B becomes difficult when they are on different elevations. It might also be necessary to cross over obstacles in one’s way and do so fast.\\
	\textbf{Climbing} works just as walking or running would, only that speed is halved. Since usually the climbers hands are occupied, what actions can be taken is up to GM discretion. Actions that need footwork or are taken twisted behind one’s back suffer at least a -20 penalty.\\
	\textbf{Leaping} is another important form of horizontal coverage. Leap length is technically a characteristic-derived value, though it decreases with exhaustion (AB + SB - Exhaustion)/2. Leap length can be doubled with proper run-up (about 4 meters).\\
	Finally \textbf{jumping} is probably the most basic form of vertical coverage. Jump height is a quarter of leaping distance, follows the same rules for run-up and - if the character has something to grip and at least one free hand - may end in a climb.
	\section{Swimming}
	Swimming is the last form of human movement and quite possibly the slowest. For most people swim speed is roughly a tenth of a character’s movement speed. Depending on equipment load, armor and special augmentation it may be even lower or completely impossible as per GM discretion.
	\section{Movement and size}
	Due to longer extremities larger characters are generally faster, as per the size table. Additionally characters that are at least 2 categories smaller can temporarily occupy the same space, as the small character runs through the larger character’s legs or climbs over. Use common sense to determine where and when that is and is not possible. In any case it should slow down both characters.
	\section{Encumbrance: bulk and weight}
	When a character is carrying too much, he will eventually be over-encumbered. Any object that is carried outside of a proper pouch will cause one point of encumbrance from bulk.
	Any excess weight will also cause encumbrance. One point is gained for surpassing half the character’s strength in kilograms and for a quarter of the character’s strength each after that point. Worn armor effectively only weighs half as much.\\
	While over-encumbered, he takes a -10 on all physical actions - most notably combat - for every point of encumbrance he has. Speed is reduced by 1 for every two points of encumbrance.
	
	\chapter{Combat}
	\section{Initiative and combat speed}
	Before combat can start, every character needs to have an initiative value. Every creature has a base initiative value and adds 1D5 to it.\\
	Every combat round is 3 seconds long and consists of a \textit{declaration phase} and an \textit{action phase}. Having higher initiative means declaring later, when that character knows what slower characters will do this round, and resolving their actions before those of slower characters.\\
	Initiative is variable. When a character is disorientated by being blinded, stunned or falling to the ground, he loses initiative. How much is up to the GM but should be between a D5 for taking a heavy hit to the head and a D10 for smacking his head on the floor.
	\section{Control area}
	Every combatant has a control area. The control area is 120° in front of the character and within melee range.
	\section{Actions}
	Every character has 2 actions per combat round, in addition they are allowed to move. Remember that all actions are happening simultaneously, so some actions might be more difficult while moving.
	There are two types of combat actions: active actions and reactions. By default one of the character’s actions is active, the other is reactive. Active actions include attacks, reactions encompass parries and dodges. Actions are interchangeable: when turning an action into a reaction or vice versa, the turned action will be at a -20 penalty. Turning actions has to be declared.
	\section{Maneuver basics}
	A maneuver describes a combat action a character can take. These actions might look differently or executed in a different way, yet mechanically act the exact same way: a skillful attack to the most vulnerable parts of the human body and a particularly powerful blow will both increase the impact’s damage at a cost to accuracy and therefore are both mechanically \textit{powerstrikes}.\\
	Unless specified otherwise any character can use any maneuver even without being properly trained (i.e. knowing the ability) but all penalties are twice as high to achieve the same results.
	\section{Voluntary penalties}
	Most maneuvers take great risk and the bigger the risk, the higher the reward. Voluntary penalties are taken by the acting character and have some sort of effect on maneuvers. The maneuvers that profit from voluntary penalties are designated with a -X modifier.\\
	Voluntary penalties can’t be taken to reduce the target value below 20. If multiple maneuvers profit from voluntary penalties, the benefits are split freely among them.
	\section{Shooting size \& multiple targets}
	When attacking a group of targets or one large target in ranged combat, hitting becomes easier. Depending on the overall target size a bonus to hit given on the Size-table is inferred. If the target is a group, the individual target is determined randomly.\\
	Attacking a single target in a large, moving group is impossible and the target will have to either be lured out or hit by chance.
	\section{One-handed weapons and dual-wielding}
	When wielding two weapons, the character may attack using both weapons in one action. Using small arms is at a -30, using large weapons is at -60. Additionally, attacking different targets is at a -10 penalty.
	\section{Melee dancing}
	When attacking or defending in melee combat, the combatants are rarely stationary. After an attack the character and his opponent move a meter into a random direction within the same control areas. Roll a D10:
	
	\begin{tabular}{ll}
		1-2: & towards the opponent\\
		3:   & forward right\\
		4:   & right\\
		5:   & backwards right\\
		6-7: & away from the opponent\\
		8:   & backwards left\\
		9:   & left\\
		10:  & forward left
	\end{tabular}

	\newpage
	\section{General combat actions}
	\subsection*{Stand up / Hop up / Drop}
	Unless restrained a prone character can spend one action to start kneeling, a kneeling character can spend an action to stand up. A prone character may choose to make an agility check instead to stand up in one action instead. On a success he stands up, on a fail he stays prone.\\
	Dropping lower is a free action, no matter if to the knees or prone.
	\subsection*{Gather senses}
	The character gets a grip of the battlefield again after losing her overview. She re-rolls initiative.
	\subsection*{Draw / Ready}
	Draw a weapon or ready an equipment piece.
	\subsection*{Defensive stance}
	A combat stance to increase one’s defensive capabilities. Grants a -30 to offensive actions but +10 to defensive actions. Unlike other defensive actions this must be declared during the declaration phase but it may be taken without an ability.
	\subsection*{Assistance / Cooperation}
	In combat assistance should be handled as a combined action (see below). Outside of combat, especially during extended actions, one character is designated as the primary actor and other characters may become assisting actors. Assisting actors make their specific tests first, granting the primary actor their degrees of success * 5 as a bonus or their degrees of failure * 5 as a penalty to her test. Assisting tests are not necessarily required to use the same characteristic or skill, for example:
	
	\begin{exampleblock}
		John attempts to help Kelly jump into a window. Since the window is narrow, Kelly will be making a check against her agility based Acrobatics skill, while John - using controlled, precise strength - uses his strength based Athletics skill.
	\end{exampleblock}
	\subsection*{Spotting}
	Spotting is a special type of assistance. The shooter and the spotter take a combined action with the spotter using Perception. 10 times his DoS will be added to the shooter’s attack roll instead of 5 times.
	\section{Melee actions}
	\subsection*{Standard attack}
	A single armed or unarmed melee attack. Attacking a specific location is modified by its size. This is compatible with any maneuver and does not require an ability. 
	\subsection*{Sure strike (+20 modifier, also uses up reaction)}
	A single melee attack with higher chances to hit. This maneuver cannot be combined with any other and does not require an ability.
	\subsection*{Attack of opportunity (-10 modifier, free action)}
	When an enemy passes through the character’s control area, the character may make a single attack as a free action with a -10 modifier in addition to any other maneuver.
	\subsection*{Disengage (free action)}
	When disengaging, no attacks are allowed to be made that round but no attacks of opportunity are invoked.
	\subsection*{Feint (-X modifier)}
	A skillful attack that is harder to defend against. The defense against this maneuver is at a penalty equal to the voluntary penalty.
	\subsection*{Called jab (-20 -opponent’s armor)}
	A strike against an armor’s weak points. The attacker picks the location without additional penalty. The attack ignores half the target’s armor.
	\subsection*{Disarm (-30 -X modifier)}
	An attack against the opponent’s grip to get control of his weapon. The defender makes a dexterity check at a penalty equal to the voluntary penalty of the maneuver. On a fail the defender loses her weapon, dropping on the ground. Failing by at least 3 degrees gives the attacker control over the weapon.
	\subsection*{Flurry (-10 modifier)}
	Two attacks in quick succession using both hands. Defending against this attack requires two reactions. On a hit the attacker deals damage once with her primary weapon and once with the weapon in her offhand. If she is not carrying a weapon in her offhand, she deals unarmed damage instead. 
	\subsection*{Piercing thrust (-40 -half of opponent’s armor, also uses up reaction)}
	An all-out stab attack. The attacker picks the location without additional penalty. The attack ignores all armor and even the injury threshold. Cannot be performed without the corresponding ability.
	\subsection*{Take-down (-20 -X modifier)}
	A sweeping and pushing attack to take the opponent off his legs. If the attack hits, it deals no damage. Instead the defender makes an agility check at a penalty equal to the voluntary penalty on the maneuver. If that fails, he falls on the ground. If it fails by 3 or more degrees, he also drops his weapon.
	\subsection*{Shift (-10 -X modifier)}
	Superior footwork or raw force moves an opponent. If the attack hits, the opponent makes a strength check at a penalty equal to the voluntary penalty on the maneuver or be moved by up to a meter per degree of failure in a direction chosen by the attacker.
	\subsection*{Powerstrike (-X modifier)}
	A strong blow that increases the hit’s damage. For every 5 points of voluntary penalty the damage is increased by one.
	\subsection*{Cleave (-15 modifier per target, also uses up the reaction)}
	A half circle of steel pushing multiple enemies back. This maneuver can target up to three enemies. A success indicates hits on all targets. A target hit will - in addition to normal effects - be pushed back by the attacker’s StrB in meters -1 per size category the target is bigger. This maneuver is always also a Knockdown.
	\subsection*{Stunning blow (-20 -X modifier)}
	A blunt attack to stun a target. If the hit is successful and the attack would deal damage, then deal half of the effective damage and the target makes a Constitution check at a penalty equal to the voluntary penalty on the maneuver. By GM discretion the target may also fall prone.
	\subsection*{Knockdown (-20 -X modifier)}
	A forceful attack to knock the target off their feet. If the attack hits, the target makes a Strength check at a penalty equal to the voluntary penalty on the maneuver. On a fail the target falls prone.
	\subsection*{Charge (-20 modifier, also uses up reaction)}
	An attack utilizing the momentum of movement. The attack gains a bonus to damage equal to the attacker’s current speed, usually his sprint speed. He needs a minimum of 4 meters of runup.
	\subsection*{Crushing blow (-40 -X modifier, also uses up the reaction)}
	A powerful, all-out attack that deals greatly increased damage. If the attack is a success, the damage is first increased by one per full 5 points of voluntary penalty and then damage and AP are doubled. Cannot be performed without the corresponding ability.
	\section{Melee reactions}
	\subsection*{Dodge (-10; -0 against unarmed)}
	Evasion without weapons touching. Evasion has to be declared before the attack is rolled. On a success the attack is evaded. This does not require an ability.
	\subsection*{Parry}
	A basic defense against a melee attack. Parrying has to be declared before the attack is rolled. On a success the attack is evaded.
	\subsection*{Bind (-X modifier)}
	Enter a bind to lead one’s opponent’s weapon and gain an advantage. The next action the character takes has a bonus equal to the voluntary penalty.
	\subsection*{Disarm from reaction (-30 -X modifier)}
	A very risky defense to rid the opponent of their weapon during her attack. If the defense is successful, the attacker makes a dexterity check at a penalty equal to the voluntary penalty of the maneuver. On a fail the attacker loses her weapon, dropping on the ground. Failing by at least 3 degrees gives the defender control over the weapon.
	\subsection*{Intercept (-20 modifier, uses attack value)}
	A reckless attack into the opponent's attack. If only one attack is successful, that attack deals damage as normal. If both succeed, the one that succeeded better (see Dice checks and stats-Opposed Checks) deals full damage, while the other one only deals half damage.\\
	Intercepting a Charge is at an additional penalty equal to 5 times the character’s CrB below 8 but deals additional damage equal to the target’s movement speed.
	\subsection*{Reversal (min -30 modifier)}
	A skillful counterattack that exploits an overswing. This maneuver can only be used against a Powerstrike series maneuver and grants a penalty equal to the attacking powerstrike penalty, at least -30. If the defense is successful, the maneuver also counts as an immediate powerstrike against the original attacker with a voluntary penalty equal to this maneuver’s penalty. The attack may be parried as normal and may also be subject to Reversal. Cannot be performed without the corresponding ability.
	\section{Grappling}
	Grappling may be somewhat more complicated than striking due to the amount of options one has and how different these options are to striking: control over someone else and dislocation of opponents or their limbs.
	\subsection*{Hold}
	A hold is the basis of all grappling. By itself it only stops the opponent from leaving but it is necessary for most other maneuvers to initiate.\\
	To initiate a hold, the character makes a grappling check which may be opposed by the target as a reaction. If the character wins, a hold is engaged.\\
	To break free the target makes a grappling check which may be opposed by the character as a reaction. If the target wins, it breaks free.
	\subsection*{Throw}
	The character attempts to lift the target off the ground and forcefully put it back.\\
	The character makes a grappling check which may be opposed by the target as a reaction. If the character wins, the target takes D10+StrB damage with the trauma quality and falls prone (therefore also losing D5 initiative).
	\subsection*{Lock}
	The character attempts to prevent his opponent from moving freely. Arm locks, leg locks and head locks are common but bear hugs also fall into this category.\\
	To initiate a lock, the character makes a grappling attack roll which may be opposed by the target as a reaction.\\
	While the lock is active, the character may use an action to interfere with any action taken by the target: the character takes a grappling check as an action and the target’s action is at a -10 penalty per degree of success.\\
	To break free the target may take a -10 grappling check, which may be opposed by the character as a reaction. If the target wins, it breaks free, back into the initial hold.
	\subsection*{Lever hold}
	While holding an opponent in a lock of some kind, the character may choose to initiate a lever hold as an action. This forfeits the option to control any action in favor of dealing damage to a location every turn.\\
	To initiate a lever hold, the character has to have his target in a lock already and takes a grappling check which may be opposed by the target as a reaction. If the character is successful, a location is determined and a lever hold is initiated.\\
	While the lever hold is active, the character deals 1D5-2+StrB damage to the location, ignoring armor.\\
	To break free the target may make a -20 grappling check, which may be opposed by the character as a reaction. If the target wins, it breaks free.
	\subsection*{Choke hold}
	Another common grappling target besides joints are the airways.\\
	To initiate a chokehold the character makes a grappling check which may be opposed by the target as a reaction. If the character wins, the chokehold is initiated.\\
	The chokehold works like a lever hold but instead of dealing damage, it causes suffocation.\\
	To break free the target may make a -20 grappling check, which may be opposed by the character as a reaction. If the target wins, it breaks free.
	\subsection*{Move}
	Moving while grappling is hard, even more so if only one party intends to move.\\
	The character makes a grappling check which may be opposed by the target as a reaction. If the character wins, the target is moved up to the difference of DoS in meters or half the amount if on the ground.
	\section{Ranged actions}
	\subsection*{Aim}
	The character designates a target and takes aim. For every action aiming the character gains a +5 on her next shot against that target up to +20 for 2 combat rounds. The bonus vanishes when her concentration, line of sight is broken or the target moves more than the effective Perception bonus (Instinct + Perception divided by 10, rounded down) in meters per round. Without proper installations to assist aiming, only +10 may ever be gained. Proper installation generally means a scope with a magnifier of at least 1/100th and at most 1/30th the distance in meters.\\
	This maneuver does not require an ability.
	\subsection*{Brace}
	A character using a heavy weapon or launcher needs to find a fixed firing position or infers a -20 to hit checks. Finding such a rest takes an action. Moving from your position or dodging breaks bracing. This does not require an ability.
	\subsection*{Reload}
	The character reloads his firearm. Depending on the weapon used, this can take varying amounts of time which usually may be interrupted if the character needs to dodge.
	\subsection*{Assisted reload}
	A heavy or launcher weapon can be reloaded with the help of another character instead. This will take both characters’ actions but the time to reload will be cut by half.
	\subsection*{Single shot}
	The character takes a single shot against an enemy. Aim bonuses are not lost unless the target breaks line of sight or moves very quickly. This does not require an ability.
	\subsection*{Burst (-10 modifier)}
	The character takes a relatively controlled burst of fire against a target. This encompasses everything between automatic pistols, heavy machine guns, flamethrowers and sustained arc rifles, even though some of those might not technically fire in bursts. For every degree of success on the check one additional hit is scored, up to a maximum of the weapon’s rate of fire in total. Aim bonuses are lost after shooting.
	\subsection*{Suppression Fire (-20 modifier)}
	The character shoots in the general direction of his enemies, expecting them to keep their heads down so as to not lose them. Whether a hit is scored or not, all enemies within an area of roughly twice the bullets fired in meters diameter are making courage checks at a penalty equal to 4 times the bullets fired. On a failure they will not leave cover until they either spend an action to retry the courage test (once per turn) or the suppression ends. Anything threatening them directly in a situation where they are pinned, such as grenades behind their cover, will cause them to suffer from fear.
	\subsection*{Called Shot (-size modifier)}
	The character targets a specific location. This does not require an ability and may modify another ranged maneuver.
	\subsection*{Reaction: Dodge (-10 modifier)}
	When dodging against single ranged attacks, the attack and defense checks are opposed. If the attacker wins, the target suffers damage. If the defender wins or the test ties, the attack is evaded.\\
	When dodging against multiple ranged attacks, the defender dodges one bullet per degree of success. The reaction may still only be taken against a single attacker.\\
	When dodging against explosives, a success may increase the distance to the center of the blast by 1+DoS.\\
	This maneuver does not require an ability.
	\section{Combined actions}
	To take combined actions, the involved members need some way to communicate - preferable privately - and go on the lowest initiative. The team may distribute all Degrees of Success among each other freely.
	\section{Damage and armor}
	When a character takes a hit that is not defended against, first worn armor and cover are reduced by the attack's armor penetration to a minimum of 0. The leftover armor and the target’s injury threshold then reduce the attack’s damage to a minimum of 0. Any leftover damage is then applied to the randomly determined hit location and the target now takes penalties in accordance.
	\section{Cover and concealment}
	Any object blocking line of sight is considered \textbf{Concealment}. Attacking a target behind such concealment comes with a -30 penalty as if blindfiring.
	\textbf{Cover} on the other hand provides additional armor points depending on material and thickness. The table below gives examples of how much armor points a centimeter of some material may provide.\\
	Cover degrades. For every 5 points of damage (not armor penetration) a section of cover blocks, the armor it provides is reduced by 1. If a section of cover functions as both cover and concealment, the concealing effect stops when roughly 25\% of armor remains.
	
	\chapter{Healing}
	\section{Anatomy}
	The human body is no monolith, so it will be looked at in 6 parts: two legs, two arms, the torso and the head. To determine a random location, consult the chart below. When a regular hit is scored, the two dice are swapped to determine the location, example: a character shoots a target. The hit roll is a 37, so the location is a 73, therefore hitting the right leg. Attacks scoring multiple hits may use the same location for convenience or roll different locations for all additional hits.
	\section{Degradation}
	For every full 20\% of location HP lost, the character takes a penalty to all values in the “Degrading stats” column when using this body part. Usually this penalty is a -10, the exception is initiative; base initiative is reduced by 1 and D5 temporary initiative is lost that can be gained back through the “Gather Senses” action.\\
	When 60\% is lost, light bleeding begins and at 80\% severe bleeding sets in. At more than 100\% the body part is lost or crippled, details are up to GM discretion.
	\section{Lethality}
	There are multiple ways for any living character to die. 
	Firstly there is \textbf{critical organ failure}. This is achieved by destruction or removal of essential organs. When the torso or head body location is destroyed in a spectacular fashion, the GM may rule that this character has died on the spot.\\
	Secondly a character may die from \textbf{blood loss}. When characters start \textbf{bleeding lightly} as determined by the anatomy table or GM discretion, they have ConB minutes (or ConB*20 rounds) before unconsciousness sets in. They then have another ConB*9 seconds (or ConB*3 rounds) before they irrevocably bleed out. When \textbf{bleeding severely} the character only has ConB*3 seconds (or ConB rounds) before unconsciousness sets in. After that he can be saved for only ConB+D5 rounds or bleed to death. Note that “light” and “severe” bleeding are a distinction within the game; both are actually quite severe, a matter of life and death.\\
	With basic medical knowledge (a medication check +50) a character can stop another from bleeding out. That character needs to be right next to the patient and cannot perform any other actions other than holding the wound shut.\\
	\textbf{Overexertion} is often overlooked but can very well be lethal. Generally if a character’s exhaustion surpasses their ConB, they collapse, recovering from one level per 2 hours of rest. If the character manages to surpass 3 times her ConB, the character collapses but does not recover naturally anymore. If the character can be saved at that point is up to the GM.
	\section{Natural healing}
	Characters recover from wounds naturally. The wounded character takes a constitution test at a modifier according to the table below. He heals one wound plus one per degree of success, if any. Recovery is split evenly among damaged zones, prioritizing more severe injuries. This recovery only happens if the wounds can at all heal and are not infected.
	\section{Medical attention}
	If a character gets medical attention, he recovers in addition to his natural healing. The medical check is at a -5 penalty for every location that is being treated beyond the first, so up to a -25 if the whole body is being treated. If the performing doctor is also the patient, the test takes an additional -15. Every treated zone will recover from one wound and the tending doctor can split their DoS between all treated locations to recover from even more wounds. Any character can benefit from this once per day.
	\section{Recovery time}
	Certain actions will require recovery time.\\
	After \textbf{implant surgery} a character will have to recover for two weeks. If he is to act during this time he suffers penalties at the GM’s discretion, at least a -20 to all mental characteristics and a -2 to initiative.\\
	The second, more common recovery will be from \textbf{exhaustion}. A character recovers roughly 2 levels of exhaustion per 3 hours of proper rest.
	
	\chapter{Hazards}
	\section{Common hazards}
	A few hazards threaten everyone.\\
	Exhaustion is easily the most common threat to any character after physical damage. Exhaustion is gathered through many ways. Every level of exhaustion gives the character a -10 penalty to any check. If exhaustion reaches too high, the character is at risk of overexertion (see Healing-Lethality).\\
	Uncontrolled falling is the most common way the environment will try to kill a character. By default the character will take damage that ignores armor but not injury threshold. The damage is an amount of D10 equal to a third of the distance fallen in meters and hits an additional zone per full 5 meters, not hitting any zones twice.\\
	For example hitting the ground after falling 12 meters would deal 4D10 damage to 2 locations. If the fall was 64 meters instead, it would deal 21D10 damage to all locations.\\
%	Heavy objects falling on top of a character deal damage according to the same calculation, except the result is multiplied with the difference in weight between the character and falling object. It hits as many zones as feasible for its size.\\
%	For example a flower pot falling from 12 meters would deal 4D10 damage with the result being divided by
	\textbf{todo: falling objects?}\\
	Suffocation, also encompassing drowning and smoke inhalation, is an often underestimated threat to most characters. If a character consciously holds her breath, she can hold it for three times her Constitution in seconds. While holding her breath, she can’t fight or do very strenuous tasks. If she cannot or can no longer hold her breath, the effects of suffocation set in after one round.\\
	The afflicted character will gain exhaustion every round starting with 1 on the first round, 2 on the second round and so on.\\
	Fire and the burns associated with it are a minor threat to characters. Fire does minor damage, generally up to D10 per round, but it deals its damage to every location ignoring three quarters of any non-sealed armor. Fire generally comes with smoke and eats away at the oxygen in the air - both of which can be very lethal in enclosed spaces, see Suffocation.\\
	Freezing is relatively rare. Should a character be submitted to cold temperatures without proper equipment however, she will suffer a level of exhaustion every hour. If temperatures are freezing cold, she will suffer 2 levels per hour.\\
	Starvation is even rarer and purely optional, food is widely available. Should the party be confronted with the wasteland however, starvation suddenly enters the ring. Starvation progresses in 5 steps, advancing one per day of no or inadequate food. Eating around half as much as required advances the effects by one step only every two days.\\
	After the first step the character will be distracted by hunger, increasing all disabling characteristics by 15. After two steps natural healing is stopped and recovery times are twice as long. The character also shows the first visual signs of malnourishment. After step three she takes -15 to every test and exhaustion does not regenerate naturally anymore, while after the fourth one level of exhaustion is also gained every day. Five days in the character will start hallucinating.\\
	Starvation starts recovering when the character has eaten enough again by one step every rest phase.
	\section{CBRN}
	While not quite an everyday occurrence, CBRN hazards are still quite common. Chemical terrorism or dirty bombs, ruins of ancient broken power plants or engineered animals; our protagonists are at a constant risk to face such hazards.\\
%	Biological and chemical hazards are likely the most common special hazards. “Biological” includes disease, as well as animal and plant toxins, and “chemical” encompasses synthetic poison, chemical fires and fumes as well as drug intake. In both cases the inflicted victim makes a constitution check at the specified penalty. If it passes, it suffers no ill effects. If it fails, it is afflicted with the hazard’s full effect. Chapter *TODO: add ref* contains specific biological hazards, while Chapter *TODO: add ref* contains chemicals.\\
	Radiological hazards, encompassing everything between radiation sickness and cancer, is a constant threat in fallout zones.\\
	An hour or two after exposure the afflicted makes a constitution check at a penalty or suffers effects depending on the dosage of radiation. Decrease the severity by one step per degree of success on the resistance test.\\
	Nuclear hazards are essentially a radiological hazard following an explosive and should be handled as such. In addition all technology will be afflicted by a strong EMP effect.\\
	EMPs, while not technically a CBRN hazard, are similarly common. EMPs are capable of disabling improperly shielded technology and can either be used voluntarily by educated personnel or can be created as a side product from orbital mining operations, terraforming or high-powered plasma lances. For every meter the machine is inside the EMP’s radius, it is disabled for one round or 3 seconds narrative time. Once the time reaches 30 seconds, all stored data is wiped.\\
	Cybernetic limbs affected by EMP cause one level of exhaustion to the wearer every round. Inner augments cause D5 levels instead.\\
	Proper shielding reduces the time of the effect and certain data drives can be immune to wipes by means of EMP.
	\section{Shock, fear and trauma}
	When a character is exposed to stressful situations, he will suffer from shock. The character makes a courage check with a modifier according to the source and severity of shock. This ranges from +0 for large amounts of blood or some dead bodies over -20 for watching someone die in front of oneself to -60 in truly desperate situations or near-death experiences. Generally the better the reputation with the injured person and the less predictable the situation, the higher the penalty. It also takes a penalty equal to the sum of all “Fear” or “Phobia” disabling characteristics that fit the situation.\\
	In case the character meets multiple panic situations in a day, add a -10 penalty for each after the first.
	
	If the check is failed, roll a D100, add 10 times the degrees of failure and apply the according result from the table on page \pageref{feartable}.
	\chapter{Transhumanism}
	\section{Philosophies}
	To understand the conflict about augmentation, one has to understand two standpoints. \textbf{Transhumanists} support augmentation of the human body. Science is a human aspect, evolution alone can only limit them. Extremists will try to exchange every part of their body with some form of cybernetic or biotechnological replacement even if only for vanity.\\
	\textbf{Body purists} believe that too many augments makes a person lose his humanity. Others fear that nerve load might be higher than initially expected, crippling some, driving others insane. The reliance on technology makes humans vulnerable to failure of even just one of those systems. Body purism is no monolith; supporters might believe one or multiple of these things or even something else entirely.
	\section{Cybernetics}
	Cybernetic augmentation is widespread. Missing or deformed limbs are replaced or existing body parts enhanced to help with work or social life. They don’t naturally regenerate anymore, they are expensive and create a huge load on the patient’s nervous system, as indicated by Rayleigh index values. However they are generally more resilient than most human limbs and most of them offer additional special features. Obviously it takes very invasive surgery to install.
	\section{Biotech}
	Biotechnological engineering has come a long way and engineered body parts are rather common. Vat-grown clones of original human body parts or extra dextrous arms; slim, fine legs or extremely dense back muscle implants; whatever it may be, it falls into this category.
	Compatibility with a human host body is even harder to assure than it is with cybernetic implants, so biotech implants put a great amount of stress on the rest of the body, as indicated by medical toughness.
	\section{Chemicals}
	Chemical augmentation is a powerful way to enhance one’s abilities for a short period of time. It is common among thugs that cannot afford proper bionics but also among military and mercenary personnel that need to surpass human peak performance. Chemical augmentation comes with a temporary benefit and some sort of drawback when it runs out. Overuse and overdose can be harmless or extremely dangerous depending heavily on the substance at hand.
	
	\chapter{Hacking}
	\section{Basics}
	Any piece of cyberware that in some way has a connection to another device may attempt a hacking attack. If someone is monitoring the target device, that person may defend or counterattack.\\
	The attacker’s goal is to reduce the target devices’ \textbf{integrity} to 0, working much like damage in combat. If the integrity reaches 0, the attacker gains access to read, write and execute. Attacking gains a modifier called the attacking device’s \textbf{processing power}.\\
	The device protects itself by means summarized as “\textbf{firewall}”, working much like a character’s damage threshold.
	\section{Actions}
	\subsection*{Attack}
	When attacking a device, the character may once per turn spend an action to attack. He makes a Computer Operation check, dealing 1D5+DoS to the target’s integrity, reduced by the target’s firewall. Failing by 10-firewall degrees of failure (or critically) locks the attacking device out of the target device indefinitely.
	\subsection*{Restore}
	As a defender - instead of counterattacking - may restore integrity to the target of the attack. As an action once per turn the defender may make a Computer Operation test to restore 2+DoS integrity.
	
	\chapter{Character Creation}
	\section{Basics}
	Character creation uses two different point pools: Generation Points, or GP for short, and Experience Points, or XP for short. GP describe the most basic attributes that make up your character, while XP depict everything the character has learned.\\
	Every character begins with 100 GP and 2500 XP. While you can use XP later on in the campaign, make sure you have exactly no GP left when you finish character creation as any leftover is wasted.
	
	Before anyone determines what the character is - i.e. create a stat sheet - first it needs to be decided who said character is. The following list of 20 questions covers all questions a player or a GM may have concerning a character and will form the basis for character creation. Keep them in mind at every step, as they define who your character is at its core.
	
	\begin{enumerate}
		\setlength\itemsep{-8mm}
		\item What does the character look like?
		\item What first impression does the character leave on strangers?
		\item How did the character grow up?
		\item Does the character still have relations to people from his past?
		\item Why did the character join the party?
		\item Where has the character been already?
		\item How does the character regard transhumanism?
		\item What’s the character’s opinion on chemical enhancements and recreation?
		\item For who or what would the character risk his life?
		\item What’s the character’s biggest wish?
		\item What’s the character’s biggest fear?
		\item What does the character’s morality look like and how law-abiding is he?
		\item Is the character open towards strangers?
		\item How important is life to him?
		\item What does the character think of animals?
		\item What does the character regard as beautiful?
		\item What does the character like to eat and drink? What would he like to try?
		\item What does love look like to the character?
		\item Does the character have a dark secret?
		\item What character traits define the character?
	\end{enumerate}
	\section{Race \& Background}
	Player characters are not the average Joe; they are heroes, villains, the protagonists of their story. However before they became these prodigies, they had to have done something, been someone. This is represented by race and background, the first step of character creation, which every character needs to have.\\
	Races and backgrounds have an associated GP cost and grant various bonuses and some penalties. Comprehensive lists can be found in sections \ref{sec:racelist} and \ref{sec:backgroundlist}.
	\section{Characteristics}
	GP can be spent to increase characteristics. Every characteristic can receive up to 25 points and up to 100 can be spent on characteristics overall but they don’t have to be exhausted.
	\section{Boons \& banes}
	The leftover GP can be spent on Boons and missing GP can be compensated with Banes.\\
	Boons describe an inherent advantage this character has over others. This is nothing that can be learned afterwards but it might be at least partially substituted with augments.\\
	Banes are disadvantages that are either innate or stem from the character’s background and are extremely hard to get rid of. They don’t cost GP but grant them instead. Up to 40 GP can be generated from banes. It should be assured that all boons and banes don’t exist purely for mechanical reasons but that they fit the character.
	\subsection{Disabling characteristics}
	A special type of Banes are Disabling Characteristics. They behave much like characteristics in that when they come up, a test is made involving them. If the test is successful, the character suffers from whatever the disabling characteristic describes, e.g. fear, arrogance, greed or megalomania.\\
	Alternatively whenever a character is making a test they would be affected by a disabling characteristic, e.g. climbing with a fear of heights, that test might be at a penalty equal to the disabling characteristic. They range from 20 to 70 only grant additional GP per full 5 or full 10 as specified.
	\section{Skills}
	The first thing to spend experience on are skills. Some skills might already have advancements from race or background. If those have prerequisites that the character does not fulfill, they are dormant until the character fulfills the prerequisites. See a full list of skills from page \pageref{skilllist} onward. 
	\section{Educations}
	Next every character has some sort of knowledge, represented by educations. Some educations might be given by background. If those have prerequisites that the character does not fulfill, they are dormant until the character fulfills the prerequisites.\\
	See an example list of Educations on page \pageref{eds-explanation} or make some up. 
	\section{Abilities}
	Some abilities might be interesting for the character as well. Some abilities might already have advancements from race or background. If those have prerequisites that the character does not fulfill, they are dormant until the character fulfills the prerequisites. A full list of abilities can be found from page \pageref{abilitylist} onward.
	\section{Shopping trip}
	Lastly, a character needs some equipment. The amount of money is dependent on the character’s background and possibly boons. By default every character will start with clothing fitting of their social standing, former profession and to a degree place of origin. Visit the equipment section below to buy anything beyond that. 
	
	\chapter{Equipment}
	\section{Special Rules}
	\specialrule{Adjustable}{Allows spending double ammunition for double range; shooting two full rounds like this deals the weapon's damage to the gun and the user.}
	\specialrule{Backblast (X)}{Everyone behind the shooter in a cone - X meters in length and X/2 meters in base diameter - takes half the weapon damage as if hit by a weapon with the Blast rule. If a wall blocks the cone, the area becomes a circle instead and includes the user.}
	\specialrule{Blast}{Every character inside the area takes a hit. For every 2 meters inside the Blast radius the target is, one additional location is hit, up to every location once.}
	\specialrule{Bulky}{Can't be carried in holsters, slings or on mag holsters}
	\specialrule{Cumbersome}{Halves speed and grants -10 to all physical actions}
	\specialrule{Disrupt}{Turns off PES hit for D5 rounds.}
	\specialrule{EMP}{Causes 2D10 rounds of EMP.}
	\specialrule{Flame}{Sets surfaces and flammable objects hit ablaze.}
	\specialrule{Flash}{Every affected character makes an Ins check at a -10 penalty. Everyone in the Blast radius looking at the source is Blinded, everyone in half the radius is Deafened and everyone within a third of the radius is Stunned for the DoF+2 in rounds. }
	\specialrule{Flexible}{The weapon cannot be parried. It only gains half of the normal melee damage bonus.}
	\specialrule{Improvised}{Does not require familiarity but instead always invokes -10 penalty and fumbles on 96+}
	\specialrule{Infection}{When touching an open wound, such as when dealing damage with an attack, the target makes a Constitution test at a -20 penalty. On a failure the target is infected by the Cerberus fungus.
		Creatures smaller than mice will simply die.}
	\specialrule{Multitargeting}{Only one attack is rolled and can be split freely among many targets.}
	\specialrule{Oversized}{Built for battle mechs, cannot be used by normal people}
	\specialrule{Piercing}{StrB is added to AP}
	\specialrule{Powered}{Requires external powersource to function}
	\specialrule{Reliable}{Can't jam and the weapon has 20\% more breakpoints}
	\specialrule{Scatter}{+10 to hit at short range or above
		no AP at long range
		adds a d10 dmg when shooting in point blank range}
	\specialrule{Single Loader}{Reload times are given for a full reload but after each piece reloading may be interrupted}
	\specialrule{Smoke}{the area inside and behind the smoke is fully conceiled
		smoke usually remains dense for half a minute and lasts for another half as slightly obsuring; this will be less in wind or active ventilation or more in a fully sealed room}
	\specialrule{Spray}{Ignores 3/4ths of non-sealed armor and all but full cover}
	\specialrule{Stun (X)}{If the target fails a constitution check at a penalty equal to 10 times X, he becomes stunned for the 1+DoF in rounds.}
	\specialrule{Tearing}{Roll an additional damage dice and drop the lowest. Armor (after AP) is twice as effective.}
	\specialrule{Trauma}{When attacking the head location, halve the target's armor. Also halves Stunning Strike penalties.}
	\specialrule{Unwieldy}{The weapon disallows transforming actions.}
	\specialrule{Upgrade Kit (X)}{The weapon is an upgrade kit for another weapon X. Price and weight include X.}
	
	\section{Supply}
	\supply{EC-Comm}{communication}{Two-way emergency communicator that fits in the ear. There are variants for all types of trans-species; vatgrown are assumed to have normal human proportions.}{cr 18}{0,01 kg}
	\supply{Emergency Location Beacon}{communication}{An emergency beacon used for creating distress signals. Able to send an emergency signal on multiple open channels up to 15 kilometers.}{cr 5}{0,03 kg}
	\supply{Marker/Transmitter}{communication}{Small Tracking device and location transmitter. Can be tethered to almost any smart device.}{cr 22}{0,005 kg}
	\supply{Radio Backpack}{communication}{An old backpack-carried radio that can transmit any small amount of data like speech up to 5 KM in clear conditions.}{cr 28}{26 kg}
	\supply{AI Docking Station}{cyberware}{By itself this device does nothing but it has the requirements to hold an AI.\\
		Integrity: 15\\
		Firewall: 6\\
		Processing Power: +25}{cr 512}{12 kg}
	\supply{Business/Lab Server}{cyberware}{A large device with a lot of processing power and storage but without a direct user interface; either needs a direct connection or access via a network.\\
		Integrity: 40\\
		Firewall: 6\\
		Processing Power: +30}{cr 420}{26 kg}
	\supply{Cell phone}{cyberware}{A communication device small enough to fit into one's pocket.\\
		Integrity: 5\\
		Firewall: 1\\
		Processing power: 0}{cr 18}{0,6 kg}
	\supply{Cheap Router/Switch}{cyberware}{A connection device to create or scale networks.\\
		Integrity: 11\\
		Firewall: 2 (may work for connected devices, if the attack passes through)\\
		Processing Power: +5}{cr 12}{0,7 kg}
	\supply{Cracker}{cyberware}{An expensive machine with incredible processing power.\\
		Integrity: 40\\
		Firewall: 8\\
		Processing Power: +30}{cr 108}{9 kg}
	\supply{Portable AI Docking Station}{cyberware}{By itself this device does nothing but it has the requirements to hold an AI. It's small enough to be carried around.\\
		Integrity: 15\\
		Firewall: 5\\
		Processing Power: +20}{cr 896}{5 kg}
	\supply{Secure Router/Switch}{cyberware}{A connection device to create or scale networks. Comes with a few security measures and proper configuration.\\
		Integrity: 25\\
		Firewall: 8 (may work for connected devices)\\
		Processing Power: +10}{cr 50}{0,8 kg}
	\supply{Smart Fridge}{cyberware}{Barely anyone needs a fridge anymore. But those who do tend to pay extra for completely unnecessary features.\\
		Integrity: 5\\
		Firewall: 0\\
		Processing Power: -5}{cr 333}{170 kg}
	\supply{Tablet}{cyberware}{A portable data processing device with a touch screen.\\
		Integrity: 7\\
		Firewall: 2\\
		Processing Power: +5}{cr 23}{1,2 kg}
	\supply{Tactical Datapad}{cyberware}{A tablet that's has 6 armor and shields against 6 rounds of EMP.\\
		Integrity: 8\\
		Firewall: 4\\
		Processing Power: +5}{cr 35}{2,2 kg}
	\supply{Workstation}{cyberware}{A personal computer made to work found in many white collar businesses.\\
		Integrity: 20\\
		Firewall: 4\\
		Processing Power: +10}{cr 43}{8 kg}
	\supply{Flash Glass Goggles}{eyewear}{Made from special glass, these goggles normalize incoming light. This removes all bright-light based penalties and makes the wearer immune to the Flash rule but the user counts as colorblind while wearing it.}{cr 30}{0,45 kg}
	\supply{Holographic Eyepiece}{eyewear}{Allows a HUD to be displayed over one eye.}{cr 28}{0,3 kg}
	\supply{Infrared Goggles}{eyewear}{Goggles that give the ability to see in Infrared, allowing to see heat signatures and infrared devices such as lasers.\\
		Infrared Goggles give Character a +15 Bonus to opposing Camouflage Tests. Infrared Goggles halve all Penalties from Darkness.}{cr 32}{0,45 kg}
	\supply{Night Vision Device}{eyewear}{Grants Boon: Night Vision but doubles all penalties to resist being blinded by bright light.}{cr 18}{0,6 kg}
	\supply{Sun Glasses}{eyewear}{Pair of goggles that halve any Penalties from bright lights but increases low-light penalties by 10 and darkness penalties by 20.}{cr 2}{0,15 kg}
	\supply{Aerial Descent Unit}{hazards}{Standard issue military parachute. Maneuvering uses Pilot: Air but anyone can decent moderately safely using this.}{cr 10}{9,5 kg}
	\supply{CBRN Unit}{hazards}{This unit detects and gives information on chemical and radioactive materials, or any other airborne or grounded contaminant. Will get overworked after 60 minutes in strong radiation, thick gases or similar effects.}{cr 12}{0,9 kg}
	\supply{Climbing Kit}{hazards}{A climbing harness kit that offers the Character a +40 Bonus to climbing tests. Contains a Harness, rappelling kit, and other various climbing tools.}{cr 7}{2,2 kg}
	\supply{Earplugs}{hazards}{A set of Military-Grade earplugs that allow Characters to ignore the hearing-based Penalties given by Flashbangs or other loud noises. \\
		Gives a -25 Penalty to Hearing-based Investigation and Perception Tests.}{cr 2}{0,004 kg}
	\supply{Explosives Detection Assistant}{hazards}{A pioneer support device assisting in detecting known explosive compounds. Grants a +30 bonus to detecting and identifying explosives.}{cr 24}{3,4 kg}
	\supply{Fire Extinguisher}{hazards}{Puts out any fire using foamed dry chemicals. Has 10 uses.}{cr 3}{15 kg}
	\supply{Metal Detector}{hazards}{A metal detection unit that is a small metallic plate on an adjustable pole. The Metal Detector\\
		has a screen at the top of the pole that displays the types of metal found underneath, within\\
		3 Meters underground, and how far underground the object is.}{cr 9}{8 kg}
	\supply{Proximity detonator}{hazards}{An expensive proximity trigger mechanism. A specialist can rig most explosives with this trigger, causing it to go off when a human or vehicles passes 1 to 3 meters depending on configuration.}{cr 12}{0,25 kg}
	\supply{Remote Detonator}{hazards}{A small hand-held device that can be synced up to Demolition and Satchel Charge explosives. Has a range of 400 Meters. At the press of a button or an input of an up to 16 digit passcode, the chosen synced explosives will detonate. Can also be set to timed detonation.}{cr 5}{0,45 kg}
	\supply{Sound Filter Plugs}{hazards}{Small speakers, a microphone array and an equalizer, in a small enough package to fit a person's ear. Ignore all hearing based-penalties.\\
		When broken down, infers a -30 to hearing based tests but still protects from loud sounds.}{cr 8}{0,01 kg}
	\supply{Tripwire}{hazards}{A kit containing all necessary components to rig a grenade into an IED triggered by a tripwire.}{cr 4}{0,7 kg}
	\supply{Field surgery kit}{medical}{A kit containing scalpels, syringes and other equipment to do basic field surgery like removing bullets or even remove augments from corpses provided the necessary expertise.\\
		Grants +10 to medical tests.}{cr 34}{5,6 kg}
	\supply{Field surgery tent}{medical}{A very simple, packaged tent that can be used as an almost sterile field surgery room. Does not protect from the elements much.\\
		Grants +10 to medical tests.}{cr 35}{1,5 kg}
	\supply{Splint}{medical}{When applied this reduces penalties from cracked and broken bones to a quarter.}{cr 3}{0,01 kg}
	\supply{Stitch kit}{medical}{A more elaborate needle and thread that will close wounds for good. Takes a minute (20 combat rounds) and a Medication check +20 for light bleeding or two minutes and an unmodified Medication check for heavy bleeding. Cannot be applied by the bleeding character on his own.}{cr 22}{0,6 kg}
	\supply{Thermal blanket}{medical}{Prevents hypothermia or overheating.}{cr 2}{0,9 kg}
	\supply{Wound dressing}{medical}{Will stop bleeding when applied. Takes 6 seconds (2 combat rounds) but already stops the target from bleeding out when started. Cannot be applied by the bleeding character on his own. Comes in a pack of 20.}{cr 5}{0,2 kg}
	\supply{Wound sealant foam}{medical}{Will stop bleeding. Takes about 12 seconds (4 combat rounds) to use, 2 of which are the application, the other 2 are hardening. Natural healing of the given zone is stopped until the foam is removed by a physician. Comes in packs of 5.}{cr 4}{0,8 kg}
	\supply{Compass}{navigation}{A standard magnetic compass that is not effected by EMP or any other sort of digital or electrical attack.}{cr 1}{0,2 kg}
	\supply{Roadware}{navigation}{Weak AI based GPS-reading software that assists drivers at high speeds and off-roads. The unit gives a +20 Bonus to high-speed driving Tests and Stunting Tests.}{cr 14}{4,8 kg}
	\supply{Balaclava}{protection}{Face mask for face protection from harsh winds or being identified.}{cr 1}{0,3 kg}
	\supply{Clothing, Simple}{protection}{Simple clothing to blend into ghettos.}{cr 6}{1,1 kg}
	\supply{Clothing, Expensive}{protection}{Expensive clothing to blend into high society.}{cr 140}{1,1 kg}
	\supply{Floatation Vest}{protection}{An adjustable floatation vest that allows up to 21 kg float in water.}{cr 2}{1 kg}
	\supply{Gas Mask}{protection}{Allows to breathe in toxic environments. Comes with 5 disposable filters, each able to last 24 hours.}{cr 18}{1,1 kg}
	\supply{Ghillie Cloak}{protection}{The Ghillie Cloak offers a +20 Bonus to Camouflage when used in matching surroundings.}{cr 6}{2,4 kg}
	\supply{Handcuffs}{protection}{Used to bind an individual’s hands or ankles. To escape, a character must roll a -40 security test or a -60 strength test. The handcuffs have an armor rating of 10 and 50 break points.}{cr 12}{0,5 kg}
	\supply{Rain Poncho}{protection}{Protects the user from rain.}{cr 2}{0,8 kg}
	\supply{Rape Whistle}{protection}{A small, loud whistle. Reportedly used by some "special" forces alongside foam swords.}{cr 1}{0,05 kg}
	\supply{Riot Shield}{protection}{The Anti-Ballistics Riot Shield acts as mobile cover for a Character. The Riot Shield is made of heavy mineral carbon with a hardened plastic window to see through. \\
		The Shield covers normal-sized or smaller peoples' full bodies, while larger people must crouch to cover their whole body. \\
		The Riot Shield functions like any normal cover worth 22 armor points.}{cr 28}{5,9 kg}
	\supply{Security Measures}{software}{Decreases a device's processing power by 10 but increases its firewall by 3. Can be deactivated if required for some reason.}{cr 75}{0 kg}
	\supply{Ammunition Bandolier}{storage}{A bandolier that is worn over armor/clothing that can hold up to 100 shotgun shells, 150 rifle and pistol Rounds, \\
		50 Sniper Rounds, and 10 Grenades, mass driver blocks, filled magazines, and 40mm Grenades.}{cr 7}{0,3 kg}
	\supply{Ammunition Pouch}{storage}{Ammunition pouch. Carries 8 magazines, grenades or anything of equivalent size.}{cr 5}{0,35 kg}
	\supply{Blastproof Clear Casing}{storage}{Blast-proof casing. Can hold up to 5 magazines, grenades or size equivalents but is generally used for portable electronic devices. Offers 18 points of cover that also blocks damage from the EMP special rule to devices on the inside. Damage from EMP cannot damage the case.}{cr 21}{2,8 kg}
	\supply{Duffle Bag}{storage}{Soft bagged carrying device like a sports- or backpack. Carries 25 magazines, grenades or size equivalent.}{cr 9}{2,9 kg}
	\supply{Ergonomic Weapon Holster}{storage}{Holds weapons in completely overengineered ways. Time to draw is reduced by one action to a free action minimum.}{cr 16}{0,35 kg}
	\supply{Hardcase/Tactical Hardcase}{storage}{An armored carrying device the size of a small backpack / lunchbox that can be placed virtually anywhere on the body. Capable of carrying up to 14/5 Magazines, Grenades, and Clips, or anything of equivalent size. \\
		The Hardcase has 10 Armor Rating protecting both itself and its content but can only take 30 damage before it's so broken down that it won't hold anything anymore. }{cr 30/18}{1,2 kg / 0,7 kg}
	\supply{Softcase/Tactical Softcase}{storage}{Soft bagged carrying device the size of a small backpack / lunchbox that can be placed on virtually anywhere on the body. Carries 20/7 magazines or grenades, or anything of equivalent size.\\
		The softcase has no armor protecting itself or its content and 25 Break Points before it's so broken down that it won't hold anything anymore. }{cr 25/13}{0,9 kg / 0,5 kg}
	\supply{Tactical Thigh Rig}{storage}{Small, thigh-rigged casing. Carries 3 magazines or grenades, or anything of equivalent size.}{cr 9}{0,2 kg}
	\supply{Weapon Holster}{storage}{Holds a small weapon. Legally bought or issued weapons are generally assumed to come with a proper holster.}{cr 5}{0,3 kg}
	\supply{Weapon Sling}{storage}{Holds a larger weapon.}{cr 5}{0,4 kg}
	\supply{Area Heater}{survival}{A small heater that can heat an area large enough to fill a dome tent.}{cr 24}{2,3 kg}
	\supply{Camping Stool}{survival}{A stool for sitting that has a setting that allows the stool to fit small to large person.}{cr 6}{1,5 kg}
	\supply{Entrenching Tool}{survival}{A compact package funtioning as a shovel, an axe or a crowbar. It is much more convenient than carrying three equipment pieces but does none quite as well as the the real thing:\\
		The crowbar end only grants 20 bonus.\\
		The axe head deals 4 damage less to structures.\\
		The small shovel takes 10\% longer.}{cr 25}{2,5 kg}
	\supply{Fishing Kit}{survival}{A fishing kit that contains a folding fishing rod, ten hooks and bobbers, a spool of 1550 meters of fishing line that can withstand up to 6 kg of tension, 50 pieces of bait, a fishing net that can hold up to 6 kg of weight and a fitting hat.}{cr 7}{2,8 kg}
	\supply{Military Shovel}{survival}{A standard issue sharpened shovel for entrenchment and other uses. Folds down to the size of the shovel’s head. Rust-proof, sturdy and reliable.}{cr 7}{1,4 kg}
	\supply{MRE / Nutrient solution}{survival}{Disgusting nutrient solution that never goes bad - or worse for that matter... \\
		One tube is enough to sustain normal people for a day and one tube is government issued to all registered civilians each day.}{cr 1}{0,3 kg}
	\supply{Multi-Tool Kit}{survival}{A briefcase sized kit of tools for repair and building.}{cr 19}{8 kg}
	\supply{Portable Electricity Generator}{survival}{A portable generator that is capable of powering equipment and structures who either don't have their own or whose generators have broken down.}{cr 42}{26 kg}
	\supply{Portable Food Stove}{survival}{A small stove that can prepare food. Since the advent of large scale nutrient solution supply this piece of equipment has become very rare.}{cr 64}{3,5 kg}
	\supply{Prepared Meal}{survival}{A luxury only very few people choose to afford. Generally a waste of biomass and more of a treat than survival equipment.}{cr 12}{0,5 kg}
	\supply{Proper Meal Ingredients}{survival}{Expensive ingredients that have short shelf life, need the time, skill and installations to be cooked and don't always offer all nutrients a person needs but if prepared correctly can be a rare, tasty treat.}{cr 4}{0,6 kg}
	\supply{Singles/Large/Dome Tent}{survival}{A weather-resistant tent for one/five/ten people to fit in.}{cr 8/22/40}{1,2 / 6 / 12 kg}
	\supply{Sleep Cot}{survival}{A small cot bed for a single person.}{cr 12}{4,5 kg}
	\supply{Sleeping Bag}{survival}{A wind-proof sleeping bag.}{cr 10}{1,2 kg}
	\supply{Survival Blanket}{survival}{A wind and water-proof blanket that uses a thermal lining to keep the user in a more comfortable temperature, closer to their body-heat.}{cr 10}{1,1 kg}
	\supply{Water Canteen}{survival}{A leak-proof survival canteen with a lock top and 2-liter capacity.}{cr 4}{0,6 kg}
	\supply{Water Purification System}{survival}{A portable water purification system, favored by wastelanders. It can process 1 liter of water every two hours. Must be cleaned after each use.}{cr 32}{24 kg}
	\supply{Blowtorch}{tools}{A blowtorch that can be used in any atmosphere and underwater. This blowtorch is plasmabased and will sear through any metal, given enough time.\\
		For every 2 points of Armor or Cover Points something gives, it takes 1 Half Action to cut through a small portion of it}{cr 18}{1,8 kg}
	\supply{Bolt Cutters}{tools}{Powerful bolt cutters. Strong enough to cut through even metal sheets and locks. Pincers may need to be replaced after heavy duty as determined by the GM.}{cr 12}{1,1 kg}
	\supply{Crowbar}{tools}{A proven tool from ages past. Grants a +30 bonus to strength based tests to pry open containers.}{cr 8}{2,6 kg}
	\supply{Duct Tape}{tools}{A simple, strong water-proof tape. A thousand years don't change everything.}{cr 1}{0,3 kg}
	\supply{Fire Starter}{tools}{Small dark-green cubes that when cracked open, begin to spark and get hot. After 8 Seconds (3 Rounds) it begins to burn. Works in wind and in rain. Comes with 8 cubes.}{cr 2}{0,1 kg}
	\supply{Grappling Hook}{tools}{A metal rod with hooks on them that allow for easier climbing when attached to a rope. +10 to Climbing Tests.}{cr 4}{1 kg}
	\supply{Lighter}{tools}{A lighter with a flip-off top that is able to produce flame. Has enough fuel for 100 uses}{cr 1}{0,1 kg}
	\supply{Rope}{tools}{A carbon fiber rope that can hold up to 5 kg. Comes in a bundle of 35 meters.}{cr 6}{4,2 kg}
	\supply{SOS Knife Kit}{tools}{A special multi-tool knife that contains the following tools: Screwdriver, corkscrew, small blade, sharpening stone, toothpick, tweezers, wood saw, large blade, metal saw, scissor.}{cr 6}{0,2 kg}
	\supply{Weapon Cleaning Kit}{tools}{A kit that can be used to clean weapons and perform maintainance to remove any adverse Penalties gained from the weapon being dirty.}{cr 2}{0,7 kg}
	\supply{Binoculars}{vision equipment}{An electronic Binocular. Has 6 zoom functions, 2x/4x/6x/10x/20x.}{cr 4}{0,8 kg}
	\supply{Chemical Light Sticks}{vision equipment}{A Chemical Light Stick is a bendable tube, that when bent, begins to glow. Gives a +10 in any Dark or Pitch-Black scenarios. Lasts for 8 hours. Comes in packs of 10.}{cr 2}{0,2 kg}
	\supply{Fiber Optic Probe}{vision equipment}{A small camera on the end of a 4-meter wire.}{cr 42}{0,6 kg}
	\supply{Flare Gun}{vision equipment}{A small firearm that fires a 40mm Parachute Flare up to 150 meters}{cr 30}{0,9 kg}
	\supply{Flashlight}{vision equipment}{Helps to see in the dark. Lowers any Low-light or Darkness penalties by up to 30 but makes it impossible to hide.}{cr 5}{0,6 kg}
	\supply{Helmet Recorder}{vision equipment}{Records every instance of what happens. Able to store 80 hours of higher quality footage.}{cr 16}{0,4 kg}
	\supply{Signal Flare}{vision equipment}{A bright flare that is activated by snapping the top off. Can be seen from 2 KM away and lasts up to 1 hour.}{cr 3}{0,35 kg}
	\supply{Spotter Target System}{vision equipment}{A scoped spotting system that has multiple zoom variants. X10, x15, x20, x25, x30, and x40 scopes that allow a Spotter to assist a sniper in extreme-ranged combat.}{cr 25}{1,1 kg}
	\supply{Stationary Motion Tracker}{vision equipment}{Scans movement of the environment up to 120 meters and sends it to tethered HUD-capabledevices. \\
		Must be stationary for 1 Minute (10 Rounds) to calibrate and work. If moved, the Stationary Motion Tracker must be re-calibrated for 1 Minute, again.}{cr 88}{29 kg}
	
	\section{Services}
	\section{Ranged}
	\subsection{Weapons}
	*TODO*
	\subsubsection{Pistols}
	\subsubsection{Short Rifle}
	\subsubsection{Long Rifle}
	\subsubsection{Heavy}
	\subsubsection{Launcher}
	\subsubsection{Bow}
	\subsubsection{Throwing}
	\subsection{Mods}
	\subsubsection{Constraints}
	Ranged weapons have a limited number of mod slots which can each only be used once - at some point the weapon becomes unwieldy or the space is simply used up. When in question, apply common sense.\\
	Pistols:
	\vspace{-10mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item Upper Rail
		\item Lower Rail
		\item Barrel
		\item Muzzle
		\item Core
	\end{itemize}
	Rifle:
	\vspace{-10mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item Upper Rail
		\item Lower Rail
		\item Two Side Rails
		\item Barrel
		\item Muzzle
		\item Core
	\end{itemize}
	Heavy Weapon / Launcher:
	\vspace{-10mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item Upper Rail
		\item Lower Rail
		\item Lower Rail (restricted to bipod / tripod)
		\item Two Side Rails
		\item Barrel
		\item Muzzle
		\item Core
	\end{itemize}
	Bow:
	\vspace{-10mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item Upper Rail
		\item Core
	\end{itemize}
	On the following pages all weapon mods are given in this format:\par
	\vspace{-5mm}
	\begin{exampleblock}
		\weaponmod{Name}{Description}{Slot used}{List price}{Weight}
	\end{exampleblock}
	\subsubsection{Optics}
	\weaponmod{Red Dot Sight}{A simple 1x scope with good eye relief, barely obstructing peripheral vision.}{Upper Rail}{cr 5}{0,15 kg}
	\weaponmod{Holographic Sight}{A non-magnifying 1x sight that is only projected when the character makes an Aim action. Only takes up minimal space on the rail it is mounted, allowing for another item to be mounted without taking this sight off.}{Upper Rail}{cr 7}{0,2 kg}
	\weaponmod{Flip Scope}{A 3x magnifier to be used in conjunction with a non-magnifying sight.}{Upper Rail}{cr 7}{0,32 kg}
	\weaponmod{AOG (Advanced Optical Gunsight)}{A common, analog 4x combat scope.}{Upper Rail}{cr 12}{0,35 kg}
	\weaponmod{TEOG (Tactical Electronic Optical Gunsight)}{A common variable 4-6x combat scope. Due to using electronic magnification it is vulnerable to EMP.}{Upper Rail}{cr 32}{0,38 kg}
	\weaponmod{LoRa Sight}{An 8x scope - the cheapest long range sight but usually absolutely sufficient.}{Upper Rail}{cr 16}{0,4 kg}
	\weaponmod{LS-Marksman Scope}{A massive 14x scope used for the longest ranges.}{Upper Rail}{cr 28}{0,42 kg}
	\weaponmod{OMS (Oculus Marksman System)}{A variable 8-14x electronic scope. Like other electronic magnifiers it is vulnerable to EMP.}{Upper Rail}{cr 51}{0,43 kg}
	\weaponmod{TS-CQC Gunsight}{A big non-magnifying thermal imaging sight with a sleek profile created for CQC.}{Upper Rail}{cr 42}{0,52 kg}
	\weaponmod{TS-BR Gunsight}{A 5x battle rifle scope with thermal imaging capabilities.}{Upper Rail}{cr 68}{0,67 kg}
	\weaponmod{TS-M Gunsight}{A 10x marksman scope with thermal imaging capabilities.}{Upper Rail}{cr 78}{0,67 kg}
	\weaponmod{Canted Irons}{A 45-degree offset rail mount is added to the top of the weapon for the use of a secondary Ironsight/Optic/Light.}{-}{cr 8}{0,1 kg}
	\subsubsection{Lights}
	\weaponmod{Laser Module}{Gives a +5 bonus to hit when not using aim actions. A target spotting the dot with a -10 Perception test cannot be surprised.}{Any rail}{cr 14}{0,1 kg}
	\weaponmod{Infrared Laser Module}{Works like a laser module but it can only be seen with thermal imaging.}{Any rail}{cr 28}{0,2 kg}
	\weaponmod{Flashlight}{A flashlight is attached to the weapon, able to light wherever the wielder is aiming.}{Any rail}{cr 6}{0,26 kg}
	\subsubsection{Muzzles}
	\weaponmod{Muzzle Brake}{Reduces recoil, thereby halving penalties from Burst actions.}{Muzzle}{cr 20}{0,2 kg}
	\weaponmod{Flash Suppressor}{Reduces muzzle flash, inferring a -30 penalty to visual perception checks to spot the weapon firing.}{Muzzle}{cr 22}{0,2 kg}
	\weaponmod{Sound Suppressor}{Reduces both noise and muzzle flash, granting a -30 penalty to all visual perception checks to spot the weapon firing and -10 to hearing based tests; can be combined with cold load ammunition}{Muzzle}{cr 28}{0,2 kg}
	\weaponmod{Shotgun choke, wide}{Reduces pellet spread on shotguns somewhat. Scatter rule only gives a hit bonus from normal range onward. Range is increased by 50\%.}{Muzzle}{cr 12}{0,2 kg}
	\weaponmod{Shotgun choke, narrow}{Reduces pellet spread on shotguns a lot. Scatter rule only gives a hit bonus from long range onward. Range is increased by 100\%.}{Muzzle}{cr 12}{0,2 kg}
	\subsubsection{Underslung Weapons}
	\weaponmod{skeleton key}{Adds an underslung MS shotgun with half range. Due to increased weight at the front this infers a -5 to hit when using aim actions without a rest.}{Lower Rail}{cr 28}{2,8 kg}
	\weaponmod{underslung "Thumper" CQC Grenade Launcher}{Adds an underslung "Thumper" CQC Grenade Launcher with half range. Due to increased weight at the front this infers a -5 to hit when using aim actions without a rest.}{Lower Rail}{cr 70}{3,2 kg}
	\subsubsection{Braces / Grips}
	\weaponmod{Angled Grip}{A fast-pull grip that grants +2 initiative when using both hands and no rest.}{Lower Rail}{cr 8}{0,1 kg}
	\weaponmod{Pistol Grip}{A stable grip that increases aim bonus by 5 when using both hands and no rest.}{Lower Rail}{cr 8}{0,1 kg}
	\weaponmod{Bipod/Tripod}{A stable rest that increases aim bonus by 10 when deployed. A bipod is short and to be used over cover or while prone. Tripods are large and to be used while standing.}{Lower Rail}{cr 10}{0,15 kg}
	\subsubsection{Barrel}
	\weaponmod{Extended barrel}{A longer barrel that increases optimum range and armor penetration by 25\%. Such a long weapon may be difficult to use in confined spaces.}{Barrel}{cr 23}{0,2 kg}
	\weaponmod{Heavy Barrel}{A heavy, more stable barrel. It halves penalties from shooting while on the move but decreases aim bonus by 10 when not using a rest.}{Barrel}{cr 11}{0,2 kg}
	\subsubsection{Ammunition}
	\weaponmod{Magazine}{A simple magazine for a ballistic weapon. It holds ammunition in the gun.}{Ballistic Magazine}{cr 12}{-}
	\weaponmod{Extended-Mag/Belt}{A larger magazine that doubles mag size but is more prone to error, causing jams on 96 and above.}{Ballistic Magazine}{cr 26}{-}
	\weaponmod{Drum-Mag}{A massive spiral magazine that triples mag size but jams on 96+ and also doesn't fit in normal mag pouches, therefore need to be carried in backpacks.}{Ballistic Magazine}{cr 34}{-}
	\weaponmod{Dual-Mag}{Taped magazines make swapping from one to the other take half as long, however it doesn't fit in mag pouches anymore. Can easily be improvised with 2 magazines and some duct tape.}{Ballistic Magazine}{-}{-}
	\weaponmod{Shell Holder}{A clip attached to a rail holding up to 8 shotgun shells. Very useful for special ammunition.}{Any Rail}{cr 2}{-}
	\weaponmod{Bolt Holder}{A container holding up to 8 bolts attached below a crossbow.}{Core}{cr 3}{-}
	\subsubsection{Misc}
	\weaponmod{Camouflage Paint}{If the pattern matches the environment, grants a -20 penalty to visually perceive the weapon. However if the pattern doesn't match, it grants a +5 to visually perceive the weapon instead.}{Paint}{cr 3}{0 kg}
	\weaponmod{Ghillie Cover}{If the pattern matches the environment, grants a -30 penalty to visually perceive the weapon. However if the pattern doesn't match, it grants a +10 to visually perceive the weapon instead.\\
	Unlike with camouflage paint patterns only exist for desert and forest.}{Paint}{cr 4}{0,15 kg}
	\subsubsection{Core}
	\weaponmod{Offload Cycler}{A technological marvel increasing a weapon's fire rate by 50\%, rounded down, if it already has a fire rate of 2 or more.}{Core}{80\%}{0,9 kg}
	\weaponmod{Multibarrel}{Adds an additional barrel feeding from the same magazine to double the amount of hits and ammo spent at an additional -10 penalty to hit. Only works if the weapon has a capacity of at least 2.}{Core}{60\%}{0,55 kg}
	\weaponmod{Heatsink}{A heat sink removing the drawbacks from the Adjustable rule. It increases the weapon's weight by 20\%.}{Core}{40\%}{20\%}
	\weaponmod{Backblast refunneling}{It halves the Backblast range to increase the weapon's range by 50\%. The additional rumble gives a penalty equal to half of the user's strength difference to 70.}{Core}{60\%}{0,4 kg}
	\weaponmod{Gim-barrel}{A self-stabilizing barrel halves penalties from shooting while moving as well as Burst actions. It doubles the weapon's weight and decreases aim bonus by 5 when not using a rest.}{Core, Barrel}{80\%}{100\%}
	\weaponmod{Biocoding}{A trigger lock reading biometric data of the user. The weapon can only be used when wielded by a user who was registered during building of the weapon. It cannot be removed or reprogrammed without destroying the weapon.}{none}{cr 20}{0,24 kg}
	\weaponmod{Vehicle Lock-on}{Adds vehicle lock-on to a Launcher or Heavy weapon; grants +30 to hitting vehicles and powered armor when taking at least one round to aim. Flares don't disrupt targeting but static smoke will.}{Core}{80\%}{3,4 kg}
	\weaponmod{Heat Seeker}{Adds heat-based targeting assistance systems, thereby granting +15 to shoot targets warmer than their surroundings but -15 to shoot targets colder than their surroundings.}{Core}{cr 280}{2,3 kg}
	\weaponmod{Energy Shield}{Adds a directional PES that covers the user's head and body. Covers the whole user instead if used with a tripod.\\
		Armor: 15 / Threshold: 9}{Core}{cr 180}{3,8 kg}

	\subsection{Ammunition}
	In the following section ammo types are given in this format:\\
	First, in bold, there is the type designation. This is little more than an identifier.\\
	Secondly after the colon you find the effect. These are all changes this type of ammunition has as opposed to the basic weapon profile.\\
	The price is the price per box off ammunition; every box contains an amount of ammunition equal to the value given at "Unit of sale". For ballistic ammo a single unit is one bullet, for others it is one full load of the weapon.\\
	Weight and bulk are given in the weight that one "standard magazine" - as used in storage capacities - weighs.
%	Pistols
	\subsubsection{7.2mm}
	\ammo{FMJ}{-}{cr 2}{30}{4g}{40}
	\ammo{AP}{-1 dmg, +4 AP}{cr 3}{30}{4g}{40}
	\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 4}{30}{4g}{40}
	\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 6}{30}{4g}{40}
	\ammo{JSP}{+2 dmg, -3 AP}{cr 3}{30}{4g}{40}
	\ammo{JHP}{+4 dmg, -6 AP}{cr 4}{30}{4g}{40}
	\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 6}{30}{4g}{40}
	\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 3}{30}{4g}{40}
	\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{4g}{40}
	\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{4g}{40}
	\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{30}{4g}{40}
	\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 3}{30}{4g}{40}
	\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 4}{30}{4g}{40}
	\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 2}{30}{4g}{40}
	\subsubsection{11.8x45mm}
	\ammo{FMJ}{-}{cr 3}{20}{22g}{40}
	\ammo{AP}{-1 dmg, +4 AP}{cr 5}{20}{22g}{40}
	\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 6}{20}{22g}{40}
	\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 9}{20}{22g}{40}
	\ammo{JSP}{+2 dmg, -3 AP}{cr 5}{20}{22g}{40}
	\ammo{JHP}{+4 dmg, -6 AP}{cr 6}{20}{22g}{40}
	\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 9}{20}{22g}{40}
	\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 5}{20}{22g}{40}
	\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 6}{20}{22g}{40}
	\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{20}{22g}{40}
	\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 9}{20}{22g}{40}
	\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 5}{20}{22g}{40}
	\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 6}{20}{22g}{40}
	\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 3}{20}{22g}{40}
	
%	Rifles
	\subsubsection{6.3mm}
	\ammo{FMJ}{-}{cr 2}{30}{8.6g}{30}
	\ammo{AP}{-1 dmg, +4 AP}{cr 3}{30}{8.6g}{30}
	\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 4}{30}{8.6g}{30}
	\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 6}{30}{8.6g}{30}
	\ammo{JSP}{+2 dmg, -3 AP}{cr 3}{30}{8.6g}{30}
	\ammo{JHP}{+4 dmg, -6 AP}{cr 4}{30}{8.6g}{30}
	\ammo{Shield Breaker}{-3 dmg, Disrupt}{cr 5}{30}{8.6g}{30}
	\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 6}{30}{8.6g}{30}
	\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 3}{30}{8.6g}{30}
	\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{8.6g}{30}
	\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{8.6g}{30}
	\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{30}{8.6g}{30}
	\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 3}{30}{8.6g}{30}
	\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 4}{30}{8.6g}{30}
	\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 2}{30}{8.6g}{30}
	\subsubsection{11.8x112mm}
	\ammo{FMJ}{-}{cr 4}{20}{50g}{5}
	\ammo{AP}{-1 dmg, +4 AP}{cr 6}{20}{50g}{5}
	\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 8}{20}{50g}{5}
	\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 12}{20}{50g}{5}
	\ammo{JSP}{+2 dmg, -3 AP}{cr 6}{20}{50g}{5}
	\ammo{JHP}{+4 dmg, -6 AP}{cr 8}{20}{50g}{5}
	\ammo{Shield Breaker}{-3 dmg, Disrupt}{cr 8}{20}{50g}{5}
	\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 12}{20}{50g}{5}
	\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{20}{50g}{5}
	\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 8}{20}{50g}{5}
	\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 8}{20}{50g}{5}
	\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 12}{20}{50g}{5}
	\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 6}{20}{50g}{5}
	\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 8}{20}{50g}{5}
	\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 4}{20}{50g}{5}
	\subsubsection{15x132mm}
	\ammo{FMJ}{-}{cr 5}{5}{85g}{4}
	\ammo{AP}{-1 dmg, +4 AP}{cr 8}{5}{85g}{4}
	\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 10}{5}{85g}{4}
	\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 15}{5}{85g}{4}
	\ammo{JSP}{+2 dmg, -3 AP}{cr 8}{5}{85g}{4}
	\ammo{JHP}{+4 dmg, -6 AP}{cr 10}{5}{85g}{4}
	\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 15}{5}{85g}{4}
	\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 8}{5}{85g}{4}
	\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 10}{5}{85g}{4}
	\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 10}{5}{85g}{4}
	\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 15}{5}{85g}{4}
	\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 8}{5}{85g}{4}
	\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 10}{5}{85g}{4}
	\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 5}{5}{85g}{4}
	
%	Shotgun
	\subsubsection{12gauge}
	\ammo{Buckshot}{-}{cr 3}{24}{42g}{8}
	\ammo{Birdshot}{halves damage, ignores all negative size modifiers}{cr 2}{24}{42g}{8}
	\ammo{Incendiary}{-2 dmg, -4 AP, ignites flammable materials hit}{cr 3}{24}{42g}{8}
	\ammo{Breaching Round}{+3 dmg, +4 AP, halved range}{cr 5}{24}{42g}{8}
	\ammo{Slug}{+2 AP, removes Scatter, doubles range}{cr 3}{24}{42g}{8}
	\ammo{Fragmentation Slug}{removes Scatter but adds Blast (2) rule, doubles range}{cr 6}{24}{42g}{8}
	\ammo{Incendiary Slug}{+1 AP, removes Scatter, doubles range, ignites flammable objects hit}{cr 4}{24}{42g}{8}
	\ammo{EMP Slug}{-2 dmg, EMP, removes Scatter, doubles range}{cr 9}{24}{42g}{8}
	\ammo{Rubber Slug}{-2 dmg, -6 AP, removes Scatter, doubles range, Stun (2)}{cr 3}{24}{42g}{8}
	
%	Fuel Tank
	\subsubsection{Small Fuel Tanks}
	\ammo{Napalm}{ignites flammable surfaces}{cr 32}{1}{10kg}{}
	\ammo{White Phosphorus}{halves range, burns for a D5 minutes, ignites flammable surfaces and sticks even to non-flammable ones}{cr 64}{1}{20kg}{}
	\ammo{Water}{1 dmg, 0 AP, Trauma, Stun (*the original amount of damage dice)}{cr 8}{1}{13kg}{}
	\subsubsection{Medium Fuel Tanks}
	\ammo{Napalm}{ignites flammable surfaces}{cr 61}{1}{20kg}{}
	\ammo{White Phosphorus}{halves range, burns for a D5 minutes, ignites flammable surfaces and sticks even to non-flammable ones}{cr 122}{1}{40kg}{}
	\ammo{Water}{1 dmg, 0 AP, Trauma, Stun (*the original amount of damage dice)}{cr 17}{1}{25kg}{}
	\subsubsection{Large Fuel Tanks}
	\ammo{Napalm}{ignites flammable surfaces}{cr 150}{1}{50kg}{}
	\ammo{White Phosphorus}{halves range, burns for a D5 minutes, ignites flammable surfaces and sticks even to non-flammable ones}{cr 300}{1}{100kg}{}
	\ammo{Water}{1 dmg, 0 AP, Trauma, Stun (*the original amount of damage dice)}{cr 32}{1}{62,5kg}{}
	
%	Fuel Cells
	\subsubsection{Small Fuel Cells}
	\ammo{Standard Issue}{-}{cr 9}{1}{250g}{2}
	\ammo{Unstable}{On a hit roll above 95 causes the weapon's damage with Blast (1) around the shooter.}{cr 5}{1}{250g}{2}
	\subsubsection{Medium Fuel Cells}
	\ammo{Standard Issue}{-}{cr 15}{1}{750g}{1}
	\ammo{Unstable}{On a hit roll above 95 causes the weapon's damage with Blast (1) around the shooter.}{cr 8}{1}{750g}{1}
	\subsubsection{Large Fuel Cells}
	\ammo{Standard Issue}{-}{cr 21}{1}{1.5kg}{0,5}
	\ammo{Unstable}{On a hit roll above 95 causes the weapon's damage with Blast (1) around the shooter.}{cr 11}{1}{1.5kg}{0,5}
	
%	Mass Driver Blocks
	\subsubsection{Small Shard Blocks}
	\ammo{Standard Issue}{-}{cr 2}{1}{300g}{1}
	\ammo{Crude}{-50\% mag size, jams on 91 and above}{cr 1}{2}{300g}{1}
	\subsubsection{Large Shard Blocks}
	\ammo{Standard Issue}{-}{cr 5}{1}{1.8kg}{0,5}
	\ammo{Crude}{-50\% mag size, jams on 91 and above}{cr 2}{2}{1.8kg}{0,5}
	\subsubsection{Vehicle Shard Blocks}
	\ammo{Standard Issue}{-}{cr 11}{1}{3.2kg}{0,2}
	\ammo{Crude}{-50\% mag size, jams on 91 and above}{cr 5}{2}{3.2kg}{0,2}
	
%	Grenades
	\subsubsection{20mm grenades}
	\ammo{Fragmentation}{2D10+2 | 2 AP | Blast (6)}{cr 60}{1}{120g}{0,5}
	\ammo{High Explosive}{2D10+6 | 5 AP | Blast (2)}{cr 60}{1}{120g}{0,5}
	\ammo{Thermobaric}{3D10 | 2 AP | Blast (10) | heat-based, ignores all cover and non-vacuum-sealed or natural armor}{cr 96}{1}{120g}{0,5}
	\ammo{Incendiary}{D10+2 | 0 AP | Blast (8) | ignites all flammable objects in the radius}{cr 60}{1}{120g}{0,5}
	\ammo{Buckshot Canister}{2D10+3 | 5 AP | Scatter}{cr 75}{1}{120g}{0,5}
	\ammo{Slug}{2D5+8 | 8 AP}{cr 75}{1}{120g}{0,5}
	\ammo{Smoke}{0 | 0 AP | Blast (8), Smoke}{cr 45}{1}{120g}{0,5}
	\ammo{Flashbang}{0 | 0 AP | Blast (12), Flash}{cr 45}{1}{120g}{0,5}
	\ammo{EMP}{0 | 0 AP | Blast (6), EMP}{cr 80}{1}{120g}{0,5}
	\ammo{Tear Gas}{0 | 0 AP | Blast (6), Smoke, Stun (0), ignores cover and non-vacuum-sealed armor, Stun is applied every round in the Smoke}{cr 45}{1}{120g}{0,5}
	\ammo{Rubber Slug}{1D10+3 | 2 AP | Stun (5), hits to the head cause 2D5 initiative loss}{cr 50}{1}{120g}{0,5}
	\ammo{Riot Foam}{0 | 0 AP | Blast (12), Sticky}{cr 20}{1}{120g}{0,5}
	\ammo{Signal Smoke}{0 | 0 AP | Blast (4) | a smoke spewer to signal allies; comes in various colors}{cr 38}{1}{120g}{0,5}
	\ammo{Parachute Flare}{D5 | 0 AP | a signal flare that burns for 3 minutes and falls at 1 meter per 3 seconds (or 1 round)}{cr 40}{1}{120g}{0,5}
	\ammo{Infrared Illuminator}{1 | 0 AP | a large chemlight that emits infrared light in a very large area}{cr 42}{1}{120g}{0,5}
	\subsubsection{40mm grenades}
	\ammo{Fragmentation}{2D10+7 | 2 AP | Blast (9)}{cr 78}{1}{230g}{1}
	\ammo{High Explosive}{3D10+6 | 5 AP | Blast (3)}{cr 78}{1}{230g}{1}
	\ammo{Thermobaric}{4D10 | 2 AP | Blast (15) | heat-based, ignores all cover and non-vacuum-sealed armor}{cr 125}{1}{230g}{1}
	\ammo{Incendiary}{D10+3 | 0 AP | Blast (12) | ignites all flammable objects in the radius}{cr 78}{1}{230g}{1}
	\ammo{Buckshot Canister}{3D10+3 | 5 AP | Scatter}{cr 98}{1}{230g}{1}
	\ammo{Slug}{2D10+9 | 9 AP}{cr 98}{1}{230g}{1}
	\ammo{Smoke}{0 | 0 AP | Blast (12), Smoke}{cr 59}{1}{230g}{1}
	\ammo{Flashbang}{0 | 0 AP | Blast (18), Flash}{cr 59}{1}{230g}{1}
	\ammo{EMP}{0 | 0 AP | Blast (9), EMP}{cr 104}{1}{230g}{1}
	\ammo{Tear Gas}{0 | 0 AP | Blast (8), Smoke, Stun (0), ignores cover and non-vacuum-sealed armor, Stun is applied every round in the Smoke}{cr 59}{1}{230g}{1}
	\ammo{Rubber Slug}{2D10+3 | 2 AP | Stun (7), hits to the head cause 2D10 initiative loss}{cr 65}{1}{230g}{1}
	\ammo{Signal Smoke}{0 | 0 AP | Blast (4) | a smoke spewer to signal allies that lasts for a few minutes; comes in various colors}{cr 49}{1}{230g}{1}
	\ammo{Parachute Flare}{D5+1 | 0 AP | a signal flare that burns for 5 minutes and falls at 1 meter per 3 seconds (or 1 round)}{cr 52}{1}{230g}{1}
	\ammo{Thermite}{6D10+10 | 25 AP | Blast (3) | takes two rounds to get going, then burns for one minute dealing its damage every round; sticks to rough surfaces}{cr 156}{1}{230g}{1}
	
%	Rockets
	\subsubsection{Micro Missiles}
	\ammo{Fragmentation}{-}{cr 84}{4}{1kg}{0,5}
	\ammo{High Explosive}{-1D10 dmg | +8 AP}{cr 88}{4}{1kg}{0,5}
	\ammo{Incendiary}{-3 dmg | -3 AP | ignites flammable objects}{cr 76}{4}{1kg}{0,5}
	\subsubsection{Small RPGs}
	\ammo{HEAT}{4D10+5 dmg | 6 AP | Blast (5)}{cr 124}{1}{2kg}{0,5}
	\ammo{High Explosive}{4D10+2 dmg | 3 AP | Blast (6)}{cr 99}{1}{2kg}{0,5}
	\ammo{Fragmentation}{3D10+8 dmg | 2 AP | Blast (8)}{cr 99}{1}{2kg}{0,5}
	\ammo{Incendiary}{2D10+5 dmg | 2 AP | Blast (6) | ignites flammable objects}{cr 112}{1}{2kg}{0,5}
	\ammo{Incendiary Fragmentation}{3D10+5 dmg | 2 AP | Blast (8) | ignites flammable objects}{cr 134}{1}{2kg}{0,5}
	\ammo{Thermobaric}{4D10+8 dmg | 3 AP | Blast (12) | heat-based, ignores all cover and non-vacuum-sealed armor}{cr 201}{1}{2kg}{0,5}
	\ammo{Thermite}{6D10+10 | 25 AP | Blast (4) | takes two rounds to get going, then burns for one minute dealing its damage every round; sticks to rough surfaces}{cr 179}{1}{2kg}{0,5}
	\ammo{Kinetic Penetrator}{4D10+5 dmg | 14 AP}{cr 201}{1}{2kg}{0,5}
	\subsubsection{Large RPGs}
	\ammo{HEAT}{4D10+6 dmg | 8 AP | Blast (6)}{cr 168}{1}{3.5kg}{0,25}
	\ammo{High Explosive}{4D10+4 dmg | 5 AP | Blast (8)}{cr 134}{1}{3.5kg}{0,25}
	\ammo{Fragmentation}{3D10+11 dmg | 3 AP | Blast (10)}{cr 134}{1}{3.5kg}{0,25}
	\ammo{Incendiary}{2D10+8 dmg | 2 AP | Blast (8) | ignites flammable objects}{cr 151}{1}{3.5kg}{0,25}
	\ammo{Incendiary Fragmentation}{3D10+8 dmg | 3 AP | Blast (10) | ignites flammable objects}{cr 181}{1}{3.5kg}{0,25}
	\ammo{Thermobaric}{5D10+10 dmg | 5 AP | Blast (18) | heat-based, ignores all cover and non-vacuum-sealed armor}{cr 272}{1}{3.5kg}{0,25}
	\ammo{Thermite}{6D10+10 | 25 AP | Blast (6) | takes two rounds to get going, then burns for one minute dealing its damage every round; sticks to rough surfaces}{cr 242}{1}{3.5kg}{0,25}
	\ammo{Kinetic Penetrator}{4D10+8 dmg | 18 AP}{cr 272}{1}{3.5kg}{0,25}
	
%	Arrows / Bolts
	\subsubsection{Arrows}
	\ammo{Broadhead}{-}{cr 1}{25}{30g}{10}
	\ammo{AP}{-1 dmg, +3 AP}{cr 1}{25}{30g}{10}
	\ammo{Shield Breaker}{-1 dmg, Disrupt}{cr 2}{25}{30g}{10}
	\ammo{Syringer}{-3 dmg, +1 AP, contains an empty vial to be filled with poisons or other injections that are released into a biological target when hit}{cr 3}{25}{30g}{10}
	\ammo{Grapple}{-4 dmg, 0 AP, half range; the mechnized grapple attaches to a rope and holds on most surfaces but e.g. very sturdy metals or fragile materials like glass}{cr 6}{1}{30g}{10}
	\subsubsection{Bolts}
	\ammo{Broadhead}{-}{cr 1}{25}{30g}{10}
	\ammo{AP}{-1 dmg, +3 AP}{cr 1}{25}{30g}{10}
	\ammo{Shield Breaker}{-1 dmg, Disrupt}{cr 2}{25}{30g}{10}
	\ammo{Syringer}{-3 dmg, +1 AP, contains an empty vial to be filled with poisons or other injections that are released into a biological target when hit}{cr 3}{25}{30g}{10}
	\ammo{Grapple}{-4 dmg, 0 AP, half range; the mechnized grapple attaches to a rope and holds on most surfaces but e.g. very sturdy metals or fragile materials like glass}{cr 6}{1}{30g}{10}
	
%	\pagebreak
	\section{Melee}
	\subsection{Building \emph{your} weapon}
	Melee weapons are not set in stone but created from various components, allowing for ideal customization.\\
	A melee weapon needs a grip. Swords, knives and whips have \emph{hilts}, while hammers, axes and spears have \emph{shafts}.\\
	The weapon point is the second component. Swords, knives and spears have \emph{blades}; axes and hammers have \emph{heads} and \emph{whips} have their own category.\\
	Lastly every melee weapon may also have a \emph{core} component. These are not required but add additional functionality to the weapon.
	\subsection{Components}
	\subsubsection{Hilts}
	\meleecomponent{Simple hilt}{A simple sword hilt. Very versatile.}{One-handed; +5 to combat rolls}{0,2 kg}{cr 3}{}
	\meleecomponent{Push hilt}{A hilt vertical to the blade. Biomechanically inferior to a normal hilt in terms of reach and leverage, yet somehow preferred by some.}{One-handed; weapon uses Melee Combat Training (Striking) instead}{0,1 kg}{cr 4}{}
	\meleecomponent{Duelist hilt}{An offensively minded hilt at a slight tilt, made to make disarming an opponent much easier.}{One-handed +15 to disarms}{0,2 kg}{cr 7}{}
	\meleecomponent{Caged hilt}{Shielding the sword wielding hand in some way is an old idea but, like many old ideas, still holds merit this day, so this handle was fitted with a protective basket.}{One-handed; Disarming the wielder is at a -20; The wielding hand (location: arm) has +3 armor}{0,4 kg}{cr 10}{}
	\meleecomponent{Ergonomic hilt}{A handle fitting the wielder's hand very closely and therefore allowing the user to get a much better feel for the weapon's point.}{One-handed; Binding grants 50\% more bonus, rounded down}{0,2 kg}{cr 12}{}
	\meleecomponent{Simple long hilt}{A generic two-handed sword hilt offering more leverage than a one-handed hilt.}{Two-handed; +5 to combat rolls}{0,3 kg}{cr 4}{}
	\meleecomponent{Giant Hilt}{A massive sword hilt. This has no utility for humans and exists more for smiths to boast.}{Oversized}{3 kg}{cr 35}{}
	\subsubsection{Shafts}
	\meleecomponent{Short shaft}{A generic short shaft that can build the basis for a spear, hammer or axe.}{One-handed}{0,3 kg}{cr 4}{}
	\meleecomponent{Long shaft}{A shaft perfect for long spears.}{Two-handed}{0,5 kg}{cr 5}{}
	\meleecomponent{Twin shaft}{A double-ended spear shaft allowing for two heads to be mounted. Not as effective individually but some people like the versatility.}{Two-handed; -1 damage; allows to add a second weapon point}{0,5 kg}{cr 11}{}
	\meleecomponent{Rifle}{A weapon mount for the tip of a gun. While a little bit outdated, making an improvised spear can be much more effective than using the knife on its own.}{Two-handed; -5 to melee combat rolls and aim actions with the rifle}{-}{-/-}{}
	\subsubsection{Blades}
	\meleecomponent{No blade}{Generally speaking a blade gives great advantages. Sometimes however a blade is simply not available but a stick is still a massive upgrade over fists.}{weapon becomes club}{0 kg}{cr 0}{}
	\meleecomponent{Knife blade}{Short, stiff blade. Good penetration, can cut if necessary.}{Piercing}{0,2 kg}{cr 7}{}
	\meleecomponent{Sword blade}{A long blade that cuts and stabs well.}{+3 damage}{0,9 kg}{cr 10}{}
	\meleecomponent{Inverse blade}{A curved swordblade with its edge on the inside. Edge alignment is more difficult but cuts become more devastating.}{Add Dex to melee damage bonus calculation}{0,9 kg}{cr 13}{}
	\meleecomponent{Plasma cutter}{A knife-sized blade consisting of finely shaped plasma. Cuts through heat much more than force and thereby is easier to use by weaker people.}{+6 damage; halve Melee Damage Bonus}{0,6 kg}{cr 17}{}
	\meleecomponent{Chain blade}{A high-power, rotating chainsaw functioning as a sword blade. Why someone invented this, no one knows.}{Tearing}{1,2 kg}{cr 23}{}
	\meleecomponent{Mono blade}{Advertised as a near mono-molecular edge, this is the sharpest knife blade built yet.}{Piercing}{1 kg}{cr 27}{}
	\subsubsection{Whips}
	\meleecomponent{Bull whip}{Leather, woven to a rope, making a bad but dirt cheap weapon.}{Flexible}{0,7 kg}{cr 2}{}
	\meleecomponent{Thorn whip}{Small thorns along the whip increase the damage against tissue but even thinner armor or thicker clothing will stop the weapon.}{Flexible, Tearing}{0,6 kg}{cr 12}{}
	\meleecomponent{Shock whip}{A difficult piece of equipment to create: coils create a strong electric field while staying flexible enough to whip around and not frying itself.}{Flexible, Shocking}{0,8 kg}{cr 27}{}
	\subsubsection{Heads}
	\meleecomponent{No head}{While a designated weapon point is generally superior to none, no weapon head is superior to no weapon.}{None}{0 kg}{cr 0}{}
	\meleecomponent{Hammer head}{A blunt implement originally designed as a tool, later used in a refined form to defeat armor.}{Trauma}{0,8 kg}{cr 8}{}
	\meleecomponent{Axe head}{A very top heavy blade. Good at splitting moreso than cutting.}{+3 damage}{0,7 kg}{cr 9}{}
	\meleecomponent{Pick head}{The head on a warpick is designed to defeat armor by breaking through weaker spots. Still works good today.}{Piercing}{0,7 kg}{cr 11}{}
	\meleecomponent{Spiked head}{Be it spiked mauls or barbed wire around a stick - damage to tissue will be significant.}{Tearing}{0,8 kg}{cr 11}{}
	\subsubsection{Core}
	\meleecomponent{Cup holder}{A cup holder for your weapon. Why? No reason, really.}{Adds a cup holder}{0,1 kg}{cr 2}{}
	\meleecomponent{Bipod}{Legend has it that bipods on knives allow stabbing helicopters to death.}{+2 to intimidation if the weapon is visible}{0,8 kg}{cr 6}{}
	\meleecomponent{Dripper}{Stiletto knives delivering toxins are as infamous as they are rare. However some shady individuals do use such weaponry.}{Adds an injector to the weapon the applies a prepared dose of an injection type chemical to the target on hit.}{0,7 kg}{cr 14}{Blade}
	\meleecomponent{Shock Wire}{An energy source is added inside the weapon, electrifying it. On an already electrical weapon it is possible to direct the electrical field in a manner that will disrupt energy shielding.}{Shocking; If the weapon is already Shocking, it gains Disrupt.}{0,8 kg}{cr 22}{}
	\meleecomponent{EMP field}{Coils within the weapon emit an electromagnetic field strong enough to interrupt electronic devices.}{EMP}{0,8 kg}{cr 22}{}
	\meleecomponent{Shotgun}{A single shot 12gauge launcher attached to a hammerhead. It might as well be an improvised explosive device and is as dangerous for the target as for the user and weapon.}{Add a single-shot shotgun to the head, increasing damage by 2D10 for one hit. That hit can only be a single or sure strike. Takes 5 actions to reload.}{0,6 kg}{cr 23}{Hammer}
	\meleecomponent{Ripper Field Generator}{Lovingly dubbed "Ripper Field" by mobsters, this projected force field tears at otherwise stable matter, making it very easy to cut through tough material. The field itself is not very stable however and can only be kept alive for a few seconds.}{When activated as a free action, the weapon gains +4 AP for 4 rounds. Takes a small fuel cell and 8 actions to recharge.}{0,8 kg}{cr 28}{Blade}
	\meleecomponent{IED}{An IED on a stick, what do you expect? Quite dangerous, quite destructive.}{Improvised; An attack causes an explosion equal to a 40mm HE grenade, generally destroying the weapon.}{0,2 kg}{cr 30}{}
	\meleecomponent{Rocket booster}{Everyone understands that a faster weapon point is more destructive. Since too high speeds make edge alignment and controlling the weapon one-handed nearly impossible, it's only safe to use on large blunt weapons.}{Allows the wielder to forego a second action to gain D10 additional damage.}{1,1 kg}{cr 32}{Two-handed axe or hammer}
	
	\section{Armor}
	\subsection{Casual wear}
	This section contains clothing that is slightly armored but looks inconspicuous.\\ %*TODO: adjust format!*
	\begin{tabularx}{\textwidth}{|l|r|r|r|r|r|l|r|r|}
		\hline
		Name & Head & Chest & Arms & Legs & Mods & Special & Price & Weight \\ \hline
		Biker helmet & 3 & 0 & 0 & 0 & 2 & -5 to sight, +5 to Drive(Bike) & cr 26 & 1,5kg \\ \hline
		armored suit & 0 & 4 & 2 & 3 & 1 & inconspicuous & cr 79 & 2,0kg \\ \hline
		Tough coat & 0 & 2 & 1 & 1 & 0 & & cr 35 & 2,0kg \\ \hline
		Flak jacket & 0 & 5 & 5 & 1 & 1 & inconspicuous & cr 96 & 2,0kg \\ \hline
		Tough pants & 0 & 0 & 0 & 2 & 0 & & cr 18 & 1,5kg \\ \hline
	\end{tabularx}
	\subsection{Helmets}
	\begin{tabularx}{\textwidth}{|l|r|r|r|r|r|l|r|r|}
		\hline
		Name & Head & Chest & Arms & Legs & Mods & Special & Price & Weight \\ \hline
		Blast helmet & 14 & 0 & 0 & 0 & 1 & -10 to sight-based perception & cr 123 & 8,0kg \\ \hline
		Improvised helmet & 5 & 0 & 0 & 0 & 1 & -5 Ag, Improvised & cr 44 & 3,0kg \\ \hline
		Banshee helmet & 6 & 1 & 0 & 0 & 2 & inbuilt spotter target assist system & cr 61 & 2,0kg \\ \hline
		Flak helmet & 8 & 0 & 0 & 0 & 1 & -5 to sight-based perception & cr 70 & 1,5kg \\ \hline
		Ghost helmet & 6 & 0 & 0 & 0 & 2 & *TODO* & cr 53 & 5,0kg \\ \hline
		EVA helmet & 5 & 0 & 0 & 0 & 3 & vac-sealed & cr 44 & 2,0kg \\ \hline
		Argus helmet & 10 & 0 & 0 & 0 & 2 & -10 to sight-based perception, inbuilt explosives detection assistant & cr 88 & 9,0kg \\ \hline
	\end{tabularx}
	\subsection{Body Armor}
	\begin{tabularx}{\textwidth}{|l|r|r|r|r|r|l|r|r|}
		\hline
		Name & Head & Chest & Arms & Legs & Mods & Special & Price & Weight \\ \hline
		EOD armor & 3 & 20 & 18 & 2 & 2 & -2 movement speed, -10 Ag, -10 to Dex and shooting tests & cr 376 & 36,0kg \\ \hline
		Banshee suit & 0 & 10 & 7 & 0 & 2 & inbuilt climbing gear & cr 149 & 4,0kg \\ \hline
		Improvised vest & 0 & 9 & 0 & 0 & 1 & -5 Ag, Improvised & cr 79 & 3,5kg \\ \hline
		Stab Vest & 0 & 9 & 0 & 0 & 1 & -5 Ag, immune to piercing rule & cr 79 & 3,5kg \\ \hline
		Flak Vest & 0 & 12 & 0 & 0 & 1 & -5 Ag & cr 105 & 4,0kg \\ \hline
		Ghost Suit & 0 & 10 & 7 & 0 & 3 & does not stop a skin-close holoprojector, includes piezo-electric exo frame & cr 149 & 12,0kg \\ \hline
		Node Armor & 0 & 14 & 4 & 0 & 3 & can carry AI, includes piezo-electric exo frame & cr 158 & 14,0kg \\ \hline
		EVA Suit & 0 & 3 & 3 & 3 & 4 & vac-sealed & cr 79 & 2,5kg \\ \hline
	\end{tabularx}
	\subsection{Leg Armor}
	\begin{tabularx}{\textwidth}{|l|r|r|r|r|r|l|r|r|}
		\hline
		Name & Head & Chest & Arms & Legs & Mods & Special & Price & Weight \\ \hline
		Blast Greaves & 0 & 1 & 0 & 18 & 1 & -1 movement speed, -10 Ag & cr 166 & 10,0kg \\ \hline
		Banshee Greaves & 0 & 0 & 0 & 6 & 2 & & cr 53 & 2,0kg \\ \hline
		Flak Greaves & 0 & 0 & 0 & 10 & 2 & -5 Ag & cr 88 & 2,5kg \\ \hline
		Ghost Greaves & 0 & 0 & 0 & 6 & 1 & halves penalties from noise on sneaking & cr 53 & 6,0kg \\ \hline
	\end{tabularx}
	\subsection{Mods}
	\section{PES}
	\section{Strike Suits}
	
	\chapter{Lists}
	\section{Status effects}
	\statuseffect{Blinded}{The character cannot see and suffers according penalties, most notably to Perception and combat. He also cannot Gather Senses if the status effect is only temporary or brand new.}
	\statuseffect{Deafened}{The character cannot hear. She suffers according penalties and can't Gather Senses if the condition is only temporary or brand new.}
	\statuseffect{Frenzied}{The character has entered a vicious rage. She no longer takes penalties from pain and damage aside from complete destruction of body parts. Melee damage bonus from strength is doubled. She will throw herself into combat and needs to make Int checks to distinguish friend from foe. These checks are at a +30 bonus for very close friends and a -30 penalty for completely unknown people.}
	\statuseffect{Nausea}{The character gains exhaustion for every minute of strenuous activity. In addition, on a failed Con check for any strenous action, he starts vomiting, getting Stunned for D5 rounds.}
	\statuseffect{Prone}{The character is granted bonuses and suffers penalties as described in Situational Modifiers. If falling prone was involuntary, she also loses D10 initiative.}
	\statuseffect{Stunned}{The character cannot act except for move with a speed of 1m/s and loses 1 initiative for every combat round he is stunned. Tests to prevent falling over automatically fail.}
	\statuseffect{Unconscious}{The character cannot act at all.}
	
	\section{Skills}
	\label{skilllist}
	\skill{Acrobatics}{Agility}{Acrobatics describes the ability to control one's body. It encompasses moving elegantly, gymnastics, breaking falls and dancing.}
	\skill{Animal Handling}{Charisma}{Animal Handling is any interaction with animals; calming them down, taming and training them.}
	\skill{Appeal}{Charisma}{Appeal encompasses any attempt to charm or convince someone that at least outwardly happens in good blood.}
	\skill{Athletics}{Strength}{Athletics is used for any task built on directing one's strength, be it lifting, pushing, running or jumping.}
	\skill[Advanced]{Brewing}{Intelligence}{Making any sort of alcoholic beverage is considered brewing. All differences between creating beer, wine and whatever else is neglected.}
	\skill[Advanced]{Chemistry}{Intelligence}{Chemistry is necessary for identifying and creating chemicals. It also includes knowledge of recipes and estimation of effects and side effects for unknown recipes.}
	\skill{Climbing}{Strength}{Climbing generally means scaling heights. Holding oneself at the ceiling might be considered climbing as well.}
	\skill{Command}{Charisma}{Command describes military social interactions that feature a clear hierarchy. It also represents knowledge about military leadership and command structure.}
	\skill[Advanced]{Commerce}{Intelligence}{Anything concerned with the exchange of money falls under the Commerce skill. This obviously includes trading but also bribery and extortion.}
	\skill[Advanced]{Computer Operation}{Intelligence}{Computer Operation means using a computer. That technically includes even the simplest tasks but only advanced operations will require a test, such as getting access to files that one should not have access to.}
	\skill[Advanced]{Construction}{Intelligence}{Construction is concerned with creating buildings and understanding buildings; that means probable layouts or weaknesses.}
	\skill[Advanced]{Cryptography}{Intelligence}{Cryptography is the knowledge about en- and deciphering data of any type. If the data was human-readable, a cunning character might identify simple probable cipher algorithms.}
	\skill{Deceive}{Charisma}{Deceiving means telling lies. Making half-truths believable might fall under this skill as well, as per GM discretion.}
	\skill{Dodge}{Agility}{Dodging is physically evading harm. This can be an attack or something more natural like falling objects or sudden vehicles.}
	\skill[Advanced]{Drive: Bike}{Agility}{Drive (Bike) encompasses the knowledge of how motorbikes and similar vehicles work and how to get them to move in a desired direction.}
	\skill[Advanced]{Drive: Boat}{Agility}{Drive (Boat) encompasses the knowledge of how motorboats and similar vehicles work and how to get them to move in a desired direction. Rowboats, canoes and so on might be covered with athletics instead.}
	\skill[Advanced]{Drive: Car}{Agility}{Drive (Car) encompasses the knowledge of how cars and similar vehicles work and how to get them to move in a desired direction.}
	\skill[Advanced]{Drive: Heavy}{Agility}{Drive (Heavy) encompasses the knowledge of how trucks and similar vehicles work and how to get them to move in a desired direction. It also includes knowledge about APCs, IFVs or tanks and other heavy armored vehicles.}
	\skill{Estimate}{Instinct}{Estimation is the ability to guess amounts, weight, size, distance and whatever else might come up; a smith estimating a knife's price might not necessarily need this.}
	\skill{Gambling}{Instinct}{Gambling is betting, card and board games: knowing how to play, knowing how to win, by all means if necessary.}
	\skill[Advanced]{Geography}{Intelligence}{Geography describes the knowledge of the world and its places.}
	\skill[Advanced]{Herbalism}{Intelligence}{Herbalism is knowledge of plants, formal or by experience.}
	\skill{History}{Intelligence}{History is the knowledge of past events. Low values don't necessarily mean no knowledge but might include false information as well.}
	\skill{Interrogation}{Instinct}{Interrogation encompasses asking the right questions as well as reading facial expressions and voice tone to determine truth or lie; also includes understanding the opposition's true meaning.}
	\skill{Intimidation}{Courage}{Intimidation means skillfully threatening others to avoid actually having to go through with the threat.}
	\skill[Advanced]{Law}{Charisma}{Law means the knowledge about rights and also the ability to accuse and defend properly.}
	\skill[Advanced]{Logic}{Intelligence}{Logic is the ability to dissect and combine information rationally and quickly or detect patterns where others do not.}
	\skill[Advanced]{Mechanics}{Dexterity}{Mechanics encompasses the knowledge of how technology works and the skill to fix or even create it.}
	\skill[Advanced]{Medication}{Dexterity}{Medication is the necessary knowledge of anatomy and medical chemicals and the skill of how to apply it, give first aid and do surgery.}
	\skill{Navigation: Air}{Instinct}{Navigation in the air is difficult and relies on good sense of both distance and direction. It may be easier when sun, moon, stars or large landmarks on the ground are visible.}
	\skill{Navigation: Ground}{Instinct}{Navigation on the ground is the most common type of navigation. It helps finding one's way on foot or in earthbound vehicles.}
	\skill{Navigation: Sea}{Instinct}{Navigation on the sea relies on reading maps and a compass. It is possible to make good educated guesses by using celestial bodies as well.}
	\skill[Advanced]{Navigation Space}{Intelligence}{Navigation through the void of space without equipment is almost impossible due to how vast space is. This skill represents finding the shortest and safest path given such instruments.}
	\skill{Navigation: Underground}{Instinct}{Navigating through underground complexes is quite difficult, as there are very few landmarks. It requires good memory or a map and good sense of distance.}
	\skill{Perception}{Instinct}{Perception is essential for noticing small details. Someone properly educated with trained sense of hearing for example might make out the type of gun or ammunition used in a shot from the sound alone.}
	\skill[Advanced]{Philosophy}{Intelligence}{Philosophy is what drives many people in the shadows of neon lights. Existential questions rarely find clear answers but one might come close.}
	\skill[Advanced]{Pilot: Air}{Agility}{Piloting aircraft means understanding basics of aerodynamics and controls of different aircraft, usually but not necessarily it also encompasses basic understanding of flight control procedures.}
	\skill[Advanced]{Pilot: Jetpack}{Agility}{While not piloting in the classical sense, using jetpacks effectively is an extremely difficult discipline of aeronautics.}
	\skill[Advanced]{Pilot: Space}{Intelligence}{Piloting spacecraft does not happen alone but this skill is representative of any position spacecraft may have.}
	\skill[Advanced]{Quaffing}{Constitution}{Quaffing, getting wrecked, hammered, tanked, any of the above. This determines a character's ability to hold his liquor.}
	\skill{Restraint}{Courage}{Restraint is the ability to push through and ignore both pain and strong emotions. Trying to suppress disabling characteristics is at a penalty equal to the disabling characteristic.}
	\skill[Advanced]{Security}{Intelligence}{Security encompasses anything that is involved in defense: Personally setting and defusing traps, tactical choice of location, how to employ chokepoints and the exploitation of any mistakes the opposition might have made.}
	\skill{Sleight of hand}{Dexterity}{Sleight of hand covers everything that requires delicate fingers and a good distraction. This may be pickpocketing or card tricks or whatever someone might come up with. Picking locks is part of this skill as well.}
	\skill[Advanced]{Smithing}{Dexterity}{Smithing is the creation of new objects from metal. Casting also falls under this skill, even though it is not technically smithing.}
	\skill{Stealth}{Agility}{Stealth describes the ability to hide, be it oneself or objects, as well as moving quietly. It is usually heavily modified and often opposed with Perception.}
	\skill{Stories}{Charisma}{Stories means the knowledge of stories, the ability to make them up on the spot and the capability to tell them interestingly.}
	\skill{Survival}{Instinct}{Survival is a catchall skill encompassing anything required for wilderness or wasteland survival: finding something edible and clean water, building improvised shelters and the most basic equipment.}
	\skill{Swimming}{Constitution}{Swimming is the capacity to cross through waters without drowning. Due to how rare open bodies of water are, this skill is surprisingly rare.}
	\skill{Tailoring}{Dexterity}{Tailoring is the knowledge of how to make objects from cloth or leathers. Very few people still do this themselves and their works are revered and sold for high prices.}
	\skill{Tracking}{Instinct}{Tracking means finding and following a trail. This might be footprints of some wild animal or disturbances left by fleeing suspects.}
	\skill[Advanced]{Voice Athlete}{Charisma}{Voice athletes are capable of changing their voices to sound a certain way. This can be used for ventriloquism, impersonation or something as simple as singing.}
	\skill[Advanced]{Zoology}{Intelligence}{Zoology is knowledge about animals. This may be from formal education or experience and can sometimes be restricted when dealing with rare or exotic animals.}
	
	\section{Abilities}
	\label{abilitylist}
	\ability{Advanced Parry}{400}{Overly Cautious}{When parrying multiple hits, distribute DoS among any amount of attackers. Still requires more DoS than the opponent for single hits. Can also parry Flexible weapons.}
	\ability{Alpha Strike}{500}{From the shadows, no Beta Strike}{Successfully attacking an unaware target automatically hits critically.}
	\ability{Assassin Strike}{350}{Acrobatics Trained}{Scoring a critical hit or deathblow in melee allows the character to move up to his speed in meters right away without provoking opportunity attacks.}
	\ability{Bar Fighter}{250}{Quaffing Trained}{Ignore "Improvised" penalties.}
	\ability{Battle Mind}{400}{Intelligence 40}{The character may use intelligence instead of instinct for initiative calculation.}
	\ability{Battle Sense}{500}{Perception Trained}{Adds a fifth of Perception Bonus to initiative. Doubles penalties to attacks of opportunity against the character.}
	\ability{Beta Strike}{500}{Constitution 40, no Alpha Strike}{Cause a level of exhaustion to an enemy for every 3 attacks targeted at him.}
	\ability{Blind Fighting}{300}{Trained Sense: Hearing}{Limits the penalties for being blinded in melee combat to -15.}
	\ability{Blurry}{250}{Acrobatics Trained, Athletics Trained}{While sprinting the character imposes a -20 to everyone trying to hit him.}
	\ability{Broken}{450}{Courage 40}{Grants +30 to fear and pinning tests but doubles penalties from bad reputation or disposition.}
	\ability{Butcher}{400}{no Earthshaker}{Damage dealt with blades is increased by 1.}
	\ability{Calculated Pilot}{300}{Instinct 30, Dexterity 30}{Halves penalties for piloting tests in demanding, stressful situations.}
	\ability{Calming Focus}{350}{Courage 40}{Re-roll one failed fear or pinning test per turn.}
	\ability{Calming Presense}{200}{Command Trained, Calming Focus}{The character may take an action to make a command test at a +20 bonus. For every degree of success all allies in his vicinity gain a +10 to tests to resist fear and pinning.}
	\ability{Clear Target}{300}{Ranged Base 30}{Halves penalties for calling hit locations on ranged attacks.}
	\ability{Clotter}{300}{Constitution 55}{When starting to bleed, make a toughness check at a -10 penalty. On a success the character doesn't bleed.}
	\ability{Crack Shot}{500}{Perception Trained, Clear Target}{Before taking a shot, make a perception check at a penalty equal to twice the target location armor. On a success halve the armor for this attack. Has no effect on shields.}
	\ability{Dominion}{350}{Supreme Awareness}{When taking a Defensive Stance and not moving, the control area is increased to 360°. The character may also gain attacks of opportunity against disengaging enemies.}
	\ability{Drunken Master}{300}{Bar Fighter}{Limits the penalty to melee combat resulting from chemicals to -10, he himself is at a -20 to hit and can use maneuvers as normal.\\Costs half as much for \textit{balanced} characters.}
	\ability{Dual Wielding}{250}{Instinct 30, Dexterity 40}{Halves penalties for dual wielding. Has to be taken once for melee and once for ranged separately.}
	\ability{Earthshaker}{400}{no Butcher}{Damage dealt with blunt weapons is increased by 1.}
	\ability{Executioner}{350}{Trained Sense: Smell}{Grants +10 to hit bleeding targets.}
	\ability{Expert Wrestler}{350}{Melee Combat Training (Grappling) Experienced}{The character is incredibly well-trained in grappling that he can initiate a Hold as a free action.}
	\ability{Face Breaker}{300}{Dexterity 30, Agility 30, Stunning Blow}{Grants unarmed strikes the Trauma special rule.}
	\ability{Fighting Retreat}{400}{Battle Sense}{Allows a single attack to be made when disengaging. This attack counts as being performed in movement.}
	\ability{Flip Up}{300}{Acrobatics Trained}{When standing up, reduce the time it takes by an action: prone to standing now takes one action or a free action and a successful agility test.}
	\ability{Focused Frenzy}{350}{Instinct 30, Intelligence 40, no Unbridled Rage}{When the character is made to go berserk by some means, they can still identify friend and foe as well as take defensive actions, albeit at a -15 penalty.}
	\ability{Formation}{300}{Intelligence 35}{When taking Combined Actions, everyone takes a cumulative +10 up to +30. When the Unbreakable Bond partner is involved, those two gain an additional +10.}
	\ability{From The Shadows}{250}{Overly Cautious}{During the first round of combat the character has 6 additional initiative, unless the character was ambushed or similarily caught off guard.}
	\ability{Gruesome}{450}{Intimidate Experienced}{When destroying body locations or landing a killing blow, the character makes an Intimidate test with a bonus equal to twice the last attack's damage. All fear tests suffer an additional penalty equal to 10 + 5 per DoS.}
	\ability{Hand-to-hand Basics}{250}{Combat Training (Striking or Grappling) Trained}{When fighting armed enemies, the character counts as armed as well.}
	\ability{Hax0r e1337}{400}{Computer Operation Experienced}{Doubles the degrees of success on Computer Operation tests to crack other devices.}
	\ability{Heroic}{400}{Courage 40}{Grants +15 to fear and pinning tests.}
	\ability{High Noon}{500}{Combat Training (Pistol) Experienced, Quickdraw}{When drawing a pistol, the character may take a single shot as a free action.}
	\ability{Iron Fist}{450}{Hand-to-hand Basics, Maneuver: Stunning Blow}{Every unarmed strike may now count as a having Stun(0) without inferring a penalty.}
	\ability{Lead Storm}{350}{Strength 45}{Weapons with a fire rate of more than 1 which are not launchers always count as braced.}
	\ability{Light Sleeper}{250}{Overly Cautious}{Overly Cautious now also works when sleeping or intoxicated.}
	\ability{Marksman}{300}{Perception Experienced}{Halves penalties for long ranges.}
	\ability{Medical Insight}{400}{Medication Experienced}{Doubles the degrees of success on Medication tests to heal others.}
	\ability{Mobile Combat}{250}{Dexterity 30, Agility 40}{Halves penalties for fighting while moving. This includes a Charge maneuver's flat penalty if the character also has Maneuver: Charge.}
	\ability{Natural Geek}{350}{Intelligence}{Halves penalties from not knowing what you're doing. This includes Weapon Training and Skills.}
	\ability{On your feet!}{100}{Command Trained, Heroic}{The character may take an action to make a command check. On a success an ally gains a +5 per degree of success to any action following the character's orders.}
	\ability{One-man artillery}{350}{Strength 45}{Launchers always count as being braced.}
	\ability{Overly cautious}{300}{Instinct 30}{While the character barely gets a good night's sleep anymore, he can ignore Unaware conditions by passing a Perception check.}
	\ability{Peer}{100}{Charisma 30}{Gain +10 to interaction tests with a specified group of people.}
	\ability{Perfectionist Craftsman}{400}{a crafting skill Experienced}{Doubles the degrees of success on crafting tests when the specific skill meets the requirements.}
	\ability{Personified Inspiration}{500}{Charisma 40, Heroic}{When the character does a daring or heroic deed, all allies present are immune to fear and pinning for the rest of the encounter or scene.}
	\ability{Precision Strike}{300}{Melee Base 30}{Halves penalties for attacking small targets with melee attacks.}
	\ability{Protective Stance}{250}{Instinct 40, Constitution 40}{When taking a Defensive Stance, the character may turn active actions into reactions without penalties and he may parry for allies within his melee range.}
	\ability{Provoke}{350}{Courage 45}{Spend an action to taunt an enemy and make a skill test opposed by the target's restraint. If the character wins, the target must attack the character at the next opportunity.}
	\ability{Quickdraw}{250}{Dexterity 30, Agility 30}{Draw smaller equipment pieces, pistols and one-handed melee weapons as a free action.}
	\ability{Rapid Reload}{300}{Dexterity 40}{Halves reload times.}
	\ability{Reliable Reputation}{200}{Charisma 40, no Broken}{Halves penalties from bad disposition.}
	\ability{Render}{400}{Strength 55}{When dealing damage with the Tearing rule, roll an additional dice. Still only keep one.}
	\ability{Ripper}{350}{Render}{When dealing damage with the Tearing rule and rolling doubles, take both dice.}
	\ability{Sidearm}{250}{Dual Wielding Melee \& Ranged}{When attacking in melee combat with a melee weapon in one hand and a pistol in the other, the character takes no penalties from shooting in melee combat.}
	\ability{Skinner}{500}{Perception Trained}{Before taking a melee attack, make a perception check at a penalty equal to twice the target location armor. On a success halve the armor for this attack.}
	\ability{Skulltaker}{500}{Clear Target or Precision Strike}{Removes penalties from calling hit locations for ranged attacks (when combined with Clear Target) or melee attacks (when combined with Precision Strike).}
	\ability{Snapshot}{350}{Steady Aim}{Aiming takes half as long.}
	\ability{Stabilization}{300}{Medication Trained}{The character is able to staunch bleeding in one round.}
	\ability{Steadfast}{200}{Agility 30, Constitution 30}{Tests to prevent falling over are at a +10.}
	\ability{Steady Aim}{250}{Intelligence 40, Strength 30}{When aiming, line of sight may be broken for a round without aiming being interrupted. By GM discretion this may count even longer if the target is moving particularily predictably.}
	\ability{Strong Back}{350}{Strength 55}{The character's carry weight is increased by half.}
	\ability{Supreme Awareness}{350}{Instinct 55 or Light Sleeper}{Roll twice when determining initiative or gathering senses, picking the higher result.}
	\ability{Tactical Advance}{350}{Command Known}{While advancing carefully from one cover to the next over a distance of MS meters in one turn, the character counts as in cover for the whole way.}
	\ability{The Best Defense}{300}{Courage 40}{Halve offensive penalties of defensive stance.}
	\ability{Thick Skull}{400}{Constitution 50}{Grants immunity to the Trauma special rule.}
	\ability{Threatening Presence}{450}{Intimidation +10, no Calming Presence}{Impose a -15 penalty to enemies' tests against fear and intimidation.}
	\ability{Too Angry To Die}{200}{Courage 40, Constitution 40}{While frenzied, the character has to take at least 8 damage at once or lose his head in order to die. Bleeding out only starts when the character stops frenzying but he will be unconscious when frenzy ends.}
	\ability{Trained Sense}{250}{Perception Trained}{Grants a +10 bonus to sensory checks using that sense. Can be taken once for every sense.}
	\ability{Unbreakable Bond}{250}{being good friends; if one is Clumsy and the other is Cursed by Fortuna, the cost is only 100 XP}{When around a specified close friend, that friend may make a +20 charisma check as a free action and every degree of success gives the character +10 to resist fear and pinning. If both of them have Unbreakable Bond, the bonus is +40 instead.}
	\ability{Unquestioned}{500}{Reliable Reputation}{Penalties to Command tests resulting from disbelief in authority (e.g. represented by Rebel or some Bound by Principle) do not apply.}
	\ability{Unrestrained Reflexes}{300}{Agility 35, Dodge Trained}{The character may make an additional dodge action using the same reaction. This may happen once per turn.}
	\ability{Vault}{300}{Agility 30, Strength 30}{The character can use suitable objects in the environment to double jump height and leap length during movement without slowing down.}
	\ability{Volume of Fire}{350}{Ranged Combat Training (Heavy) Known}{When using a weapon with a rate of fire above 1 to take a standard shot, the character may spend more ammunition to gain a +5 to hit per shot fired after the first, up to the weapon's rate of fire.}
	\ability{Walk it off}{350}{Constitution 40}{The character can continue acting while bleeding until completely bled out. If combined with Tough as nails, the character may enter a frenzy when bleeding as well.}
	\ability{Where it hurts}{400}{Hand-to-hand Basics, Strength 40}{The character's unarmed attacks may profit from the Tearing special rule.}
	
	\subsection{Maneuvers}
	\maneuver{Attack of Opportunity}{150}{Instinct 30, Agility 30}
	\maneuver{Bind}{200}{Instinct 35, Dexterity 35}
	\maneuver{Burst}{200}{Dexterity 30, Strength 35}
	\maneuver{Called Jab}{100}{Maneuver: Feint, Perception Known}
	\maneuver{Charge}{100}{Maneuver: Knockdown, Agility 40}
	\maneuver{Cleave}{100}{Maneuver: Knockdown, Courage 40, Instinct 40}
	\maneuver{Crushing Blow}{300}{Maneuver: Powerstrike, Courage 50, Strength 60}
	\maneuver{Disarm}{100}{Maneuver: Feint, Maneuver: Bind}
	\maneuver{Feint}{200}{Dexterity 35, Agility 35}
	\maneuver{Flurry}{100}{Maneuver: Feint, Dual Wield (Melee)}
	\maneuver{Intercept}{100}{Maneuver: Bind, Courage 50}
	\maneuver{Knockdown}{100}{Maneuver: Powerstrike, Strength 45}
	\maneuver{Piercing Thrust}{300}{Maneuver: Called Jab, Courage 40, Dexterity 40}
	\maneuver{Powerstrike}{200}{Strength 35}
	\maneuver{Reversal}{300}{Maneuver: Intercept, Courage 60, Instinct 50}
	\maneuver{Shift}{100}{Maneuver: Feint, Instinct 40, Dexterity 35, Agility 35}
	\maneuver{Stunning Blow}{100}{Maneuver: Powerstrike, Intelligence 35}
	\maneuver{Takedown}{100}{Maneuver: Feint, Agility or Strength 40}
	
	\section{Races}
	\label{sec:racelist}
	\paragraph*{Pure (0 GP)}
	\textit{Earth's standard human. Comes in all shapes and sizes.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		25 & 25 & 25 & 25 & 25 & 25 & 25 & 25 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} \\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	\textbf{Usual Backgrounds:} Any\\
	\textbf{Disallowed Backgrounds:} 
	
	\hrulefill
	\paragraph*{Trans-species / Avian (3 GP)}
	\textit{A human that has undergone surgery and gene therapy to attain some bird-like features. Generally that is good eyesight but it might also encompass a feather coat.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 22 & 35 & 22 & 22 & 30 & 22 & 22 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Perception +1,	Survival +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Nimble,	Outstanding sense (sight)\\
	\textbf{Banes:} Second-class citizen\\
	\textbf{Usual Backgrounds:} Courier, Driver, Gambler, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Canine (1 GP)}
	\textit{A human that through gene therapy and surgery has attained dog-like features. These are cosmetic changes and an outstanding sense of smell.\\
	These types of people are generally more obedient after their transformation. Due to this and their sharp senses, they are often employed by private investigators.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		25 & 22 & 35 & 30 & 20 & 25 & 20 & 22 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Perception +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Outstanding sense (smell)\\
	\textbf{Banes:} Second-class citizen, Slave mentality 20\\
	\textbf{Usual Backgrounds:} Gambler, Investigator, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Castorimorpha (3 GP)}
	\textit{A human that through gene therapy and surgery has attained beaver-like features. These are some cosmetic changes, an affinity for swimming and a more agile but weaker body.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 25 & 30 & 25 & 20 & 30 & 25 & 22 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Swimming +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Diver's Lung, Nimble\\
	\textbf{Banes:} Second-class citizen\\
	\textbf{Usual Backgrounds:} Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Elf (0 GP)}
	\textit{Among all trans-species transformations this is by far the most expensive and complicated, due to how difficult creating the necessary material is. However due to the very fine process, some who undergo the procedure keep just a small part of their fertility.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 25 & 28 & 25 & 25 & 28 & 20 & 20 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Acrobatics +1, Appeal +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} one Outstanding Sense, Looker\\
	\textbf{Banes:} \\
	\textbf{Usual Backgrounds:} Escort, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Feline (6 GP)}
	\textit{The oldest form of trans-species humans, someone that has undergone gene therapy to attain some cat-like features. They come to see very well in the dark and gain a superior sense of balance.\\
	However they also become playful and particularly dislike hard or dirty work, which is why of all trans-humans they are likely the most trafficked, usually just as status symbols.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		20 & 25 & 35 & 25 & 25 & 30 & 22 & 20 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Acrobatics +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Balance, Dark Vision\\
	\textbf{Banes:} Second-class citizen, Vanity 20\\
	\textbf{Usual Backgrounds:} Escort, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Piscean (3 GP)}
	\textit{By far the rarest form of trans-species humans, these people have acquired some fish-like attributes. The skin is covered in scales, the breathing can partially be substituted by gills.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 22 & 30 & 22 & 22 & 30 & 22 & 22 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Perception +1, Swimming +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Dark Vision, Diver's Lung, Natural Armor 2\\
	\textbf{Banes:} Second-class citizen\\
	\textbf{Usual Backgrounds:} Gambler, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Reptilian (1 GP)}
	\textit{Sometimes regarded as the odd one out even among trans-species, these people chose to gain reptilian qualities like scales, an inclination to climb and even higher reflexes than other trans-humans.
		While other trans-species might pass as some sort of costume, these changes are absolutely unmistakable.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 22 & 38 & 20 & 20 & 25 & 25 & 20 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Climbing +1, Perception +1\\
	\textbf{Abilities:} Overly cautious\\
	\textbf{Boons:} Natural Armor 4\\
	\textbf{Banes:} Second-class citizen, Impaired Sense (Touch)\\
	\textbf{Usual Backgrounds:} Gambler, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Ungulate (0 GP)}
	\textit{Through gene therapy and surgery this person has taken on cow-like features. Most of the changes are of cosmetic nature, but most of them are tougher than the average human.\\
	Likely for both of those reasons these people are often employed as cheap workforce for dangerous, exhausting jobs.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 22 & 30 & 22 & 22 & 22 & 30 & 28 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Perception +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Poisonresistance\\
	\textbf{Banes:} Second-class citizen\\
	\textbf{Usual Backgrounds:} Gambler, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Trans-species / Generic (1 GP)}
	\textit{Trans-species humans have changed their bodies to resemble a humanoid version of some animal. Roughly every decade a new wave of trans-species humans rises in popculture, looked upon suspiciously from all those that are not part of the movement themselves.\\
	These changes come with qualities and drawbacks related to the animal in question, as well as general physical weakening and sterility.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		22 & 22 & 36 & 22 & 22 & 22 & 22 & 22 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} one except instinct +5\\
	\textbf{Skills:} Perception +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Big Spender 2, Outstanding sense (any one)\\
	\textbf{Banes:} Second-class citizen\\
	\textbf{Usual Backgrounds:} Gambler, Laborer, Performer, Wastelander\\
	\textbf{Disallowed Backgrounds:} Academic, Shark, Soldier
	
	\hrulefill
	\paragraph*{Vat-grown / Adaptive (26 GP)}
	\textit{Artificially grown, these humans are created to serve a single person or institution for generally a single purpose. They are superior to normal humans in almost every way, except they usually intentionally lack some creative thought and can't reproduce due to how unique their genetic material is.\\
	They don't strive to raise in social classes or to improve their living situation much due to inbuilt programming and are very obedient unless their master wishes specifically for creative thought.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		28 & 28 & 28 & 28 & 28 & 28 & 28 & 28 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} +4 to any two\\
	\textbf{Skills:} \\
	\textbf{Abilities:} \\
	\textbf{Boons:} 3 levels between: Adaptable Circulation, Nerves of Steel\\
	\textbf{Banes:} Slave Mentality 25\\
	\textbf{Usual Backgrounds:} \\
	\textbf{Disallowed Backgrounds:} Orphan, Shark
	
	\hrulefill
	\paragraph*{Vat-grown / Biocomputer (24 GP)}
	\textit{Created with incredible intelligence they are grown to serve as generals, advisers and assistants. The only limit to their incredible intellect is usually jokes.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		30 & 40 & 30 & 25 & 25 & 25 & 25 & 25 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} two educations +2
	one education +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} Slave Mentality 25\\
	\textbf{Usual Backgrounds:} Academic, Hacker\\
	\textbf{Disallowed Backgrounds:} Orphan, Shark
	
	\hrulefill
	\paragraph*{Vat-grown / Crafter (27 GP)}
	\textit{Blessed with incredible dexterity, they are created to create. The basic muscle memory to build a certain thing is engrained during the building process and they have an easy time learning more craftsmanship.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		25 & 30 & 30 & 25 & 40 & 25 & 25 & 30 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} +2 on one of: Chemistry, Construction, Mechanics, Medication, Security, Smithing\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Outstanding Sense (Touch)\\
	\textbf{Banes:} Slave Mentality 25\\
	\textbf{Usual Backgrounds:} Academic, Doctor, Engineer, Fixer, Laborer\\
	\textbf{Disallowed Backgrounds:} Orphan, Shark
	
	\hrulefill
	\paragraph*{Vat-grown / Social (26 GP)}
	\textit{Built for any type of social role, these specimen are generally ordered by members of high society to fulfill a certain job, be it as an escort, as a salesperson or as some sort of investigator.\\
	Since those jobs can be fulfilled sufficiently by normal humans and growing people is not cheap, these types are rare.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		30 & 30 & 30 & 40 & 25 & 25 & 25 & 25 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} +1 to: Appeal and Deceive OR Command and Intimidate OR Commerce and Estimate\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Smoking OR Social Chameleon\\
	\textbf{Banes:} Slave Mentality 25
	Vanity 30\\
	\textbf{Usual Backgrounds:} Escort, Fence, Investigator, Performer\\
	\textbf{Disallowed Backgrounds:} Orphan, Shark
	
	\hrulefill
	\paragraph*{Vat-grown / Warrior (30 GP)}
	\textit{The most common vat-grown human. The fight against terrorists for governments, against governments for insurgents or against whoever pays the least, but they are also employed as high-society bouncers and bodyguards.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		35 & 20 & 25 & 20 & 20 & 30 & 35 & 35 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} Con or Str +8\\
	\textbf{Skills:} Melee Combat Training (Striking or Grappling) +1
	Security +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Two of: Combat Academic, Iron Resilience, Stoic, Tough as nails\\
	\textbf{Banes:} Slave Mentality 30\\
	\textbf{Usual Backgrounds:} Bodyguard, Bouncer, Mercenary, Soldier, Terrorist\\
	\textbf{Disallowed Backgrounds:} Orphan, Shark
	\section{Backgrounds}
	\label{sec:backgroundlist}
	\paragraph*{Academic (9 GP)}
	\textit{Formerly educated in a single or many different things this character mainly knows a lot of things but might lack in the necessary skills to apply them properly.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		& 5 &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} +6, maximum of +2 across: Chemistry, Computer Operation, Cryptography, Herbalism, History, Law, Mechanics, Medication, Philosophy, Smithing, Stories, Zoology;
	one Education +2
	one Education +1\\
	\textbf{Abilities:} Natural Geek\\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Bodyguard (7 GP)}
	\textit{Sworn to protect this character is versed in how to identify and eliminate threats to another person.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		5 &  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Ranged Combat Training (Pistol or Short rifle) +2
	One armed Melee Combat Training +2
	Combat Training (Striking or Grappling) +1
	Perception +1
	One Drive +2
	a fitting Navigation +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Bouncer (1 GP)}
	\textit{This character was employed to stop intrusions. Usually this happens rather peacefully but if necessary this might include force as well.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Combat Training (Striking AND Grappling) +2
	Intimidate +2
	Interrogation +1
	Restraint +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Child Soldier (15 GP)}
	\textit{Naturally born children are far cheaper than vatgrown soldiers but, if trained correctly, can be just as effective. These children are raised mentally scarred but very efficient and disciplined killing machines.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		2 &  & 2 & -5 & 2 & 2 & 2 & 2 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Command +1
	Ranged Combat Training (Pistol and two others) +2
	Melee Combat Training (Any one) +2
	Melee Combat Training (Another unarmed) +1
	Security +2\\
	\textbf{Abilities:} Broken\\
	\textbf{Boons:} Tough as nails\\
	\textbf{Banes:} Ignorant (Horrors of war) 40\\
	
	\hrulefill
	\paragraph*{Courier (8 GP)}
	\textit{Delivering packages in the darker parts can be easier said than done. It takes precision, cunning and obviously a fit pair of legs. Such a character knows the darkest secrets of his city and those secrets are safe with him.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  & 5 &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Athletics +2
	Climbing +2
	Deceive +1
	One Drive or Pilot +2
	Sleight of hand +1
	Stealth +1\\
	\textbf{Abilities:} Flip Up\\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Doctor (7 GP)}
	\textit{A medical professional is always welcome. He has learned not just first aid but may also be capable of performing surgery.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		& 5 &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Appeal +1
	Medication +3
	Perception +1
	Restraint +2\\
	\textbf{Abilities:} Stabilization\\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Driver (8 GP)}
	\textit{Professionally trained in the art of moving a vehicle. She keeps her calm in stressful situations and gets her contractor from point A to B safely.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  & 5 &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} One Drive +2
	One Drive or Pilot +3
	One fitting Navigation +2
	Restraint +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Engineer (0 GP)}
	\textit{Constructing buildings is incredibly important, people who understand how to are vital to society.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Computer Operation +1
	Construction +3
	Mechanics +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Escort (4 GP)}
	\textit{Capable of talking through almost every situation and usually chosen for their looks, such people managed to turn their bodies and tongues into money.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  & 5 &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Appeal +2
	Deceive +1
	Interrogation +1
	Quaffing +1
	Restraint +2
	Sleight of hand +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Fence (2 GP)}
	\textit{Stolen goods are not terribly uncommon, one just needs to know where to sell them to. Some of those fences are even capable of stealing their own goods.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Commerce +3
	Deceive +2
	Sleight of hand +1
	Stealth +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Good Reputation 2\\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Fixer (4 GP)}
	\textit{There are a lot of people dependent on drugs, be it Flow addicted members of illegal fight clubs, corporate hackers working under Speed influence or young couples experimenting with Raze, someone has to make their substances. These people know how to make it and know what it does to one's body, in the short as well as long term. Whether they care is an individual question.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Appeal +1
	Brewing +1
	Chemistry +3
	Commerce +2
	Stealth +1
	Medication +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Gambler (2 GP)}
	\textit{Somehow Lady Fortuna is with this one and he made his money by gambling. In many cases such players are accused of cheating, sometimes banned from their dens and other times wanted by crime families.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Gambling +3
	Interrogation +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Fortune's Child\\
	\textbf{Banes:} Debt (2000cr)\\
	
	\hrulefill
	\paragraph*{Hacker - Black Hat (1 GP)}
	\textit{Corporate hacking, blackmailing or juvenile curiosity and too much contact with cyberspace can lead someone to become a black hat. Their acts are malicious and their allegiance lies with money. More often than not they are in the process of fleeing from authorities or corporations.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Commerce +1
	Computer Operation +3
	Security +1
	Stealth +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Hacker - White Hat (0 GP)}
	\textit{As opposed to black hats, white hats are trying to find weaknesses in systems so they can fix them. Their actions are generally benevolent in nature but they also rarely work unpaid.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Computer Operation +3
	Law or Security +2
	the other +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Investigator (4 GP)}
	\textit{Be it private investigators or police officials, many unsolved cases drift through any city's archive. Some investigators are interested in these old, unsolved cases, others are commited to reducing the amount of new ones.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Interrogation +2
	Perception +2
	Law +2
	Security +2\\
	\textbf{Abilities:} Overly Cautious\\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Laborer (1 GP)}
	\textit{A lot of work can be taken over by machines. Yet sometimes a machine can't be used or is simply more expensive than a low wage laborer or a slave. This usage of human resources is not officially endorsed and even technically illegal, yet when a contract is formed (or forged...), the endeavour might be considered legitimate.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Athletics +2
	Medication +1
	Navigation (Ground) +1
	Restraint +2
	Survival +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Mercenary (2 GP)}
	\textit{Born for fighting and fighting for pay; the core principles of mercenaries haven't changed. Loyalty belongs to the first or highest bidder and as long as the price fits, the dirty work will be taken care of.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Intimidation +1
	Ranged Combat Training (Pistol and one other) +2
	Melee Combat Training (Any one) +1
	Security +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Stoic or Tough as nails\\
	\textbf{Banes:} Bound by duty or Wanted II\\
	
	\hrulefill
	\paragraph*{Performer (5 GP)}
	\textit{Performers are paid to sing, dance, balance and whatever might be entertaining to watch or listen to. Payment is usually slim or depending on the circumstances as simple as continuing to live.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  & 3 &  & 3 &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Acrobatics +2
	Appeal +1
	Athletics +1
	Education: Etiquette +2
	Voice Athlete +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Shark (0 GP)}
	\textit{Some people have enough money to make more money by loaning money and having it paid back at ludicrous interest rates. These people are usually versed in all forms of trade and bending the law.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Commerce +3
	Intimidation +1
	Law +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Soldier (3 GP)}
	\textit{Harsh training and incredible equipment make them a force to be reckoned with. Most are only employed to defend borders but the best of them are chosen to sabotage terrorists, either by infiltration or via an orbital drop in a strike suit.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Command +2
	Ranged Combat Training (Pistol and one other) +2
	Melee Combat Training (Any one and another unarmed) +1
	Security +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Stoic or Tough as nails\\
	\textbf{Banes:} Belief in authority 30
	Bound by duty\\
	
	\hrulefill
	\paragraph*{Terrorist (3 GP)}
	\textit{There are many reasons to be unhappy with the country's situation but only few take such radical measures. These people have reached the point of either complete devotion to a cause and an according enemy or of having absolutely nothing to lose anymore.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Chemistry or Construction +2
	Deceive +1
	History or Philosophy +2
	Melee Combat Training (Any one) +1
	Ranged Combat Training (Any one) +1
	Security +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} Social Chameleon\\
	\textbf{Banes:} Rebel 30\\
	
	\hrulefill
	\paragraph*{Trafficker (3 GP)}
	\textit{Anything can be traded, so long as you aren't caught. A particularily hot good is giving the term "human ressources" a new meaning. People like this are cunning, cold and the toughest tradesmen.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Appeal +1
	Commerce +2
	Deceive +2
	Intimidation +1
	Security +1\\
	\textbf{Abilities:} Broken\\
	\textbf{Boons:} \\
	\textbf{Banes:}
	
	\hrulefill
	\paragraph*{Urchin (0 GP)}
	\textit{A child that lost its guardians and maybe its living place very early in life needs to learn a lot of things in a short amount of time in order to survive. There is not much time for youth nor slacking off and it will understand that acting slowly is very dangerous.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Appeal +1
	Athletics +1
	Climbing +1
	Deceive +1
	Dodge +1
	Perception +1
	Restraint +1
	Sleight of hand +1
	Stealth +1
	Survival +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{E-Girl (5 GP)}
	\textit{}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  & 5 &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Appeal +2
	Deceive +1
	Commerce +2
	Stories +1
	Voice Athlete +2\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Wastelander (1 GP)}
	\textit{Not everyone grows up in flashing cities. Many people grow up in the far outskirts, places where barely anything grows and that are by their very existence hostile towards life, yet somehow small communities arise in them again and again. 
		Growing up in such places takes a toll on someone and it requires quickly learning a very particular set of skills.}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Cooking +2
	Perception +2
	Survival +2\\
	\textbf{Abilities:} Trained sense (any one)\\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Technician (8 GP)}
	\textit{}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		& 3 &  &  & 3 &  &  &  \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} Computer Operation +2
	Construction +1
	Mechanics +3
	Perception +1
	Security +1
	two Educations +1\\
	\textbf{Abilities:} \\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	\hrulefill
	\paragraph*{Street Fighter (8 GP)}
	\textit{}\par
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline
		Cr & Int & Ins & Ch & Dex & Ag & Con & Str \\ \hline
		&  &  &  &  &  & 3 & 3 \\ \hline
	\end{tabular}\par
	\noindent\textbf{Other modifiers:} \\
	\textbf{Skills:} One armed Melee Combat Training +2
	Melee Combat Training (Striking or Grappling) +2
	Melee Combat Training (the other) +1
	Restraint +2\\
	\textbf{Abilities:} Melee Maneuvers worth 400 XP\\
	\textbf{Boons:} \\
	\textbf{Banes:} \\
	
	
	\section{Boons}
	\boon[each]{Adaptable Circulation}{Medical Toughness is increased by 1. Can be taken multiple times.}{2}
	\boon{Ambidextrous}{The character can use either hand equally good. Dual Wielding and Maneuver: Flurry only cost half. When combined with Dual Wielding, removes penalties for dual wielding melee weapons and pistols completely.}{12}
	\boon{Aptitude}{Adds +5 to a characteristic which doesn't count against investment limits. Can be taken multiple times but only once per characteristic.}{10}
	\boon{Balance}{Tests to prevent falling over are at a +20. Improves on Steadfast and doesn't stack.}{10}
	\boon{Battle Trance}{The character can enter a battle trance. This takes two actions and causes one level of exhaustion. The character becomes frenzied but can identify friend and foe and return to normal by spending two actions.}{12}
	\boon[each]{Big Spender}{The character gains additional equipment worth up to \(5 * Ch * level\) of this boon. The money can only be spent at character creation and unused credits are wasted. Equipment may as always be restricted by the GM.}{3}
	\boon{Born Hero}{The character counts as having all prerequisites for the Abilities Heroic, On your feet! and Personified Inspiration. These abilities only cost half as much.}{6}
	\boon[+ new background]{Broad Education}{The character may choose a second background and gain its skill bonuses as well.}{17}
	\boon{Combat Academic}{All maneuver abilities only cost 75\% of their original cost. Penalties from missing combat training are halved.}{12}
	\boon{Dark Vision}{The character only takes half penalties in low light but normal penalties in complete darkness.}{10}
	\boon{Diver's Lung}{The character may hold her breath twice as long.}{4}
	\boon{Euphonia}{The character has a beautiful voice. He gains a +10 to social interaction tests when the other party can hear him. This also makes Voice Athlete a basic skill.}{10}
	\boon[each]{Formal Education}{Grants 50 XP to be spent only on educations. Can be taken multiple times.}{1}
	\boon{Fortune's Child}{Every session the character may reroll one of her dice rolls or one that she is directly affected by.}{10}
	\boon{Giant}{The character becomes two categories larger. He is easier to hit, has more melee range, is faster and more imposing.}{10}
	\boon[each]{Good Reputation}{The character has some sort of good reputation, either from well known deeds or from known genetic markers. If he is talking to someone who knows of this, he gains a bonus equal to 5 times the boon's level. Can be taken up to level 10.}{2}
	\boon{Iron Resilience}{Degredation from wounds is reduced by one step.}{10}
	\boon{Large}{The character becomes a category larger. He is easier to hit, has more melee range, is faster and more imposing.}{5}
	\boon{Looker}{The character is beautiful. She gains +5 to social interaction tests. Not compatible with Smoking, Ugly and Physically repulsive.}{5}
	\boon[each]{Natural Armor}{The character has natural armor covering her skin. Adds +1 armor to every location and can be taken multiple times.}{6}
	\boon[each]{Nerves Of Steel}{Rayleigh Index is increased by 1. Can be taken multiple times.}{2}
	\boon{Night Vision}{The character only takes half penalties in complete darkness and no penalties in low light.}{18}
	\boon{Nimble}{Speed is increased by 1 and dodging penalties are reduced by 10.}{10}
	\boon{Outstanding Sense}{Grants +20 to tests based on the chosen sense. Counts as a Trained Sense for the purposes of prerequisites. Not compatible with Impaired Sense for the same sense.}{7}
	\boon{Personal Possession}{The character owns a very special, valuable (up to 800cr) item with not only large material but also high sentimental value. This may include sets of items such as two bionic arms but are up to GM discretion even more than usual.}{8}
	\boon{Pleasant Smell}{If the target of a character's charming social test can smell the character, the character gains +10. Not compatible with Terrible odor.}{7}
	\boon{Poison Resistance}{Grants +20 to resist the effects of poison or venom.}{4}
	\boon{Privileged Access}{The character gains a 25\% discount for license-free equipment made by a certain company. During character creation this bonus is 50\% instead to account for sales in the past. Requires Good Reputation with that company / salesman.}{7}
	\boon{Quick Regeneration}{Grants +30 to natural regeneration tests.}{10}
	\boon{Smoking}{The character is extremely physically attractive or otherwise imposing. He gains +15 to social interaction tests but -20 to hide because his appearance is extremely memorable and outstanding. Not compatible with Looker, Ugly and Physically repulsive. If the character already is a Looker, this can replace it for 7 GP.}{12}
	\boon{Social Chameleon}{Halves all penalties from unknown cultures and improves NPCs' default disposition to the character.}{12}
	\boon{Stoic}{Halves all penalties and double all bonuses on fear tests.}{18}
	\boon{Superior Balance}{Tests to prevent falling over are at a +30. Improves on Balance and doesn't stack.}{16}
	\boon{Thick Skull}{Tests against being stunned gain a +10 and all penalties are halved.}{6}
	\boon{Tough As Nails}{The character can continue acting while bleeding until completely bled out.}{12}
	\boon{Unbridled Rage}{Any check to enter a berserk or frenzy state is at a +20 and any check to resist or return from such a state is at a -20.}{7}
	\boon{Unrivaled Flexibility}{Agile without peer, the character gains a +30 when attempting to release himself from holds or to escape from being tied up.}{15}
	\boon[+ background]{Veteran}{The character is older and more experienced. He gains his background's skill bonuses again, up to the skill's maximum.}{17}

	\section{Banes}
	\bane{Addiction}{The character is addicted to a substance. A week of withdrawal will cause a level of exhaustion every day which are not naturally regenerated anymore. Other exhaustion still regenerates naturally until two weeks of withdrawal. This only applies to uncontrolled withdrawal, not to therapy.}{10}{}
	\bane{Agoraphobia (DC)}{The character is afraid of wide, open places.}{1}{per 5}
	\bane{Annoying Voice}{The character has an annoying voice. This grants -10 to social tests that involve talking.}{5}{}
	\bane{Arrogance (DC)}{The character believes to be superior to others.}{1}{per 5}
	\bane{Backwoods Customs}{Even though most cultures have melted, the character has grown up outside the core of society. He has internalized customs that some would call barbaric.}{5}{}
	\bane{Bad Reputation}{The character has some sort of bad reputation, either from well known deeds or from known genetic markers. If he is talking to someone who knows of this, he gains a penalty equal to 5 times the boon's level. Can be taken up to level 10.}{2}{per level}
	\bane{Bathophobia}{The character is afraid of depths. This may trigger at the bottom of the ocean just as much as it could in a massive canyon.}{1}{per 10}
	\bane{Belief in authority (DC)}{The character believes in authority and tends to believe them. Not compatible with Rebel.}{1}{per 10}
	\bane{Berserk Rush}{When the character is thoroughly enraged or he is influenced by substances that boost courage, he falls into a frenzy. Resisting frenzy from other sources is at a -30 penalty.}{15}{}
	\bane{Blind}{The character can't see. This is due to nervous or brain damage and can't be fixed via augments.}{40}{}
	\bane{Blood Lust (DC)}{Lust for bloody combat drives the character. She likes taking the time to make her victims suffer and might end up causing trouble for herself and her group due to this.}{1}{per 10}
	\bane{Bound by Duty}{The character is obliged to follow a certain person's or group's commands. If she disobeys, there might be severe consequences.}{12}{}
	\bane{Bound by Principle}{The character is bound by her own principles. They are central moral values that may rarely be bent and almost never broken. If they are, doubts will follow the character for at least a week, inferring a -40 penalty to anything requiring focus. By GM discretion these penalties might function slightly differently depending on the situation.}{12}{}
	\bane{Caring (DC)}{The character is overly caring for his peers. He will take great risks to help others.}{1}{per 5}
	\bane{Claustrophobia}{The character is afraid of small, narrow places.}{3}{per 10}
	\bane{Clumsy}{Critical failures occur on a roll of 96 and above.}{20}{}
	\bane{Colorblind}{The character is incapable of seeing colors. When she wants to identify something that is only discernible by color, she takes a -20 penalty. This also counts for ranged attacks against large or smaller targets.}{5}{}
	\bane{Curiosity (DC)}{When there is something to know, the character will want to know, whether it is of concern or not.}{1}{per 5}
	\bane{Cursed by Fortuna}{When a bad event hits the group, this character is much more likely to be hit in particular. Also once per session the GM may declare a success to be a failure instead.}{15}{}
	\bane{Debt}{The character is indebted to someone. The loaner will require regular payments or the character will suffer consequences depending on their relationship and the type of people they are.}{1}{per 1000 cr}
	\bane{Delusions of grandeur (DC)}{The character tends to overstate and overestimate her own ability and take on monumental tasks with delusional confidence.}{1}{per 5}
	\bane{Dietary Rules}{The character will only eat certain things due to personal reasons. Whenever the character is forced to eat something that does not align with his values, e.g. as to not starve to death, this infers penalties equal to the bane's value.}{5}{}
	\bane{Directionally Challenged}{The character has extreme difficulty distinguishing left from right. This makes navigation quite difficult: navigation and navigation-related tests - like tests made in a chase - are at a -10.}{5}{}
	\bane{Dwarfish}{The character is tiny. He is harder to hit, has less melee range and is slower. He is also rarely taken seriously.}{8}{}
	\bane{Envy (DC)}{When another has something that the character does not, she will overstep boundaries to get some of her own.}{1}{per 10}
	\bane{Evil Monologue}{The character tends to talk to herself. This may lead to embarrassing social encounters or even to spilling information about secret plans.}{5}{}
	\bane{Fear of heights (DC)}{The character is followed by an everlasting fear of falling.}{3}{per 10}
	\bane{Flimsy}{Medical Toughness reduced by 1. Can be taken multiple times.}{2}{each}
	\bane{Food Restrictions}{Due to mutation or specific engineering, the character can only consume certain types of food. Anything else leaves the body undigested; often times violently.}{5}{}
	\bane{Forgetful}{The character tend to forget even the most important details. Any checks made to remember specific details suffer a -20.}{5}{}
	\bane{Gambler (DC)}{The character will not pass up on a good bet. When he can play a more or less fair game for something, he has a hard time passing up the chance.}{1}{per 5}
	\bane{Greed (DC)}{Getting more money is great.}{1}{per 5}
	\bane{Hallucinations}{Hallucinating characters live in a notably vastly different reality, e.g. thinking that milk is a deadly poison, that he is haunted by demons only vulnerable to supersonic cheese and so on. Every person will notice and this will infer penalties as per GM discretion.}{10}{}
	\bane{Hesitant}{The character suffers a -3 to initiative.}{5}{}
	\bane{Hungry I/II/III}{The character needs 1.5/2/3 times as much food.}{5}{per level}
	\bane{Impaired Sense}{One of the character's senses functions improperly, incurring -20 on checks based on that sense. This may be offset with augments but never restored to normal levels. Not compatible with Outstanding Sense for the same sense.}{5}{}
	\bane{Impatient (DC)}{The character does not like waiting. Tasks that take a long time of not doing much will be severely harder.}{1}{per 5}
	\bane{Impulsive}{The character tends to act on stupid decisions in the heat of the moment. When such an idea comes up, it takes a -20 intelligence check to resist acting on it.}{5}{}
	\bane{Insomnia}{Getting a good night's rest is hard for the character. In roughly a quarter of all nights (whether randomly or following a pattern) the character takes a -30 penalty to regenerating naturally.}{7}{}
	\bane{Laziness (DC)}{The character is a slob and doesn't put more effort into things than absolutely necessary.}{1}{per 5}
	\bane{Light sensitivity}{The character hates the light. Every action taken in light is at a -30 penalty. Protection from the light is generally enough work and requires enough equipment that the sheer bulk grants similar penalties.}{10}{}
	\bane{Ignorant (DC)}{The character has a hard time understanding a certain topic. This topic should be specified when the Bane is chosen.}{1}{per 10}
	\bane{Naive (DC)}{The character easily trusts strangers. Resisting deception and persuasion is at a penalty equal to the Bane.}{1}{per 5}
	\bane{Necrophobia}{The character has fear of death and dead creatures and will be unable to focus properly when on battlefields, murder or slaughter scenes or graveyards.}{1}{per 5}
	\bane{Needy (DC)}{The character's strong physical desires become distracting to everyday life.}{1}{per 10}
	\bane{Nervous}{Rayleigh Index reduced by 1. Can be taken multiple times.}{2}{each}
	\bane{Neurotically Hygienic (DC)}{The character has a need to keep clean.}{1}{per 5}
	\bane{Night blind}{Doubles all penalties for low light.}{5}{}
	\bane{No tactile sense}{Anything requiring sense of touch takes a -40 penalty, this includes any weapon with a trigger or a blade.}{15}{}
	\bane{Nyctophobia (DC)}{The character has a strong fear of the dark.}{2}{per 5}
	\bane{Obese}{The character is heavily overweight. This comes with multiple drawbacks like a -20 penalty to strength based checks that have to do with body weight (e.g. climbing), -3 to medical toughness, as well as stigmatization and other drawbacks by GM discretion.}{15}{}
	\bane{One-armed}{The character has lost an arm and due to nerve damage can't accept replacements.}{15}{}
	\bane{One-eyed}{The character has lost an eye and due to nerve damage can't accept replacements.}{5}{}
	\bane{One-handed}{The character has lost a hand and due to nerve damage can't accept replacements.}{10}{}
	\bane{One-legged}{The character has lost a leg and due to nerve damage can't accept replacements.}{25}{}
	\bane{Paralyzed Leg}{Due to irreversible nervous damage the character can barely move one leg. This reduces speed by 2 and grants penalties around -15 to tests as per GM discretion.}{15}{}
	\bane{Personal Enemy}{An important person or group has set its eyes on the character and will take measures to foil his plans.}{7}{}
	\bane{Physically Repulsive}{The character is staggeringly ugly. This infers a -20 penalty to social tests when the character can be seen. Not compatible with Smoking, Looker and Ugly.}{12}{}
	\bane{Playful (DC)}{The character loves playing. That can include simple things like chess or video games, but also "games" of predator and prey.}{1}{per 5}
	\bane{Portly}{The character is stocky or otherwise slower than her peers. Her speed is reduced by 1.}{5}{}
	\bane{Prejudice (DC)}{The character is biased against a certain group of people and has a hard time interacting with them.}{1}{per 5}
	\bane{Rebel (DC)}{The character has a hard time trusting authority and tends to revolt. Not compatible with Belief in authority.}{1}{per 10}
	\bane{Righteous (DC)}{Some laws are absolute and they must be followed. The character will work against any injustice to the order she believes in.}{1}{per 5}
	\bane{Scrooge (DC)}{Spending money is painful.}{1}{per 10}
	\bane{Second-class Citizen}{The character is oppressed for one reason or another. This may e.g. be due to stigmatization of a part of his lifestyle or being born with extremely few resources. In any case this will have consequences in social situations and encounters with law enforcement.
		Cannot be taken by Vatgrown.}{5}{}
	\bane{Sensitive Smell (DC)}{When around something that smells particularly nasty, he takes penalties to everything that requires concentration or a healthy stomach equal to the bane.}{3}{per 10}
	\bane{Short}{The character is small. He is harder to hit, has less melee range and is slower. He is also rarely taken seriously.}{5}{}
	\bane{Shortcoming}{A characteristic, that hasn't been invested in, is reduced by 5.}{7}{}
	\bane{Sickly}{Grants -15 penalty to resist disease.}{2}{}
	\bane{Slave Mentality (DC)}{The character does not like making his own decisions. Such situations put a lot of stress on the character.}{1}{per 5}
	\bane{Slow Healer}{The character only heals naturally at a -20 penalty and tests taken to heal this character are at a -10.}{10}{}
	\bane{Speech Disorder}{The character has some sort of speaking disorder. What it may be, the character gains a -10 to tests requiring to speak and takes longer to finish sentences which might cause problems in stressful situations like combat or a heated chase.}{7}{}
	\bane{Squeamish (DC)}{The character takes a penalty to tests to resist fear and panic.}{2}{per 5}
	\bane{Technophobia (DC)}{The character is suspicious of technological advancements, especially solutions to things that could easily be done by humans.}{3}{per 10}
	\bane{Temperamental (DC)}{Small things may make the character unreasonably angry.}{3}{per 10}
	\bane{Terrible Odor}{The character has bad smell. This grants -10 to social tests when the character is in smelling distance and hiding from watchdogs is essentially impossible. Not compatible with Pleasant smell.}{5}{}
	\bane{Trigger Phrase}{Sleeper agents were rumored to have trigger phrases carved into their mind. For the longest time that was purely a myth but now many vat-grown are programmed with such a phrase to force certain behavior. When the phrase is heard by the character, all tests to resist persuasion and commands is at a -20 penalty.}{7}{}
	\bane{Trouble Magnet (DC)}{Some people actively look for trouble. This character has the tendency, willingly or not, to provoke and attract the wrath of others.}{1}{per 10}
	\bane{Ugly}{The character is unshapely. This grants -10 to social tests while the character is being seen. Not compatible with Smoking, Looker and Physically repulsive.}{5}{}
	\bane{Uneducated}{The character has not learned much and loses 50 XP. Can be taken multiple times but XP may never be negative.}{1}{per level}
	\bane{Vanity (DC)}{The character is posh to an extreme. He might refuse tube food, simple and cheap clothing or getting dirty.}{1}{per 5}
	\bane{Vengeful (DC)}{The character does not forget. When someone wronged him, he will make sure to pay them back tenfold.}{1}{per 5}
	\bane{Wanted I-V}{The character is being looked for by an organization. This can be due to criminal record, corporate espionage or involvement in gang wars. The first step roughly describes being the target of a small mercenary or criminal group, a level 3 target would be a low-priority military target and a level 5 target is on LEGION's radar.}{5}{per level}
	
	\section{Sizes}
	\label{sizestable}
	\begin{tabular}{|l|r|r|l|}
		\hline
		\underline{Name} & \underline{\smash{Hit / Intimidate}} & \underline{MS} & \underline{\smash{Example}}                   \\ \hline
		Miniscule  & -40                                                                                      & -4                                     & a knife, pistol or mobile phone \\ \hline
		Puny       & -30                                                                                      & -3                                     & a limb, rifle or sword          \\ \hline
		Tiny       & -20                                                                                      & -2                                     & a child                         \\ \hline
		Small      & -10                                                                                      & -1                                     & small people, tall children     \\ \hline
		Average    & 0                                                                                        & 0                                      & most humans                     \\ \hline
		Tall       & 10                                                                                       & 1                                      & imposing super soldiers         \\ \hline
		Huge       & 20                                                                                       & 2                                      & horses, bikes                   \\ \hline
		Hulking    & 30                                                                                       & 3                                      & cars                            \\ \hline
		Enormous   & 40                                                                                       & 4                                      & busses or larger                \\ \hline
	\end{tabular}

	\section{Fear}
	\label{feartable}
	\begin{tabularx}{\textwidth}{|l|X|}
		\hline
		1-20    & Shivering, the character takes a -10 penalty on his tests until he passes a courage check. He can spend one action to attempt this check.                                                                                                                                                                                                                                            \\ \hline
		21-40   & Severely shaken, the character takes a -15 penalty on all tests for the rest of the encounter or scene and can't use maneuvers or transform actions.                                                                                                                                                                                                                                 \\ \hline
		41-60   & Dumbstruck by fear, the character freezes in place and can’t act until he passes a courage check at the end of one of his turns. This check begins at the same penalty as the initial one and gets a cumulative +10 for every previous attempt. He may take reactions to defend himself or run away (at an increased risk of stumbling as quickly avoiding obstacles is “acting”...) \\ \hline
		61-80   & Frozen by terror, the character is completely unable to move until he passes a courage check at the end of one of his turns. This check begins at the same penalty as the initial one and gets a cumulative +5 for every previous attempt. Courage checks are allowed 1D5-1 rounds after fear strikes. He may take reactions to defend himself.                                      \\ \hline
		81-100  & Overcome by horror, the character loses consciousness for 1D10-CrB minutes, minimum of 1.                                                                                                                                                                                                                                                                                            \\ \hline
		101-120 & Pure horror pierces the character’s heart. His courage is reduced by 2D10+5 for a week, recovering by 1 each day afterwards. He takes a second shock effect at a value of D100/2.                                                                                                                                                                                                    \\ \hline
		121-140 & Stuck in their worst nightmare, the character falls comatose for a day.                                                                                                                                                                                                                                                                                                           \\ \hline
		141-200 & Fear breaks the character’s mind. He falls into a coma for half a week and his memory of the last 2D10 days is erased. After such a traumatic experience, the character likely develops a mental disorder (a Bane worth 2-3 GP). Player and GM should discuss what this might be.                                                                                                    \\ \hline
		201+    & The character dies from sudden cardiac arrest.                                                                                                                                                                                                                                                                                                                                       \\ \hline
	\end{tabularx}
	\section{Modifiers}
	\label{situationalmodifiers}
	\subsection{General}
	\begin{center}
	\begin{tabular}{|l|l|l|}
		\hline
		\ul{Situation}         & \ul{Modifier} \\ \hline
		Difficulty: Difficult   & -10            \\ \hline
		Difficulty: Hard        & -20            \\ \hline
		Difficulty: Very Hard   & -30            \\ \hline
		Difficulty: Grueling    & -40            \\ \hline
		Difficulty: Punishing   & -50            \\ \hline
		Difficulty: Hellish     & -60            \\ \hline
		Difficulty: Challenging & +0             \\ \hline
		Difficulty: Ordinary    & +10            \\ \hline
		Difficulty: Routine     & +20            \\ \hline
		Difficulty: Easy        & +30            \\ \hline
		Difficulty: Simple      & +40            \\ \hline
		Difficulty: Elementary  & +50            \\ \hline
		Difficulty: Trivial     & +60            \\ \hline
	\end{tabular}
	\end{center}
	\subsection{Melee Combat}
	\begin{tabularx}{\textwidth}{|X|l|l|}
		\hline
		\ul{Situation} & \ul{Modifier} & \ul{Keyword} \\ \hline
		The character attacks below his optimum & -20 & Distance \\ \hline
		The character is attacking slightly outside of reach. & -20 & Distance \\ \hline
		The character is fighting in strong winds, heavy rain or on slippery ground. & -10 & Environment \\ \hline
		The character tries to attack or parry while prone. & -10 & Environment \\ \hline
		The character is fighting a character in mist, fog or smoke. & -20 & Environment \\ \hline
		The character tries to dodge while prone. & -20 & Environment \\ \hline
		The character is fighting in knee deep snow or water. & -30 & Environment \\ \hline
		Fighting an armed opponent while unarmed. & -10 & Equipment \\ \hline
		The character is attempting to use two knives or a sword and a knife at once. & -10 & Equipment \\ \hline
		The character attempts to use a spear one-handed. & -20 & Equipment \\ \hline
		The character is attempting to use two spears at once. & -40 & Equipment \\ \hline
		The character is outnumbered 2 to 1. & -10 & Numbers \\ \hline
		The character and his allies outnumber the enemy 2 to 1. & +10 & Numbers \\ \hline
		The character is attacking a kneeling target. & +10 & Target \\ \hline
		The character attacks a stunned target & +20 & Target \\ \hline
		The character is attacking a prone target. & +20 & Target \\ \hline
		The character attacks an unaware target. & +30 & Target \\ \hline
	\end{tabularx}
	\subsection{Ranged Combat}
	\begin{tabularx}{\textwidth}{|X|l|l|}
		\hline
		\ul{Situation} & \ul{Modifier} & \ul{Keyword} \\ \hline
		The character is shooting over extreme range. & -50 & Distance \\ \hline
		The character is shooting over long range. & -20 & Distance \\ \hline
		The character shoots over short range. & +10 & Distance \\ \hline
		The character shoots at point blank range. & +30 & Distance \\ \hline
		The character attempts to use a pistol one-handed. & -10 & Dualwielding \\ \hline
		The character is attempting to use two pistols at once. & -20 & Dualwielding \\ \hline
		The character attempts to use a small rifle one-handed. & -30 & Dualwielding \\ \hline
		The character attempts to use another weapon one-handed. & -60 & Dualwielding \\ \hline
		The character is attempting to use two small rifles at once. & -40 & Dualwielding \\ \hline
		The character is fighting in strong winds, heavy rain or on slippery ground. Multiple may stack. & -10 & Environment \\ \hline
		The character tries to dodge while prone. & -20 & Environment \\ \hline
		The character is attacking a specific enemy caught up in melee combat or he himself is caught in melee combat. & -30 & Environment \\ \hline
		The character is attempting to fire blindly at an enemy he knows the rough location of. & -30 & Environment \\ \hline
		The character is fighting in knee deep snow or water. & -30 & Environment \\ \hline
		The character is shooting at a character in mist, fog or smoke. & -30 & Environment \\ \hline
		The character is using a long weapon in somewhat confined spaces like a house. & -20 & Environment \\ \hline
		The character is using smgs in very tight corridors or tunnels. & -20 & Environment \\ \hline
		The character shoots from the higher ground. & +10 & Environment \\ \hline
		The character is shooting a crouching target. & -10 & Target \\ \hline
		The character is shooting a prone target. & -20 & Target \\ \hline
		The character attacks a stunned target. & +20 & Target \\ \hline
		The character attacks an unaware target. & +30 & Target \\ \hline
	\end{tabularx}
	\subsection{Social}
	\begin{tabularx}{\textwidth}{|X|X|l|}
		\hline
		\ul{Situation} & \ul{Modifier} & \ul{Focussed skill} \\ \hline
		Performing a simple dance. & -10 / +0 if the character is trained in both etiquette as well as acrobatics & Acrobatics / Etiquette \\ \hline
		Performing a difficult, intricate dance. & -40 / -30 if the character is trained in both etiquette as well as acrobatics & Acrobatics / Etiquette \\ \hline
		The target has something else to do or does not want to be bothered. & -10 & Appeal \\ \hline
		The target is suspicious and/or has had bad experiences with the character. & -20 & Appeal \\ \hline
		The target is hostile but not aggressive yet. & -30 & Appeal \\ \hline
		The target is a devoted enemy and currently in mortal combat with the character. & -60 & Appeal \\ \hline
		The target and the character are aquainted. & +10 & Appeal \\ \hline
		The target is friendly. & +20 & Appeal \\ \hline
		The target is devoted to or close friends with the character. & +30 & Appeal \\ \hline
		Pickpocketing something obvious like an ID card or a phone sticking out of someone's pocket & -10 & Sleight of hand \\ \hline
		Performing a simple magic trick to draw one person's attention. & +10 & Sleight of hand \\ \hline
	\end{tabularx}
	\subsection{Exploration}
	\begin{tabularx}{\textwidth}{|X|l|l|}
		\hline
		\ul{Situation} & \ul{Modifier} & \ul{Focused skill} \\ \hline
		Driving under fire or on difficult terrain. & -20 & Drive / pilot \\ \hline
		Driving a damaged vehicle, still under heavy fire. & -40 & Drive / pilot \\ \hline
		Driving a vehicle for the first time. & +0 & Drive / pilot \\ \hline
		Driving in familiar terrain and regions. & +10 & Drive / pilot \\ \hline
		Controlling a civilian vehicle at moderate speeds or at low speeds in fairly close quarters. & +20 & Drive / pilot \\ \hline
		Controlling a civilian vehicle at low speeds. & +40 & Drive / pilot \\ \hline
		Making out sounds with an engine humming on an idle car right next to the character or light animal chatter in the background. & -10 & Perception \\ \hline
		Trying to make out sounds in a firefight or riot. & -20 & Perception \\ \hline
		Trying to see something or fight in low light or against light. & -20 & Perception \\ \hline
		Trying to make out sounds in a street war. & -40 & Perception \\ \hline
		Trying to fight in total darkness or while blinded. & -60 & Perception \\ \hline
		Trying to make out sounds with large explosions going off. & -60 & Perception \\ \hline
		Listening for footsteps on sandy ground. & +0 & Perception \\ \hline
		Listening for footsteps on wet ground. & +15 & Perception \\ \hline
		Listening for footsteps in tall grass, on gravel or snow. & +20 & Perception \\ \hline
		Listening for footsteps on metal flooring. & +30 & Perception \\ \hline
		Listening for footsteps on grassy ground. & +5 & Perception \\ \hline
		Listening for sounds in echoing environments. & +100\% & Perception \\ \hline
		Hide or draw a small object. & -10 & Sleight of hand \\ \hline
		Hide or draw a fairly large object, like a submachinegun. & -30 & Sleight of hand \\ \hline
		Trying to hide while moving slowly. & -10 & Stealth \\ \hline
		Trying to sneak in armor or heavy footwear. & -10 & Stealth \\ \hline
		Trying to sneak in a strike suit. & -15 & Stealth \\ \hline
		Trying to hide while running. & -40 & Stealth \\ \hline
		Trying to sneak while barefoot or wearing very light footwear. & +0 & Stealth \\ \hline
		Trying to hide while crouching in place. & +10 & Stealth \\ \hline
		Trying to hide while laying prone in place. & +30 & Stealth \\ \hline
	\end{tabularx}
	\subsection{Craftsmanship}
	\begin{tabularx}{\textwidth}{|X|l|l|}
		\hline
		\ul{Situation} & \ul{Modifier} & \ul{Focused skill} \\ \hline
		Creating or repairing equipment with only insufficient or improvised tools. & -20 & Mechanics \\ \hline
		Trying to fix unknown technology. & -40 & Mechanics \\ \hline
		Attempting to repair and use damaged weapon attachments. & +10 & Mechanics \\ \hline
		Reparing a damaged vehicle with the necessary tools. & +20 & Mechanics \\ \hline
		Repairing simple circuitry or devices like antennas. & +30 & Mechanics \\ \hline
		Picking more secure locks like found on motorized vehicles. & -10 & Security \\ \hline
		Defusing an old landmine. & -30 & Security \\ \hline
		Setting up a tripwire or trapping a door. & +10 & Security \\ \hline
		Picking a simple lock like found on a bicycle. & +20 & Security \\ \hline
		Strategically placing a simple lock or chain. & +60 & Security \\ \hline
	\end{tabularx}
\end{document}