\section*{Game Design}
All content has been collected from various sources, modified and joined into a cohesive system by me.\\
Take a look below to find said sources.

\section*{Art}
All artwork was created locally using stable-diffusion.\\
Find it here: \url{https://github.com/AUTOMATIC1111/stable-diffusion-webui}\\
Try it here: \url{https://stablediffusionweb.com/}

\section*{Inspiration}
Various parts of this system were directly inspired by other systems.
\begin{enumerate}
	\item[Halo Mythic] This system was originally supposed to be a small Halo Mythic 4.0 conversion. With more and more changes I wanted to make, it became easier to pretty much start from scratch.\\
		I still advise to try it here: \url{https://www.reddit.com/r/HaloMythic/}
	\item[Warhammer 40k] Many abilities and traits have been inspired by the Warhammer 40k TTRPG systems made by Fantasy Flight Games. They seem to no longer be publicly available, but Cubicle 7 released a spiritual successor in \emph{Imperium Maledictum}.
	\item[The Dark Eye] By far the TTRPG system I have used the most. Melee combat, the initiative system and most of character creation was inspired from this rule set. The version in question - 4.1 - is no longer publicly available and was never really translated to English.
	\item[Technoir] A lot of rules were subtly influenced by this particular system. Playing it has done a lot to change my approach to TTRPGs in general and GMing in particular, so I strongly advise you to try.\\
		Find it here: \url{https://www.technoirrpg.com/}
\end{enumerate}

\section*{Fonts}
"Mission Danger" by \textit{Iconian Fonts - Daniel Zadorozny}\\
"Paladins" by \textit{Iconian Fonts - Daniel Zadorozny}\\
"Legend" by \textit{Artyom Levanov}

\section*{Scripts}
Generally all Lua, Python and Bash scripts have been written by me. All exceptions are noted in comments within the script files.