\chapter{Act I: Pub Crawl}
\label{ch:act1}
\vspace{-20mm} %quickfix
The characters, currently doing R\&R in a safe location,
receive a cryptic message on their comm devices:
\begin{exampleblock}
	\itshape
	Meet at the \hyperref[location:bar]{Blue Lotus Bar}.
	Job offer. Quick and easy.
	In a time crunch, hurry.
	\\%
	-Dusk
\end{exampleblock}
When they reach the bar, the bartender points them to \hyperref[char:dusk]{Evelyn} waiting for them.
She is visibly tense.
She immediately gets to the point:
\begin{sitemize}
	\item She claims to work for Helix Dynamics.
	\item An early AI chip prototype was stolen from Helix Dynamics.
	\item She knows who has it (\hyperref[char:hayes]{Dr Alden Hayes}).
	\item She knows of a data broker, \hyperref[char:rika]{Rika},
		who has the doctor's location.
		You can find her on the \hyperref[location:techbazaar]{Tech Bazaar}.
	\item Retrieve it for her.
	\item She is willing to pay cr600 each.
	\item It'll likely be moved within the next few (meaning 2 or 3) days.
		They'll need to hurry.
\end{sitemize}
\vspace{-5mm}
There is more information,
	which she will not share willingly.
Smart characters may figure out some of the below:
\begin{sitemize}
	\item A fixer should not be a spokesperson for a giant Corp.
	\item For a simple retrieval job that is a massive sum of money.
		Something is likely off; the risk is probably higher than anticipated.
	\item She is on Helix Dynamics' wanted list.
	\item Working with her will get the party on the same list.
\end{sitemize}

\vspace{-5mm}
If the players take too long,
	a group of mercenaries working for Helix Dynamics,
	looking for Dusk,
	enter the Blue Lotus.
Dusk will intend to promptly escape to safety.
