\section{Ranged actions}
\subsection*{Aim}
The character designates a target and takes aim.
For every action aiming the character
	gains a +5 on her next shot against that target,
	up to +20 for 2 full combat rounds.\\
The bonus vanishes when her concentration or line of sight is broken,
	or the target moves more than a tenth of her effective \emph{Perception} in meters per second.
\par
\begin{exampleblock}
	A character with 40 Instinct
		and Trained Perception (granting +10)
		would lose her Aim bonus when the target moves faster than
		5 meters per second
		(or 18 kilometers an hour).
\end{exampleblock}
Without proper installations to assist aiming, only +10 may ever be gained.
Proper installation generally means
	a properly zeroed and intact sight,
	with a magnifier of
	at least 1\%
	and at most 4\%
	the distance in meters.\\
\begin{exampleblock}
	For example at a distance of 200m the magnifier should lie between
		2x and 8x.
	\\%
	Every weapon is assumed to come with Iron Sights that offer "1x magnification".
\end{exampleblock}
This maneuver does not require an ability.
\subsection*{Brace}
A character using a heavy weapon or launcher (that is not mounted)
	needs to find a solid firing position or infers a -20 to hit checks.
Finding such footing takes an action.
Moving from your position, dodging or fighting in melee breaks bracing.
This does not require an ability.
\subsection*{Reload}
The character reloads his firearm. Depending on the weapon used, this can take varying amounts of time which usually may be interrupted if the character needs to dodge.\\
He makes a Reload check. If the character is reloading two weapons simultaneously - such as when dual wielding - the test takes a -40 penalty.
The required time is reduced by one action per degree of success,
	down to a minimum of 1 action.\\
Failing this test has no negative impact, neither do critical successes or failures have special effects.
\subsection*{Assisted reload}
A heavy or launcher weapon can be reloaded with the help of another character instead. In such a case both characters will be occupied for the duration but both characters may reload as a combined action, adding their DoS.
\\%
Failed tests and critical results once again do nothing.
\begin{exampleblock}
	Two characters are reloading an M2 Brass Storm (18 action reload).
	\\%
	One of them rolls 3 DoS, the other fails by 2 DoF.
	Since failure does not matter, the reload time is reduced to 15 actions.
\end{exampleblock}
\subsection*{Single shot}
The character takes a single shot against an enemy.
Aim bonuses are not lost from this action.
This does not require an ability.
\subsection*{Burst (-10)}
The character takes a relatively controlled burst of fire against a target.
This encompasses everything between automatic pistols, heavy machine guns, flamethrowers and sustained arc rifles, even though some of those might not technically fire in bursts.
\\%
For every degree of success on the check one hit is scored,
	up to a maximum of the weapon’s rate of fire in total.
Aim bonuses are lost after shooting.
\subsection*{Suppression Fire (-20)}
The character shoots in the general direction of his enemies, expecting them to keep their heads down so as to not lose them.
Whether a hit is scored or not, all enemies within an area of
	roughly \emph{the bullets fired in meters radius}
	are making Courage checks at a penalty equal to
	4 times the bullets fired.
On a failure they will not leave cover until they either spend an action to retry the courage test (once per turn) or the suppression ends.
\begin{exampleblock}
	Julie, armed with her AR-22, faces a group of opponents.
	Her weapon has a rate of fire of 3.
	\\%
	She rolls an attack to suppress her enemies, scoring 1 DoS.
	She now suppresses an area that is roughly
		3 meters in radius (or 6 meters diameter)
		and one enemy in the area takes one hit (as she scored a DoS).
	\\%
	All enemies in this area need to make a
		-12 Courage test
		(which they may retry as an action)
		or be forced to stick to cover.
\end{exampleblock}
Anything threatening them directly in a situation where they are pinned
	- such as grenades behind their cover -
	will cause them to suffer from \emph{Fear} (see p. \pageref{sec:fear}).
\subsection*{Called Shot (-size modifier)}
The character targets a specific location. This does not require an ability and may modify another ranged maneuver.
\subsection*{Reaction: Dodge (-10)}
A character may attempt to dodge primitive ranged attacks like bows and thrown weapons, as well as move out of blast ranges.\\
When dodging against single ranged attacks, the attack and defense checks are \emph{Opposed}.
If the attacker wins, the target suffers damage.
If the defender wins or the test ties, the attack is evaded.
\\%
When dodging against multiple ranged attacks, the defender dodges one hit per Degree of Success.
The reaction may still only be taken against a single attacker.
\\%
When dodging against explosives, a success may increase the distance to the center of the blast by up to DoS.\\
This maneuver does not require an ability.
