\documentclass[12pt,a4paper,openany]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}
\usepackage{ltablex}

\def\subtitle{GM Companion}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}

	\chapter{Distinctions}
	Neon is vastly different from other TTRPG systems in various ways. Focus here lays on \emph{lethality} and \emph{modularity}.\\
	Any character - be that player or non-player - is always at the risk of dying in combat. The key is sneakiness, cunning or avoiding combat to stay alive against the odds.\\
	Everything in this system is meant to be modular. Keep the parts that work for you, remove that which doesn't and include add-ons if you need other specific mechanics. Player characters don't follow classes - they are comprised of their genetic heritage and their past, and they can become basically whoever they want to be.
	\paragraph{Now, what does this mean for us GMs?}
	\def\hspacepar{5mm}
	\def\vspacepar{-5mm}
	Before we get to play, we need to choose which add-ons we use, ideally in consultation with the players. Some of them - like the narrative rules - slightly adjust how the game plays. Others - like psionics - open up a massive can of worms that the world you're building has to account for.\\
	\hspace*{\hspacepar} Keep in mind that the more moving parts you are using, the more you will need to prepare for, so don't be afraid to exclude modules.\par \vspace{\vspacepar}
	Secondly when the players create their characters, you should make sure their mechanics align with their 20 questions.\\
	\hspace*{\hspacepar} They have many options and may overlook a few things, so remind them: they only know and can only do whatever their Skills and Educations dictate. Conversely when they pick a Bane (especially a Disabling Characteristic), they will suffer from it when the occasion arises, whether the backstory they wrote dictates they should or not.\par \vspace{\vspacepar}
	Lastly, during play a single misstep can mean the end of a character. Variance is high, damage is high and penalties from pain in the wrong situation may spell someone's end.\\
	\hspace*{\hspacepar} Two things to keep in mind here. One: Encourage your players to avoid combat sometimes when they don't feel comfortable they can win. That may not always be possible, especially when a situation goes ass up, but it's nice to have options.\\
	\hspace*{\hspacepar} Also remember that this does not just go for player characters. A stray bullet may take out key antagonists just as likely - so make sure they are taking precautions if you feel the need to show them in person.

	\chapter{Mission Creation}
	\input{components/mission-creation.tex}

	\chapter{Bestiary}
	\section{Hit Locations}
	Not all creatures have to look like humans necessarily; the list at the end of this chapter contains humanoids, quadrupeds, worms and hexapeds. Of course hit locations and location hp differ.
	\input{components/hitlocations.tex}

	\section{Size}
	Larger creatures are more resilient on average. Mechanically this means that HP is multiplied by a factor depending on a creature's size category.\\
	Example: While an \emph{average} humanoid has 25 HP on his body, a \emph{huge} humanoid would have 200\% of that, i.e. 2 times, i.e. 50.
	\begin{tabularx}{\textwidth}{|l|r|}
		\hline
		Minuscule &  50\% \\ \hline
		Puny      &  66\% \\ \hline
		Tiny      &  75\% \\ \hline
		Small     &  88\% \\ \hline
		Average   & 100\% \\ \hline
		Tall      & 150\% \\ \hline
		Huge      & 200\% \\ \hline
		Hulking   & 250\% \\ \hline
		Enormous  & 300\% \\ \hline
	\end{tabularx}

	\section{Tags}
	Creatures may carry tags like \emph{ANIMAL}. Any tag means some collection of traits that these creatures share, whether they are generally similar or not. If you want to create your own creatures, start by adding a tag to an existing creature and reskinning it. Example:\par
	\begin{exampleblock}
		One might say that a bear [an existing creature] by itself is not all that interesting. A \emph{DRUGGED} bear [added a tag] sounds hilarious and much more mechanically engaging but might not exactly be taken seriously by many players. Going on to call it Subject B4R, a recent bio-weapon built by Mishima Zaibatsu for brutal, morale breaking close quarters engagements [reskin] might make for a very interesting plot point and tense encounter.
	\end{exampleblock}
	
	\vspace{5mm}
	\input{components/tags.tex}

	\section{Creatures}
	\input{components/bestiary.tex}

	\section{Hordes}
	Sometimes heroes stand against insurmountable swarms and hordes. Such hordes are created with the following few simple rules.
	
	\subsection*{Size}
	With numbers increasing, so increases the size of the horde, i.e. the space they take up. For every factor of 4 the size increases by one category.
	\begin{exampleblock}
		\itshape A single bat is puny, 4 bats are tiny, 16 (=4*4) are small and so on. When a horde decreases in size as it loses members is up to the GM.
	\end{exampleblock}
	
	\subsection*{Resilience}
	Swarms and hordes have vastly different vulnerabilities than single targets. For this reason we follow the rules below:
	\begin{itemize}
		\setlength\itemsep{-8mm} \vspace{-8mm}
		\item The horde's armor and toughness rating is the average armor and toughness of all members.
		\item If at least one point of damage is dealt to the horde, one member is incapacitated. There are however a few notable exceptions:
			\begin{itemize}
				\setlength\itemsep{-8mm} \vspace{-8mm}
				\item Weapons with the \emph{Blast} rule take out an amount of members equal to the Blast radius.
				\item \emph{Spray} weapons take out an amount of members equal to a third of their range in meters.
			\end{itemize}
	\end{itemize}
	
	\subsection*{Actions}
	In combat a horde acts as a single entity but gains 2 bonus actions every time its size increases. These bonus actions may be offensive, defensive or utility-driven. \\
	Note, however, that hordes never have to reload. They represent "a bunch of creatures", not professional 17th century firing lines.
	
	\section{Companions}
	A player may ask for a companion. If it is just a pet, you can easily ignore this section. If it is supposed to have mechanical advantages (like combat assistance), follow the steps below.
	\subsection{Prerequisites}
	The character should have either the \textit{Companion} or \textit{Mighty Companion} ability and no other companion so far.\\
	If the player character does not have the ability but has great chemistry with an NPC, you may give them a discount (see \textit{Unique Experience} in Narrative Rules).\\
	With GM permission any character may acquire multiple companions at any given time, requiring multiple instances of the same ability. \textit{Note however that many companion will slow down combat considerably.}
	\subsection{Picking}
	Valid to be companions are any creatures with a Combat Difficulty of up to 1 (or up to 3 in case of a \textit{Mighty Companion}) that don't have the CERBERUS or LEGION trait or that the GM otherwise deems inappropriate.\\
	Notice that the companion is not chosen by the player but it is offered by the GM, taking into account the player's wishes.
	\subsection{In Effect}
	The companion will assist the group in reasonable ways, this includes in exploration and combat. However this should not include social encounters - because the GM talking to imself is simply not interesting - nor riddles - as it makes them completely redundant.\\
	A companion should supplement whatever the characters can do already or compensate individual (but not overall) weaknesses.\\
	Also keep in mind that a companion should always be inferior to the player characters, otherwise the player character would be the companion...
	\subsection{The Worst Case}
	There is always a chance for the companion to be crippled or lethally wounded. In case the companion is effectively lost, the player character may adopt another companion in its stead, using the same ability he already has. It will however require the following:
	\begin{itemize}
		\item The character needs to acknowledge the companion's death.
		\item The character is offered a new companion, when he has developed a fitting relationship to another NPC.
		\item If the character acquired his ability at a discount, he has to pay the difference when adopting the new companion.
	\end{itemize}
	

	\chapter{Nemesis}
	Very special, personal enemies might be classified as \emph{Nemesis}. They should be few and far between and have a personal connection to one player character or even the whole party.\\
	To make them special mechanically as well they should gain 20-25 GP in Boons, 10-15 GP in Banes and one or two Nemesis Abilities. They may be chosen from the list below or made up.
	\section*{Nemesis Abilities}
	The following section contains a list of possible Nemesis abilities. It is by no means comprehensive.
	{\setlength{\extrarowheight}{5pt}
	\begin{tabularx}{\textwidth}{l|X}
		Ability & Effect\\
		\hline
		\textbf{Blooded} & The Nemesis is incredibly jaded and resilient. He ignores any pain and fear.\\
		\hline
		\textbf{Charismatic} & The Nemesis is charismatic and kind to his underlings. Anyone not hostile towards him will support him in a fight to the best of their abilities.\\
		\hline
		\textbf{Conniving} & The Nemesis is prepared for everything. Once per day when failing a test, he may decide to pass with D5 DoS instead, as he planned for exactly this occasion. If his opponent does something absolutely bananas, the GM may rule even this ability to be outclassed.\\
		\hline
		\textbf{Cruel} & The Nemesis is a heartless individual. Once per encounter he may make an Intimidate test, causing fear in its opponents. Each time a character sees him after the first, the test gains cumulative a bonus of +10.\\
		\hline
		\textbf{Fanatical} & The Nemesis is obsessed and nothing will stop him. He can ignore any and all modifiers that directly distract him from his goal, be that pain, exhaustion, sleep deprivation or someone talking at him while he's driving. While he is blinded by that goal however, his Instinct is reduced by 20.\\
		\hline
		\textbf{Foresightful} & The Nemesis can almost see the future. His instinct is increased by 10 and deceptive maneuvers like \emph{Faints} don't work against him, nor will he ever lose initiative from dirty tricks.\\
		\hline
		\textbf{Honor-bound} & The Nemesis will never stab someone in the back, in turn he has become a great duelist. While in a one-on-one fight - be that melee or shootout - he gains a +15 to combat tests. Otherwise he will gain a -10 to combat tests.\\
		\hline
		\textbf{Masked} & The Nemesis' facial features are very unremarkable and he knows to use this as an advantage. When the Nemesis dies and the body is not closely investigated, it may turn out later that the corpse is just a double.\\
		\hline
		\textbf{Reputable} & The Nemesis is generally well regarded; this means that characters who speak out against him at the wrong place or the wrong time will quite possibly suffer dire consequences.
	\end{tabularx}}
	\section*{Keep In Mind}
	Horde rules may work for every type of creature - technically. However, your miles may vary if you use these rules for smart or extremely large creatures. Hordes are much flimsier and - in a way - less dangerous than single creatures.

	\chapter{Patrons \& Contacts}
	On the opposite side of the Nemesis lay the contacts and patrons - the powerful allies. Usually their individual stats are not that important, it is what they represent: influence, knowledge and goods.
	\section*{Personality}
	We cannot create a character without a personality, so we will start here. There are two basic options to create a personality.\\
	Firstly we can answer the same \emph{20 questions} as the player did for their characters. This process takes a long time but is also incredibly precise and will make for a very fleshed out character. This may be a good choice if the player characters are sent on their way time and time again by the same person.
	\emph{Alternatively} we can go through the following simple steps. It is much faster but possible contradictory.
	\begin{enumerate}
		\setlength\itemsep{-8mm} \vspace{-8mm}
		\item \textbf{Specialties}: What can the character do extremely well and what does she like to do? Anything can work here but don't overdo it.
		\item \textbf{Iniquity}: Under which vice does she (moreso her surroundings) suffer? An easy source are the seven deadly sins, alternatively find something or \emph{someone} she is afraid of.
		\item \textbf{Quirk}: Some quirk makes a character come alive. A speech disorder, an obsession, a physical dependency on chewing gum. It doesn't have to be actually impactful, it just has to be human.
		\item \textbf{Goal}: What goals does the patron pursue? She will not offer assets that conflict with her goal or be reluctant when the deal seems too good.
	\end{enumerate}
	\section*{Assets}
	The assets they offer is often the actual first step in creating a patron as it is the reason to create such a patron. Examples include:
	\begin{enumerate}
		\setlength\itemsep{-8mm} \vspace{-8mm}
		\item Transportation
		\item Black Market Access
		\item Medical Assistance
		\item Intel
		\item Firepower
	\end{enumerate}
	\section*{Costs}
	Tying directly into the assets offered: what does it cost the player characters? Again, many things can work here, e.g. money, protection, favors.
	\begin{exampleblock}
		\itshape A mob boss selling forbidden goods will expect large amounts of money for their services.\par
		A hacker known to one of the player characters will not necessarily want to get paid but may make dangerous enemies that he needs protection from.
	\end{exampleblock}
\end{document}