	\section{Abilities}
\label{abilitylist}
\vspace{3mm}
\begin{multicols}{2}
\ability{Advanced Parry}{400}{Overly Cautious}{When parrying multiple hits, distribute DoS among any amount of attackers. Still requires more DoS than the opponent for single hits. Can also parry Flexible weapons.}
\ability{Alpha Strike}{500}{From the shadows, no Beta Strike}{Successfully attacking an unaware target automatically hits critically.}
\ability{Assassin Strike}{350}{Acrobatics Trained}{Scoring a critical hit or deathblow in melee allows the character to move up to his speed in meters right away without provoking opportunity attacks.}
\ability{Bar Fighter}{250}{Quaffing Trained}{Ignore "Improvised" penalties.}
\ability{Battle Mind}{400}{Intelligence 40}{The character may use intelligence instead of instinct for initiative calculation.}
\ability{Battle Sense}{500}{Perception Trained}{Adds a fifth of Perception Bonus (2, 4, or 6) to initiative.
	Doubles penalties to attacks of opportunity against the character.}
%TODO: rework!
\ability{Beta Strike}{500}{Constitution 40, no Alpha Strike}{Cause a level of exhaustion to an enemy for every 3 attacks targeted at him.}
\ability{Blind Fighting}{300}{Trained Sense: Hearing}{Limits the penalties for being blinded in melee combat to -10.}
\ability{Blurry}{250}{Acrobatics Trained, Athletics Trained}{While sprinting the character imposes a -20 to everyone trying to hit him.}
\ability{Broken}{450}{Courage 40}{Grants +30 to fear and pinning tests but doubles penalties from bad reputation or disposition.}
\ability{Butcher}{400}{no Earth Shaker}{Damage dealt with blades is increased by 1 for one-handed weapons and 2 for two-handed weapons.}
\ability{Calculated Pilot}{300}{Instinct 30, Dexterity 30}{Halves penalties for piloting tests in demanding, stressful situations.}
\ability{Calming Focus}{350}{Courage 40}{Re-roll one failed fear or pinning test per turn.}
\ability{Calming Presence}{200}{Command Trained, Calming Focus}{The character may take an action to make a command test at a +20 bonus. For every degree of success all allies he addresses gain a +10 to tests to resist fear and pinning.}
\ability{Clear Target}{300}{Ranged Base 30}{Halves penalties for calling hit locations on ranged attacks.}
\ability{Clotter}{300}{Constitution 55}{When starting to bleed, make a toughness check at a -10 penalty. On a success the character doesn't bleed.}
\ability{Companion}{200}{per GM discretion}{The character may adopt a small companion. The GM will explain the details.}
\ability{Crack Shot}{500}{Perception Trained, Clear Target}{Before taking a shot, make a perception check at a penalty equal to twice the target location armor. On a success halve the armor for this attack. Has no effect on shields.}
\ability{Dominion}{350}{Supreme Awareness}{When taking a Defensive Stance and not moving, the control area is increased to 360°. The character may also gain attacks of opportunity against disengaging enemies.}
\ability{Drunken Master}{300}{Bar Fighter}{Limits the penalty to melee combat resulting from intoxication to -10.
	While intoxicated he himself is at a -20 to hit
	and can use maneuvers as normal.\\
	Costs half as much for \textit{balanced} characters.}
\ability{Dual Wielding}{250}{Instinct 30, Dexterity 40}{Halves penalties for dual wielding. Has to be taken once for melee and once for ranged separately.}
\ability{Earth Shaker}{400}{no Butcher}{Damage dealt with blunt weapons is increased by 1 for one-handed weapons or 2 for two-handed weapons.}
\ability{Executioner}{350}{Trained Sense: Smell}{Grants +10 to hit bleeding targets.}
\ability{Expert Wrestler}{350}{Melee Combat Training (Grappling) Experienced}{The character is incredibly well-trained in grappling that he can initiate a Hold as a free action.}
\ability{Face Breaker}{300}{Dexterity 30, Agility 30, Stunning Blow}{Grants unarmed strikes the Trauma special rule.}
\ability{Fighting Retreat}{400}{Battle Sense}{Allows a single attack to be made when disengaging. This attack counts as being performed in movement.}
\ability{Flip Up}{300}{Acrobatics Trained}{When standing up, reduce the time it takes by an action: prone to standing now takes one action or a free action and a successful agility test.}
\ability{Focused Frenzy}{350}{Instinct 30, Intelligence 40, no Unbridled Rage}{When the character is made to go berserk by some means, they can still identify friend and foe as well as take defensive actions, albeit at a -15 penalty.}
\ability{Formation}{300}{Intelligence 35}{When taking Combined Actions, everyone involved is granted a +10,
	up to +30 when three or more characters have Formation.
	When \emph{Unbreakable Bond} partners also have Formation,
	those two gain an additional +10.}
\ability{From The Shadows}{250}{Overly Cautious}{During the first round of combat the character has 6 additional initiative, unless the character was ambushed or similarly caught off guard.}
\ability{Gruesome}{450}{Intimidate Experienced}{When destroying body locations or landing a killing blow, the character makes an Intimidate test with a bonus equal to twice the last attack's damage. All fear tests suffer an additional penalty equal to 10 + 5 per DoS.}
\ability{Hand-To-Hand Basics}{250}{Combat Training (Striking or Grappling) Trained}{When fighting armed enemies, the character counts as armed as well.}
\ability{Hax0r e1337}{400}{Computer Operation Experienced}{Add two degrees of success to any Computer Operation tests to crack other devices or protect your own.}
\ability{Heroic}{400}{Courage 40}{Grants +15 to fear and pinning tests.}
\ability{High Noon}{500}{Combat Training (Pistol) Experienced, Quick Draw}{When drawing a pistol, the character may take a single shot as a free action.}
\ability{Iron Fist}{450}{Hand-to-hand Basics, Maneuver: Stunning Blow}{Every unarmed strike may now count as a having Stun(0) without inferring a penalty.}
\ability{Lead Storm}{350}{Strength 45}{Weapons with a fire rate of more than 1 which are not launchers always count as braced.}
\ability{Light Sleeper}{250}{Overly Cautious}{Overly Cautious now also works when sleeping or intoxicated.}
\ability{Marksman}{300}{Perception Experienced}{Halves penalties for long ranges.}
\ability{Medical Insight}{400}{Medication Experienced}{Doubles the degrees of success on Medication tests to help others recover.}
\ability{Mighty Companion}{500}{per GM discretion}{The character may adopt a powerful companion. The GM will explain the details.}
\ability{Mobile Combat}{250}{Dexterity 30, Agility 40}{Halves penalties for fighting while moving. This includes a Charge maneuver's flat penalty if the character also has Maneuver: Charge.}
\ability{Natural Geek}{350}{Intelligence 45}{Halves penalties to mental tasks resulting from not knowing what you're doing.
	This may include Weapon Training and Skills
	but does not include tasks in stressful situations (like open combat)
	or purely physical actions
	- no matter how apt,
	thinking won't make him lift heavier weights.}
\ability{On Your Feet!}{100}{Command Trained, Heroic}{The character may take an action to make a command check. On a success an ally gains a +5 per degree of success to any action following the character's orders.}
\ability{One-Man Artillery}{350}{Strength 45}{Launchers always count as being braced.}
\ability{Overly Cautious}{300}{Instinct 30}{The character becomes jittery or nervous,
	but he can ignore Unaware conditions by passing a simple Perception check,
	so long as he is not asleep, intoxicated or otherwise impaired.}
\ability{Peer}{100}{Charisma 30}{Gain +15 to interaction tests with a specified group of people.
	May be chosen once per group of people.}
\ability{Perfectionist Craftsman}{400}{Experienced in a crafting skill}{Doubles the degrees of success on crafting tests when the specific skill is used.\\
	May (theoretically) be taken once per skill.}
\ability{Personified Inspiration}{500}{Charisma 40, Heroic}{When the character does a daring or heroic deed, all allies present are immune to fear and pinning for the rest of the encounter or scene.}
\ability{Precision Strike}{300}{Melee Base 30}{Halves penalties for attacking small targets with melee attacks.}
\ability{Protective Stance}{250}{Instinct 40, Constitution 40}{When taking a Defensive Stance, the character may turn active actions into reactions without penalties and he may parry for allies within his melee range.}
\ability{Provoke}{350}{Courage 45}{Spend an action to taunt an enemy and make a skill test opposed by the target's restraint. If the character wins, the target must attack the character at the next opportunity.}
\ability{Quick Draw}{250}{Dexterity 30, Agility 30}{Draw smaller equipment pieces, pistols and one-handed melee weapons as a free action.}
\ability{Rapid Reload}{300}{Dexterity 40, Reload Experienced}{When reducing reload time to below 1 action, reload as a free action.}
\ability{Reliable Reputation}{200}{Charisma 40, no Broken}{Halves penalties from bad disposition.}
\ability{Render}{400}{Strength 55}{When dealing damage with the Tearing rule, roll an additional dice. Still only keep one.}
\ability{Revenge}{400}{Broken}{When taking damage from a direct attack, you may forego one of your actions later in the combat round to immediately attack the offending enemy.}
\ability{Ripper}{350}{Render}{When dealing damage with the Tearing rule and rolling doubles,
	you may choose those two dice
	(instead of keeping just one).}
\ability{Sidearm}{250}{Dual Wielding Melee \& Ranged}{When attacking in melee combat with a melee weapon in one hand and a pistol in the other, the character takes no penalties from shooting in melee combat.}
%I have determined that there are enough ways to bypass armor using maneuvers
%\ability{Skinner}{500}{Perception Trained}{Before taking a melee attack, make a perception check at a penalty equal to twice the target location armor. On a success halve the armor for this attack.}
\ability{Skull Taker}{500}{Clear Target or Precision Strike}{Removes penalties from calling hit locations for ranged attacks (when combined with Clear Target) or melee attacks (when combined with Precision Strike).}
\ability{Snapshot}{350}{Steady Aim}{Aiming takes half as long.}
\ability{Stabilization}{300}{Medication Trained}{The character is able to staunch bleeding in one round.}
\ability{Steadfast}{200}{Agility 30, Constitution 30}{Tests to prevent falling over are at a +10.}
\ability{Steady Aim}{250}{Intelligence 40, Strength 30}{When aiming, line of sight may be broken for a round without aiming being interrupted. By GM discretion this may count even longer if the target is moving particularly predictably.}
\ability{Strong Back}{350}{Strength 55}{The character's carry weight is increased by half.}
\ability{Supreme Awareness}{350}{Instinct 55 or Light Sleeper}{Roll twice when determining initiative or gathering senses, picking the higher result.}
\ability{Tactical Advance}{350}{Command Known}{While advancing carefully from one cover to the next over a distance of MS meters in one turn, the character counts as in cover for the whole way.}
\ability{The Best Defense}{300}{Courage 40}{Reduces offensive penalties of Defensive Stance by 20.}
\ability{Thick Skull}{400}{Constitution 50}{Grants immunity to the Trauma special rule.}
\ability{Threatening Presence}{450}{Intimidation +10, no Calming Presence}{Impose a -15 penalty to enemies' tests against fear and intimidation.}
\ability{Too Angry To Die}{200}{Courage 40, Constitution 40}{While frenzied,
	the character has to take at least 8 damage at once or lose his head in order to die.
	Bleeding out only starts when the character stops frenzying,
	but he will in this case be unconscious when frenzy ends.}
\ability{Trained Sense}{250}{Perception Trained}{Grants a +10 bonus to sensory checks using that sense. Can be taken once for every sense.}
\ability{Unbreakable Bond}{250}{being good friends; if one is Clumsy and the other is Cursed by Fortuna, the cost is only 100 XP}{When around one particular close friend, that friend may make a +20 charisma check as a free action and every degree of success gives the character +10 to resist fear and pinning,
	as well as potentially the effects of disabling characteristics.
	If both of them have Unbreakable Bond,
	the bonus to the charisma check is +40 instead.}
\ability{Unquestioned}{500}{Reliable Reputation}{Penalties to Command tests resulting from disbelief in authority (e.g. represented by Rebel or some Bound by Principle) do not apply.}
\ability{Unrestrained Reflexes}{300}{Agility 35, Dodge Trained}{The character may make an additional dodge action using the same reaction. This may happen once per turn.}
\ability{Vault}{300}{Agility 30, Strength 30}{The character can use suitable objects in the environment to double jump height and leap length during movement without slowing down.}
\ability{Volume of Fire}{350}{Ranged Combat Training (Heavy) Known}{When using a weapon with a rate of fire above 1 to take a standard shot, the character may spend more ammunition to gain a +5 to hit per shot fired after the first, up to the weapon's rate of fire.}
\ability{Walk It Off}{350}{Constitution 40}{The character can continue acting while bleeding until completely bled out. If combined with Tough as nails, the character may enter a frenzy when bleeding as well.}
\ability{Where It Hurts}{400}{Hand-to-hand Basics, Strength 40}{The character's unarmed attacks may gain the Tearing special rule.}
\end{multicols}

\vspace{-5mm}
\subsection{Maneuvers}
\vspace{8mm}
\begin{multicols}{2}
\maneuver{Attack of Opportunity}{150}{Instinct 30, Agility 30}
\maneuver{Bind}{200}{Instinct 35, Dexterity 35}
\maneuver{Burst}{200}{Dexterity 30, Strength 35}
\maneuver{Called Jab}{100}{Maneuver: Feint, Perception Known}
\maneuver{Charge}{100}{Maneuver: Knockdown, Agility 40}
\maneuver{Cleave}{100}{Maneuver: Knockdown, Courage 40, Instinct 40}
\maneuver{Crushing Blow}{300}{Maneuver: Powerstrike, Courage 50, Strength 60}
\maneuver{Disarm}{100}{Maneuver: Feint, Maneuver: Bind}
\maneuver{Feint}{200}{Dexterity 35, Agility 35}
\maneuver{Flurry}{100}{Maneuver: Feint, Dual Wield (Melee)}
\maneuver{Intercept}{100}{Maneuver: Bind, Courage 50}
\maneuver{Knockdown}{100}{Maneuver: Powerstrike, Strength 45}
\maneuver{Piercing Thrust}{300}{Maneuver: Called Jab, Courage 40, Dexterity 40}
\maneuver{Powerstrike}{200}{Strength 35}
\maneuver{Reversal}{300}{Maneuver: Intercept, Courage 60, Instinct 50}
\maneuver{Shift}{100}{Maneuver: Feint, Instinct 40, Dexterity 35, Agility 35}
\maneuver{Stunning Blow}{100}{Maneuver: Powerstrike, Intelligence 35}
\maneuver{Takedown}{100}{Maneuver: Feint, Agility or Strength 40}
\end{multicols}
