\section{Banes}
\begin{multicols}{2}
\bane{Addiction}{The character is addicted to a substance. A week of withdrawal will cause a level of exhaustion every day which are not naturally regenerated anymore. Other exhaustion still regenerates naturally until two weeks of withdrawal. This only applies to uncontrolled withdrawal, not to therapy.}{10}{}
\bane{Agoraphobia (DC)}{The character is afraid of wide, open places.}{1}{per 5}
\bane{Annoying Voice}{The character has an annoying voice. This grants -10 to social tests that involve talking.}{5}{}
\bane{Arrogance (DC)}{The character believes to be superior to others.}{1}{per 5}
\bane{Backwoods Customs}{Even though most cultures have melted, the character has grown up outside the core of society. He has internalized customs that some would call barbaric.}{5}{}
\bane{Bad Reputation}{The character has some sort of bad reputation, either from well known deeds or from known genetic markers. If he is talking to someone who knows of this, he gains a penalty equal to 5 times the boon's level. Can be taken up to level 10.}{2}{per level}
\bane{Bathophobia}{The character is afraid of depths. This may trigger at the bottom of the ocean just as much as it could in a massive canyon.}{1}{per 10}
\bane{Belief in authority (DC)}{The character believes in authority and tends to believe them. Not compatible with Rebel.}{1}{per 10}
\bane{Berserk Rush}{When the character is thoroughly enraged or he is influenced by substances that boost courage, he falls into a frenzy. Resisting frenzy from other sources is at a -30 penalty.}{15}{}
\bane{Blind}{The character can't see. This is due to nervous or brain damage and can't be fixed via augments.}{40}{}
\bane{Blood Lust (DC)}{Lust for bloody combat drives the character. She likes taking the time to make her victims suffer and might end up causing trouble for herself and her group due to this.}{1}{per 10}
\bane{Bound by Duty}{The character is obliged to follow a certain person's or group's commands. If she disobeys, there might be severe consequences.}{12}{}
\bane{Bound by Principle}{The character is bound by her own principles. They are central moral values that may rarely be bent and almost never broken. If they are, doubts will follow the character for at least a week, inferring a -40 penalty to anything requiring focus. By GM discretion these penalties might function slightly differently depending on the situation.}{12}{}
\bane{Caring (DC)}{The character is overly caring for his peers. He will take great risks to help others.}{1}{per 5}
\bane{Claustrophobia}{The character is afraid of small, narrow places.}{3}{per 10}
\bane{Clumsy}{Critical failures occur on a roll of 96 and above.}{20}{}
\bane{Colorblind}{The character is incapable of seeing colors. When she wants to identify something that is only discernible by color, she takes a -20 penalty. This also counts for ranged attacks against large or smaller targets.}{5}{}
\bane{Curiosity (DC)}{When there is something to know, the character will want to know, whether it is of concern or not.}{1}{per 5}
\bane{Cursed by Fortuna}{When a bad event hits the group, this character is much more likely to be hit in particular. Also once per session the GM may declare a success to be a failure instead.}{15}{}
\bane{Debt}{The character is indebted to someone. The loaner will require regular payments or the character will suffer consequences depending on their relationship and the type of people they are.}{1}{per 1000 cr}
\bane{Delusions of grandeur (DC)}{The character tends to overstate and overestimate her own ability and take on monumental tasks with delusional confidence.}{1}{per 5}
\bane{Dietary Rules}{The character will only eat certain things due to personal reasons. Whenever the character is forced to eat something that does not align with his values, e.g. as to not starve to death, this infers penalties equal to the bane's value.}{5}{}
\bane{Directionally Challenged}{The character has extreme difficulty distinguishing left from right. This makes navigation quite difficult: navigation and navigation-related tests - like tests made in a chase - are at a -10.}{5}{}
\bane{Dwarfish}{The character is tiny. He is harder to hit, has less melee range and is slower. He is also rarely taken seriously.}{8}{}
\bane{Envy (DC)}{When another has something that the character does not, she will overstep boundaries to get some of her own.}{1}{per 10}
\bane{Evil Monologue}{The character tends to talk to herself. This may lead to embarrassing social encounters or even to spilling information about secret plans.}{5}{}
\bane{Fear of heights (DC)}{The character is followed by an everlasting fear of falling.}{3}{per 10}
\bane{Flimsy}{Medical Toughness reduced by 1. Can be taken multiple times.}{2}{each}
\bane{Food Restrictions}{Due to mutation or specific engineering, the character can only consume certain types of food. Anything else leaves the body undigested; often times violently.}{5}{}
\bane{Forgetful}{The character tend to forget even the most important details. Any checks made to remember specific details suffer a -20.}{5}{}
\bane{Gambler (DC)}{The character will not pass up on a good bet. When he can play a more or less fair game for something, he has a hard time passing up the chance.}{1}{per 5}
\bane{Greed (DC)}{Getting more money is great.}{1}{per 5}
\bane{Hallucinations}{Hallucinating characters live in a notably vastly different reality, e.g. thinking that milk is a deadly poison, that he is haunted by demons only vulnerable to supersonic cheese and so on. Every person will notice and this will infer penalties as per GM discretion.}{10}{}
\bane{Hesitant}{The character suffers a -3 to initiative.}{5}{}
\bane{Hungry I/II/III}{The character needs 1.5/2/3 times as much food.}{5}{per level}
\bane{Impaired Sense}{One of the character's senses functions improperly, incurring -20 on checks based on that sense. This may be offset with augments but never restored to normal levels. Not compatible with Outstanding Sense for the same sense.}{5}{}
\bane{Impatient (DC)}{The character does not like waiting. Tasks that take a long time of not doing much will be severely harder.}{1}{per 5}
\bane{Impulsive}{The character tends to act on stupid decisions in the heat of the moment. When such an idea comes up, it takes a -20 intelligence check to resist acting on it.}{5}{}
\bane{Insomnia}{Getting a good night's rest is hard for the character. In roughly a quarter of all nights (whether randomly or following a pattern) the character takes a -30 penalty to regenerating naturally.}{7}{}
\bane{Laziness (DC)}{The character is a slob and doesn't put more effort into things than absolutely necessary.}{1}{per 5}
\bane{Light sensitivity}{The character hates the light. Every action taken in light is at a -30 penalty. Protection from the light is generally enough work and requires enough equipment that the sheer bulk grants similar penalties.}{10}{}
\bane{Ignorant (DC)}{The character has a hard time understanding a certain topic. This topic should be specified when the Bane is chosen.}{1}{per 10}
\bane{Naive (DC)}{The character easily trusts strangers. Resisting deception and persuasion is at a penalty equal to the Bane.}{1}{per 5}
\bane{Necrophobia}{The character has fear of death and dead creatures and will be unable to focus properly when on battlefields, murder or slaughter scenes or graveyards.}{1}{per 5}
\bane{Needy (DC)}{The character's strong physical desires become distracting to everyday life.}{1}{per 10}
\bane{Nervous}{Rayleigh Index reduced by 1. Can be taken multiple times.}{2}{each}
\bane{Neurotically Hygienic (DC)}{The character has a need to keep clean.}{1}{per 5}
\bane{Night blind}{Doubles all penalties for low light.}{5}{}
\bane{No tactile sense}{Anything requiring sense of touch takes a -40 penalty, this includes any weapon with a trigger or a blade.}{15}{}
\bane{Nyctophobia (DC)}{The character has a strong fear of the dark.}{2}{per 5}
\bane{Obese}{The character is heavily overweight. This comes with multiple drawbacks like a -20 penalty to strength based checks that have to do with body weight (e.g. climbing), -3 to medical toughness, as well as stigmatization and other drawbacks by GM discretion.}{15}{}
\bane{One-armed}{The character has lost an arm and due to nerve damage can't accept replacements.}{15}{}
\bane{One-eyed}{The character has lost an eye and due to nerve damage can't accept replacements.}{5}{}
\bane{One-handed}{The character has lost a hand and due to nerve damage can't accept replacements.}{10}{}
\bane{One-legged}{The character has lost a leg and due to nerve damage can't accept replacements.}{25}{}
\bane{Paralyzed Leg}{Due to irreversible nervous damage the character can barely move one leg. This reduces speed by 2 and grants penalties around -15 to tests as per GM discretion.}{15}{}
\bane{Personal Enemy}{An important person or group has set its eyes on the character and will take measures to foil his plans.}{7}{}
\bane{Physically Repulsive}{The character is staggeringly ugly. This infers a -20 penalty to social tests when the character can be seen. Not compatible with Smoking, Looker and Ugly.}{12}{}
\bane{Playful (DC)}{The character loves playing. That can include simple things like chess or video games, but also "games" of predator and prey.}{1}{per 5}
\bane{Portly}{The character is stocky or otherwise slower than her peers. Her speed is reduced by 1.}{5}{}
\bane{Prejudice (DC)}{The character is biased against a certain group of people and has a hard time interacting with them.}{1}{per 5}
\bane{Rebel (DC)}{The character has a hard time trusting authority and tends to revolt. Not compatible with Belief in authority.}{1}{per 10}
\bane{Righteous (DC)}{Some laws are absolute and they must be followed. The character will work against any injustice to the order she believes in.}{1}{per 5}
\bane{Scrooge (DC)}{Spending money is painful.}{1}{per 10}
\bane{Second-class Citizen}{The character is oppressed for one reason or another. This may e.g. be due to stigmatization of a part of his lifestyle or being born with extremely few resources. In any case this will have consequences in social situations and encounters with law enforcement.
	Cannot be taken by Vat-grown.}{5}{}
\bane{Sensitive Smell (DC)}{When around something that smells particularly nasty, he takes penalties to everything that requires concentration or a healthy stomach equal to the bane.}{3}{per 10}
\bane{Short}{The character is small. He is harder to hit, has less melee range and is slower. He is also rarely taken seriously.}{5}{}
\bane{Shortcoming}{A characteristic, that hasn't been invested in, is reduced by 5.}{7}{}
\bane{Sickly}{Grants -15 penalty to resist disease.}{2}{}
\bane{Slave Mentality (DC)}{The character does not like making his own decisions. Such situations put a lot of stress on the character.}{1}{per 5}
\bane{Slow Healer}{The character only heals naturally at a -20 penalty and tests taken to heal this character are at a -10.}{10}{}
\bane{Speech Disorder}{The character has some sort of speaking disorder. What it may be, the character gains a -10 to tests requiring to speak and takes longer to finish sentences which might cause problems in stressful situations like combat or a heated chase.}{7}{}
\bane{Squeamish (DC)}{The character takes a penalty to tests to resist fear and panic.}{2}{per 5}
\bane{Technophobia (DC)}{The character is suspicious of technological advancements, especially solutions to things that could easily be done by humans.}{3}{per 10}
\bane{Temperamental (DC)}{Small things may make the character unreasonably angry.}{3}{per 10}
\bane{Terrible Odor}{The character has bad smell. This grants -10 to social tests when the character is in smelling distance and hiding from watchdogs is essentially impossible. Not compatible with Pleasant smell.}{5}{}
\bane{Trigger Phrase}{Sleeper agents were rumored to have trigger phrases carved into their mind. For the longest time that was purely a myth but now many vat-grown are programmed with such a phrase to force certain behavior. When the phrase is heard by the character, all tests to resist persuasion and commands is at a -20 penalty.}{7}{}
\bane{Trouble Magnet (DC)}{Some people actively look for trouble. This character has the tendency, willingly or not, to provoke and attract the wrath of others.}{1}{per 10}
\bane{Ugly}{The character is unshapely. This grants -10 to social tests while the character is being seen. Not compatible with Smoking, Looker and Physically repulsive.}{5}{}
\bane{Uneducated}{The character has not learned much and loses 50 XP. Can be taken multiple times but XP may never be negative.}{1}{per level}
\bane{Vanity (DC)}{The character is posh to an extreme. He might refuse tube food, simple and cheap clothing or getting dirty.}{1}{per 5}
\bane{Vengeful (DC)}{The character does not forget. When someone wronged him, he will make sure to pay them back tenfold.}{1}{per 5}
\bane{Wanted I-V}{The character is being looked for by an organization. This can be due to criminal record, corporate espionage or involvement in gang wars. The first step roughly describes being the target of a small mercenary or criminal group, a level 3 target would be a low-priority military target and a level 5 target is on LEGION's radar.}{5}{per level}
\end{multicols}