	\section{Fear}
\label{feartable}
\begin{tabularx}{\textwidth}{|l|X|}
	\hline
	1-20    & Shivering, the character takes a -10 penalty on his tests until he passes a courage check. He can spend one action to attempt this check.                                                                                                                                                                                                                                            \\ \hline
	21-40   & Severely shaken, the character takes a -15 penalty on all tests for the rest of the encounter or scene and can't use maneuvers or transform actions.                                                                                                                                                                                                                                 \\ \hline
	41-60   & Dumbstruck by fear, the character freezes in place and can’t act until he passes a courage check at the end of one of his turns. This check begins at the same penalty as the initial one and gets a cumulative +10 for every previous attempt. He may take reactions to defend himself or run away (at an increased risk of stumbling as quickly avoiding obstacles is “acting”...) \\ \hline
	61-80   & Frozen by terror, the character is completely unable to move until he passes a courage check at the end of one of his turns. This check begins at the same penalty as the initial one and gets a cumulative +5 for every previous attempt. Courage checks are allowed 1D5-1 rounds after fear strikes. He may take reactions to defend himself.                                      \\ \hline
	81-100  & Overcome by horror, the character loses consciousness for 1D10-CrB minutes, minimum of 1.                                                                                                                                                                                                                                                                                            \\ \hline
	101-120 & Pure horror pierces the character’s heart. His courage is reduced by 2D10+5 for a week, recovering by 1 each day afterwards. He takes a second shock effect at a value of D100/2.                                                                                                                                                                                                    \\ \hline
	121-140 & Stuck in their worst nightmare, the character falls comatose for a day.                                                                                                                                                                                                                                                                                                           \\ \hline
	141-200 & Fear breaks the character’s mind. He falls into a coma for half a week and his memory of the last 2D10 days is erased. After such a traumatic experience, the character likely develops a mental disorder (a Bane worth 2-3 GP). Player and GM should discuss what this might be.                                                                                                    \\ \hline
	201+    & The character dies from sudden cardiac arrest.                                                                                                                                                                                                                                                                                                                                       \\ \hline
\end{tabularx}
