\section{Modifiers}
\label{situationalmodifiers}
\subsection{General}
\begin{center}
	\begin{tabular}{|l|l|l|}
		\hline
		\ul{Situation}         & \ul{Modifier} \\ \hline
		Difficulty: Hellish     & -60            \\ \hline
		Difficulty: Punishing   & -50            \\ \hline
		Difficulty: Grueling    & -40            \\ \hline
		Difficulty: Very Hard   & -30            \\ \hline
		Difficulty: Hard        & -20            \\ \hline
		Difficulty: Difficult   & -10            \\ \hline
		Difficulty: Challenging & +0             \\ \hline
		Difficulty: Ordinary    & +10            \\ \hline
		Difficulty: Routine     & +20            \\ \hline
		Difficulty: Easy        & +30            \\ \hline
		Difficulty: Simple      & +40            \\ \hline
		Difficulty: Elementary  & +50            \\ \hline
		Difficulty: Trivial     & +60            \\ \hline
	\end{tabular}
\end{center}
\subsection{Melee Combat}
\begin{tabularx}{\textwidth}{|X|l|l|}
	\hline
	\ul{Situation} & \ul{Modifier} & \ul{Keyword} \\ \hline
	The character attacks below his optimum & -20 & Distance \\ \hline
	The character is attacking slightly outside of reach. & -20 & Distance \\ \hline
	Not all enemy combatants are within the character's control area. & -20 & Target \\ \hline
	The character is fighting in strong winds, heavy rain or on slippery ground. & -10 & Environment \\ \hline
	The character tries to attack or parry while prone. & -10 & Environment \\ \hline
	The character is fighting a character in mist, fog or smoke. & -20 & Environment \\ \hline
	The character tries to dodge while prone. & -20 & Environment \\ \hline
	The character is fighting in knee deep snow or water. & -30 & Environment \\ \hline
	Fighting an armed opponent while unarmed. & -10 & Equipment \\ \hline
	The character is attempting to use two knives or a sword and a knife at once. & -10 & Equipment \\ \hline
	The character attempts to use a spear one-handed. & -20 & Equipment \\ \hline
	The character is attempting to use two spears at once. & -40 & Equipment \\ \hline
	The character is outnumbered 2 to 1. & -10 & Numbers \\ \hline
	The character and his allies outnumber the enemy 2 to 1. & +10 & Numbers \\ \hline
	The character is attacking a kneeling target. & +10 & Target \\ \hline
	The character attacks a stunned target & +20 & Target \\ \hline
	The character is attacking a prone target. & +20 & Target \\ \hline
	The character attacks an unaware target. & +30 & Target \\ \hline
\end{tabularx}
\subsection{Ranged Combat}
\begin{tabularx}{\textwidth}{|X|l|l|}
	\hline
	\ul{Situation} & \ul{Modifier} & \ul{Keyword} \\ \hline
	The character is shooting over extreme range. & -50 & Distance \\ \hline
	The character is shooting over long range. & -20 & Distance \\ \hline
	The character shoots over short range. & +10 & Distance \\ \hline
	The character shoots at point blank range. & +30 & Distance \\ \hline
	The character attempts to use a pistol one-handed. & -10 & Dual-wielding \\ \hline
	The character is attempting to use two pistols at once. & -20 & Dual-wielding \\ \hline
	The character attempts to use a small rifle one-handed. & -30 & Dual-wielding \\ \hline
	The character attempts to use another weapon one-handed. & -60 & Dual-wielding \\ \hline
	The character is attempting to use two small rifles at once. & -40 & Dual-wielding \\ \hline
	The character is fighting in strong winds, heavy rain or on slippery ground. Multiple may stack. & -10 & Environment \\ \hline
	The character tries to dodge while prone. & -20 & Environment \\ \hline
	The character is attacking a specific enemy caught up in melee combat or he himself is caught in melee combat. & -30 & Environment \\ \hline
	The character is attempting to fire blindly at an enemy he knows the rough location of. & -30 & Environment \\ \hline
	The character is fighting in knee deep snow or water. & -30 & Environment \\ \hline
	The character is shooting at a character in mist, fog or smoke. & -30 & Environment \\ \hline
	The character is using a long weapon in somewhat confined spaces like a house. & -20 & Environment \\ \hline
	The character is using smgs in very tight corridors or tunnels. & -20 & Environment \\ \hline
	The character shoots from the higher ground. & +10 & Environment \\ \hline
	The character is shooting a crouching target. & -10 & Target \\ \hline
	The character is shooting a prone target. & -20 & Target \\ \hline
	The character attacks a stunned target. & +20 & Target \\ \hline
	The character attacks an unaware target. & +30 & Target \\ \hline
\end{tabularx}
\subsection{Social}
\begin{tabularx}{\textwidth}{|X|r|l|}
	\hline
	\ul{Situation} & \ul{Modifier} & \ul{Focused skill} \\ \hline
	Performing a simple dance. & +/-0 & Acrobatics / Etiquette \\ \hline
	Performing a difficult, intricate dance. & -35 & Acrobatics / Etiquette \\ \hline
	The target has something else to do or does not want to be bothered. & -10 & Appeal \\ \hline
	The target is suspicious and/or has had bad experiences with the character. & -20 & Appeal \\ \hline
	The target is hostile but not aggressive yet. & -30 & Appeal \\ \hline
	The target is a devoted enemy and currently in mortal combat with the character. & -60 & Appeal \\ \hline
	The target and the character are acquainted. & +10 & Appeal \\ \hline
	The target is friendly. & +20 & Appeal \\ \hline
	The target is devoted to or close friends with the character. & +30 & Appeal \\ \hline
	Pickpocketing something obvious like an ID card or a phone sticking out of someone's pocket & -10 & Sleight of hand \\ \hline
	Performing a simple magic trick to draw one person's attention. & +10 & Sleight of hand \\ \hline
\end{tabularx}

\subsection{Exploration}
\begin{tabularx}{\textwidth}{|X|l|l|}
	\hline
	\ul{Situation} & \ul{Modifier} & \ul{Focused skill} \\ \hline
	Driving under fire or on difficult terrain. & -20 & Drive / pilot \\ \hline
	Driving a damaged vehicle, still under heavy fire. & -40 & Drive / pilot \\ \hline
	Driving a vehicle for the first time. & +0 & Drive / pilot \\ \hline
	Driving in familiar terrain and regions. & +10 & Drive / pilot \\ \hline
	Controlling a civilian vehicle at moderate speeds or at low speeds in fairly close quarters. & +20 & Drive / pilot \\ \hline
	Controlling a civilian vehicle at low speeds. & +40 & Drive / pilot \\ \hline
	Making out sounds with an engine humming on an idle car right next to the character or light animal chatter in the background. & -10 & Perception \\ \hline
	Trying to make out sounds in a firefight or riot. & -20 & Perception \\ \hline
	Trying to see something or fight in low light or against light. & -20 & Perception \\ \hline
	Trying to make out sounds in a street war. & -40 & Perception \\ \hline
	Trying to fight in total darkness or while blinded. & -60 & Perception \\ \hline
	Trying to make out sounds with large explosions going off. & -60 & Perception \\ \hline
	Listening for footsteps on sandy ground. & +0 & Perception \\ \hline
	Listening for footsteps on wet ground. & +15 & Perception \\ \hline
	Listening for footsteps in tall grass, on gravel or snow. & +20 & Perception \\ \hline
	Listening for footsteps on metal flooring. & +30 & Perception \\ \hline
	Listening for footsteps on grassy ground. & +5 & Perception \\ \hline
	Listening for sounds in echoing environments. & +100\% & Perception \\ \hline
	Hide or draw a small object. & -10 & Sleight of hand \\ \hline
	Hide or draw a fairly large object, like a submachinegun. & -30 & Sleight of hand \\ \hline
\end{tabularx}

\subsection{Stealth and Deception}
\begin{tabularx}{\textwidth}{|X|l|l|}
	\hline
	\ul{Situation} & \ul{Modifier} & \ul{Focused skill} \\ \hline
	Trying to hide while moving slowly. & -10 & Stealth \\ \hline
	Trying to sneak in armor or heavy footwear. & -10 & Stealth \\ \hline
	Trying to sneak in a strike suit. & -15 & Stealth \\ \hline
	Trying to hide while running. & -40 & Stealth \\ \hline
	Trying to sneak while barefoot or wearing very light footwear. & +0 & Stealth \\ \hline
	Trying to hide while crouching in place. & +10 & Stealth \\ \hline
	Trying to hide while laying prone in place. & +30 & Stealth \\ \hline
	Distracting someone & +20 & Deceive \\ \hline
	Telling half-truths and partial lies & +10 & Deceive \\ \hline
	Telling lies and complete untruths & -10 & Deceive \\ \hline
	Gaslighting someone in their own area of expertise & -50 & Deceive \\ \hline
\end{tabularx}

\subsection{Craftsmanship}
\begin{tabularx}{\textwidth}{|X|l|l|}
	\hline
	\ul{Situation} & \ul{Modifier} & \ul{Focused skill} \\ \hline
	Creating or repairing equipment with only insufficient or improvised tools. & -20 & Mechanics \\ \hline
	Trying to fix unknown technology. & -40 & Mechanics \\ \hline
	Attempting to repair and use damaged weapon attachments. & +10 & Mechanics \\ \hline
	Repairing a damaged vehicle with the necessary tools. & +20 & Mechanics \\ \hline
	Repairing simple circuitry or devices like antennas. & +30 & Mechanics \\ \hline
	Picking more secure locks like found on motorized vehicles. & -10 & Security \\ \hline
	Defusing an old landmine. & -30 & Security \\ \hline
	Setting up a tripwire or trapping a door. & +10 & Security \\ \hline
	Picking a simple lock like found on a bicycle. & +20 & Sleight of hand \\ \hline
%	Strategically placing a simple lock or chain. & +60 & Security \\ \hline
\end{tabularx}
