\section{Skills}
\label{skilllist}
\skill{Acrobatics}{Agility}{Acrobatics describes the ability to control one's body. It encompasses moving elegantly, gymnastics, breaking falls and dancing.}
\skill{Animal Handling}{Charisma}{Animal Handling is any interaction with animals; calming them down, taming and training them.}
\skill{Appeal}{Charisma}{Appeal encompasses any attempt to charm or convince someone that at least outwardly happens in good blood.}
\skill{Athletics}{Strength}{Athletics is used for any task built on directing one's strength, be it lifting, pushing, running or jumping.}
\skill[Advanced]{Brewing}{Intelligence}{Making any sort of alcoholic beverage is considered brewing. All differences between creating beer, wine and whatever else is neglected.}
\skill[Advanced]{Chemistry}{Intelligence}{Chemistry is necessary for identifying and creating chemicals. It also includes knowledge of recipes and estimation of effects and side effects for unknown recipes.}
\skill{Climbing}{Strength}{Climbing generally means scaling heights. Holding oneself at the ceiling might be considered climbing as well.}
\skill{Command}{Charisma}{Command describes military social interactions that feature a clear hierarchy. It also represents knowledge about military leadership and command structure.}
\skill[Advanced]{Commerce}{Intelligence}{Anything concerned with the exchange of money falls under the Commerce skill. This obviously includes trading but also bribery and extortion.}
\skill[Advanced]{Computer Operation}{Intelligence}{Computer Operation means using a computer. That technically includes even the simplest tasks but only advanced operations will require a test, such as getting access to files that one should not have access to.}
\skill[Advanced]{Construction}{Intelligence}{Construction is concerned with creating buildings and understanding buildings; that means probable layouts or weaknesses.}
\skill[Advanced]{Cryptography}{Intelligence}{Cryptography is the knowledge about en- and deciphering data of any type. If the data was human-readable, a cunning character might identify simple probable cipher algorithms.}
\skill{Deceive}{Charisma}{Deceiving means telling lies. Making half-truths believable might fall under this skill as well, as per GM discretion.}
\skill{Dodge}{Agility}{Dodging is physically evading harm. This can be an attack or something more natural like falling objects or sudden vehicles.}
\skill[Advanced]{Drive: Bike}{Agility}{Drive (Bike) encompasses the knowledge of how motorbikes and similar vehicles work and how to get them to move in a desired direction.}
\skill[Advanced]{Drive: Boat}{Agility}{Drive (Boat) encompasses the knowledge of how motorboats and similar vehicles work and how to get them to move in a desired direction. Rowboats, canoes and so on might be covered with athletics instead.}
\skill[Advanced]{Drive: Car}{Agility}{Drive (Car) encompasses the knowledge of how cars and similar vehicles work and how to get them to move in a desired direction.}
\skill[Advanced]{Drive: Heavy}{Agility}{Drive (Heavy) encompasses the knowledge of how trucks and similar vehicles work and how to get them to move in a desired direction. It also includes knowledge about APCs, IFVs or tanks and other heavy armored vehicles.}
\skill{Estimate}{Instinct}{Estimation is the ability to guess amounts, weight, size, distance and whatever else might come up; a smith estimating a knife's price might not necessarily need this.}
\skill{Gambling}{Instinct}{Gambling is betting, card and board games: knowing how to play, knowing how to win, by all means if necessary.}
\skill[Advanced]{Geography}{Intelligence}{Geography describes the knowledge of the world and its places.}
\skill[Advanced]{Herbalism}{Intelligence}{Herbalism is knowledge of plants, formal or by experience.}
\skill{History}{Intelligence}{History is the knowledge of past events. Low values don't necessarily mean no knowledge but might include false information as well.}
\skill{Interrogation}{Instinct}{Interrogation encompasses asking the right questions as well as reading facial expressions and voice tone to determine truth or lie; also includes understanding the opposition's true meaning.}
\skill{Intimidation}{Courage}{Intimidation means skillfully threatening others to avoid actually having to go through with the threat.}
\skill[Advanced]{Law}{Charisma}{Law means the knowledge about rights and also the ability to accuse and defend properly.}
\skill[Advanced]{Logic}{Intelligence}{Logic is the ability to dissect and combine information rationally and quickly or detect patterns where others do not.}
\skill[Advanced]{Mechanics}{Dexterity}{Mechanics encompasses the knowledge of how technology works and the skill to fix or even create it.}
\skill[Advanced]{Medication}{Dexterity}{Medication is the necessary knowledge of anatomy and medical chemicals and the skill of how to apply it, give first aid and do surgery.}
\skill{Navigation: Air}{Instinct}{Navigation in the air is difficult and relies on good sense of both distance and direction. It may be easier when sun, moon, stars or large landmarks on the ground are visible.}
\skill{Navigation: Ground}{Instinct}{Navigation on the ground is the most common type of navigation. It helps finding one's way on foot or in earthbound vehicles.}
\skill{Navigation: Sea}{Instinct}{Navigation on the sea relies on reading maps and a compass. It is possible to make good educated guesses by using celestial bodies as well.}
\skill[Advanced]{Navigation Space}{Intelligence}{Navigation through the void of space without equipment is almost impossible due to how vast space is. This skill represents finding the shortest and safest path given such instruments.}
\skill{Navigation: Underground}{Instinct}{Navigating through underground complexes is quite difficult, as there are very few landmarks. It requires good memory or a map and good sense of distance.}
\skill{Perception}{Instinct}{Perception is essential for noticing small details. Someone properly educated with trained sense of hearing for example might make out the type of gun or ammunition used in a shot from the sound alone.}
\skill[Advanced]{Philosophy}{Intelligence}{Philosophy is what drives many people in the shadows of neon lights. Existential questions rarely find clear answers but one might come close.}
\skill[Advanced]{Pilot: Air}{Agility}{Piloting aircraft means understanding basics of aerodynamics and controls of different aircraft, usually but not necessarily it also encompasses basic understanding of flight control procedures.}
\skill[Advanced]{Pilot: Jet pack}{Agility}{While not piloting in the classical sense, using jet packs effectively is an extremely difficult discipline of aeronautics.}
\skill[Advanced]{Pilot: Space}{Intelligence}{Piloting spacecraft does not happen alone but this skill is representative of any position spacecraft may have.}
\skill[Advanced]{Quaffing}{Constitution}{Quaffing, getting wrecked, hammered, tanked, any of the above. This determines a character's ability to hold his liquor.}
\skill{Restraint}{Courage}{Restraint is the ability to push through and ignore both pain and strong emotions. Trying to suppress disabling characteristics is at a penalty equal to the disabling characteristic.}
\skill[Advanced]{Security}{Intelligence}{Security encompasses anything that is involved in defense: Personally setting and defusing traps, tactical choice of location, how to employ choke points and the exploitation of any mistakes the opposition might have made.}
\skill{Sleight of hand}{Dexterity}{Sleight of hand covers everything that requires delicate fingers and a good distraction. This may be pickpocketing or card tricks or whatever someone might come up with. Picking locks is part of this skill as well.}
\skill[Advanced]{Smithing}{Dexterity}{Smithing is the creation of new objects from metal. Casting also falls under this skill, even though it is not technically smithing.}
\skill{Stealth}{Agility}{Stealth describes the ability to hide, be it oneself or objects, as well as moving quietly. It is usually heavily modified and often opposed with Perception.}
\skill{Stories}{Charisma}{Stories means the knowledge of stories, the ability to make them up on the spot and the capability to tell them interestingly.}
\skill{Survival}{Instinct}{Survival is a catchall skill encompassing anything required for wilderness or wasteland survival: finding something edible and clean water, building improvised shelters and the most basic equipment.}
\skill{Swimming}{Constitution}{Swimming is the capacity to cross through waters without drowning. Due to how rare open bodies of water are, this skill is surprisingly rare.}
\skill{Tailoring}{Dexterity}{Tailoring is the knowledge of how to make objects from cloth or leathers. Very few people still do this themselves and their works are revered and sold for high prices.}
\skill{Tracking}{Instinct}{Tracking means finding and following a trail. This might be footprints of some wild animal or disturbances left by fleeing suspects.}
\skill[Advanced]{Voice Athlete}{Charisma}{Voice athletes are capable of changing their voices to sound a certain way. This can be used for ventriloquism, impersonation or something as simple as singing.}
\skill[Advanced]{Zoology}{Intelligence}{Zoology is knowledge about animals. This may be from formal education or experience and can sometimes be restricted when dealing with rare or exotic animals.}
