\section{Special Rules}
\vspace{10mm}
\begin{multicols}{2}
%\specialrule{Adjustable}{Allows spending double ammunition for double range. Shooting two full rounds like this deals the weapon's damage to the weapon and the user.}
\specialrule{Backblast (X)}{Everyone behind the shooter in a cone - X meters in length and X/2 meters in base diameter - takes half the weapon damage as if hit by a weapon with the Blast rule.
	If a wall blocks the cone, the area becomes Blast(X) centered on - and including - the user instead.}
\specialrule{Blast (X)}{Every character inside the area - a circle X meters in radius - takes a hit.
	For every 2 meters inside the Blast radius the target is,
	one additional location is hit,
	up to every location once.}
\specialrule{Bulky}{Cannot be carried in holsters, slings or such.}
\specialrule{Cerberus Infection}{When touching an open wound, such as when dealing damage with an attack, the target makes a Constitution test at a -20 penalty. On a failure the target is infected by the Cerberus fungus. Small creatures like mice will simply die.}
\specialrule{Cumbersome}{Halves speed of the wearer/user and grants -10 to all physical actions.}
\specialrule{Disrupt}{Turns off PES for D5 rounds after a hit.}
\specialrule{EMP}{Causes 2D10 rounds of EMP (p. \pageref{hazards:cbrn}).}
\specialrule{Flame}{Sets ablaze any flammable surfaces and objects it hits.}
\specialrule{Flash}{Any affected character looking at the source makes an Ins test at -10 or becomes Blinded for DoF+2 rounds.
	In addition any affected character within half range makes a Con test at -10 or becomes deafened for DoF+2 rounds.
	Any affected character with a third becomes Stunned instead of deafened.}
\specialrule{Flexible}{The weapon cannot be parried. It only gains half of the normal melee damage bonus.}
\specialrule{Improvised}{
	Does not require familiarity,
	but instead always invokes -10 penalty.
	It is also \emph{Unreliable}
	and usually breaks apart on a fumble.}
\specialrule{Multitargeting}
	{This weapon cannot perform single attacks;
		it is limited to \emph{Bursts}.
		\\%
		The attack's hits can be split freely among any valid targets,
			so long as they are roughly in the same direction.}
\specialrule{Oversized}{Way too large to be used by humans.}
\specialrule{Piercing}{The user's Melee Damage Bonus is added to the weapon's AP as well.}
\specialrule{Powered}{Requires an external power source to function.}
\specialrule{Protective}{Made for defense: -10 to hit, -2 damage, but +20 to parry.}
\specialrule{Reliable}{Can't jam (instead just indicates a miss) and is more resilient to damage.}
\specialrule{Rending}{When the attack is blocked by armor (after AP),
	it deals no damage to the target.
	Instead the armor is burnt away
	and reduced by the damage that would have been dealt until it is repaired.
	This will only affect solid armor, not energy shields.}
\specialrule{Scatter}{+10 to hit at short to extreme range, no AP at long and extreme range, +1d10 dmg when shooting in point blank range}
\specialrule{Single Loader}{Reloading may be interrupted after each bullet. The given reload time is a single round of ammunition. \\
	A Reload test - instead of reducing the reload time - increases the amount of shells reloaded during the loading time, but is at a penalty equal to 5 times the reload time.}
\specialrule{Smoke}{The area inside and behind the smoke is fully concealed. Smoke usually remains dense for a minute and lasts for another as slightly obscuring; this will be reduced in wind or active ventilation, or increased in a fully sealed room.}
\specialrule{Spray}{Ignores half of non-sealed armor and all but full cover.}
\specialrule{Stun (X)}{If the target fails a constitution check at a penalty equal to 10 times X, he becomes stunned for DoF rounds.}
\specialrule{Tearing}{Roll an additional damage dice and drop the lowest. Armor (after AP) is twice as effective.}
\specialrule{Trauma}{When attacking the head location, halve the target's armor. Also halves Stunning Strike penalties.}
\specialrule{Unreliable}{The weapon is a liability more often than not.
	It fumbles at any roll of 96+.}
\specialrule{Unwieldy}{The weapon disallows transforming reactions to actions, or vice versa.}
\specialrule{Upgrade Kit (X)}{The weapon is an upgrade kit for another weapon X. Price and weight include X.}
\end{multicols}
