\documentclass[12pt,a4paper,openany]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Strike Suits}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}

	\chapter{Introduction}
	A marvel of technological advancement, these powered armors offer vastly improved physical capabilities as well as a near skintight bunker. Many different series are in production and each of them offers many different variants to offer requested adaptability for almost any feasible area of operation.\par
	Any strike suit is built specifically for its pilot. These pilots are born either highly qualified or extremely privileged and are trained by many specialists; the cheapest part of their journey. The really expensive part is their equipment: weapons, augments, modifications for each, specialized ammunition, scanners and the list goes on - culminating their armor.\par
	Depending on their field of expertise, the armor series and variant is picked as detailed below. Note that due to how expensive and rare this type of equipment is, it is also extremely rare and hard to acquire, as even if a suit could be obtained from a dead pilot, the armor likely would not fit.

	\chapter{Building a Strike Suit}
	\section{Common Features}
	Every Strike Suit has a few similar properties, referred to as the \emph{Baseline}. These common aspects are then modified by the series and variant, as well as custom modifications.\par
	\begin{itemize}
		\item Every Strike Suit has very thick armor plates. Arms and legs sport 20 armor, the head has 16 and the torso makes it to 22.
		\item The armor is fitted with a piezoelectric exo-skeleton. This is ramped up to grant a bonus of 20 points, freely distributed between strength and agility of the wearer, to be determined at the time of creation.
		\item For squad communication every suit is fitted with a HUD, an intercom and a vitals monitor.
		\item Additionally every suit has space for 4 mods. Often times this is reduced by variant specific modifications.
		\item Lastly - to prevent the technology falling into the wrong hands - every suit has a Final Hour chip installed, blowing up the armor in a giant ball of fire and fragmentation when the wearer's vital signs drop to zero.\\
		This system is both safe and secure - it cannot be hacked or overridden in any way and it does not make mistakes.
		\item The single downside to strike suits is the fact that vehicle lock-on works against such a piece of armor, making them a priority target out in the open.
	\end{itemize}
	\par
	Such a marvel of technology requires strong connections to powerful people and a fair sum of money - production cost alone is at around 1800 cr.

	\section{Series}
	Every strike suit is constructed to fulfill a specific purpose. This means that every piece of armor has to belong to a specific series of strike suit, specialized in various areas of operation.

    \luaimport{strikesuits-series.csv}{strikesuit.tpl}

	\section{Variant}
	Unlike series variants are purely optional and offer more specialized and unique modules. Wearers of such armors are usually the best at their craft but rarely equipped to respond to enormous surprises all by themselves and rely on their teams to make up for their deficits.

    \luaimport{strikesuits-variants.csv}{strikesuit.tpl}

\end{document}