\section{Backgrounds}
\label{sec:backgroundlist}
%TODO: this is not required until there are more backgrounds
%\subsection*{At a glance}
%\providecommand{\tmplastgroup}{}
%\begin{center}
%	\begin{tabularx}{0.7\textwidth}{X|rr}
%		Background & Cost & Page \\
%		\hline
%		\luaimport{components/backgrounds.csv}{race-sum.tpl}{bg-summary}
%	\end{tabularx}
%\end{center}
%\subsection*{In detail}
\luaimport{components/backgrounds.csv}{race.tpl}{bgs}

\section{Boons}
\boon{Blessed Birth}{The character starts with a random \hyperref[ch:mutation]{mutation} and 3 corruption.}{6}
\boon{Mutation Prone}{The character gains a Mutation every 7 corruption (rather than 10).}{6}
\boon{Mutation Resistant}{The character gains a Mutation every 14 corruption (rather than 10).}{3}
\section{Banes}
\bane{Mark of Sacrifice}
	{The character bears the mark of sacrifice somewhere on his body.
		Otherworldly creatures (at least all those with the DEMONIC trait)
		react aggressively towards him
		and he takes a -30 penalty to hide from them.
		At some point in time the mark will glow and a Harvest (p. \pageref{anomaly:harvest}) will begin,
		coming for his body and soul.
	}
	{7}
	{}
\bane{Voidscarred}
	{Otherworldly entities are aware of the character.
		He always has at least 2 Insight.
		May be taken multiple times to increase the amount (2, 4, 6...).}
	{3}
	{each}
\section{Abilities}
\ability{Steeled}
	{400}
	{Courage 40}
	{Whenever the character would gain corruption,
		he makes a Con test at a penalty
		equal to 3 times the corruption.
		On a success the corruption gain is reduced by DoS, to a minimum of 0.}
\pagebreak%quick fix
\section{Bestiary}
\subsection{Traits}
\begin{tabularx}{\columnwidth}{l|X}
	Name & Effect \\ \hline
	DEMONIC & Other non-DEMONIC creatures suffer D5-1 Insight upon witnessing this creature. 
	This includes seeing, touching, hearing and smelling the creature, among others. \\
	\hline
	INCORPOREAL & The creature cannot interact with the physical world and vice versa.
\end{tabularx}

\subsection{Creatures}
\luaimport{components/bestiary.csv}{beast.tpl}{components/horrorbestiary}
