%TODO Introduction: anomalies can be basically anything
\section{Relics}
\subsection*{Book of Skin}
\paragraph{Description}
The book is bound in thick, gray leather.
It has a stylized eye etched into its cover.
The pages are beige and tattered,
	the ever shifting text written in dark crimson.
It is always slightly warm to the touch.
\paragraph{Effect}
Reading the book gives the reader
	100 XP, as well as D5 Insight and Corruption every hour.
If one dies while reading the book, he is absorbed and becomes a new page.
If the book is burned, it will attract and enrage large amounts of demons,
	trying to consume the freed souls and anyone else in the vicinity.
\subsection*{Shifting Cube}
\paragraph{Description}
A Rubik's cube with a faint RGB glow from within.
It has a pleasant but eerie silky smooth surface.
Feels soapy to the touch and never gets dirty.
\paragraph{Effect}
Solving the cube will make the user invisible for D100 minutes.
\\%
The cube will then also become invisible and much more slippery,
	completely impossible to hold on to.
When the time is up,
	the cube is nowhere to be found
	and will show up at another place, another time, often to another person.

\section{Locations}
\subsection*{Mirror District}
\paragraph{Description}
A once-thriving urban neighborhood,
	now a labyrinth of reflective surfaces and distorted realities.
The streets are lined with shattered glass, polished metal, and cracked mirrors,
	all reflecting warped and fragmented images of those who pass by.
Buildings appear to twist and bend in impossible ways,
	creating a disorienting environment where up can seem like down,
	and distances can stretch or shrink in an instant.
\paragraph{Effect}
Any senses are warped to the extreme,
	making it impossible to judge distance and direction.
Negative modifiers to tests are doubled.
Navigation is completely impossible.
\\%
Creatures can try to see through the illusions:
A creature can suffer D10 Insight to ignore the effect for a single test.
\\%
By GM discretion reflective surfaces in the area may show visions of possible futures.
\subsection*{Scaleway}
\paragraph{Description}
The Scaleway is a surreal, non-Euclidean landscape
	where the concepts of "big" and "small" become navigable dimensions.
As you traverse this bizarre realm,
	each step forward can either magnify or diminish your size
	relative to the world around you.
Gigantic mountains shrink to pebbles underfoot,
	and a single grain of sand can swell into a towering dune. 
\paragraph{Effect}
Any creature of at least 12 Insight
	and that knows to be within an anomalous location
	can consciously change its size at will.
Changing its size by one category causes 2 levels of exhaustion.
If the creature increases its size by 3 or more categories,
	it will collapse once it leaves the anomalous location
	and be unable to get up or die outright
	as physics takes its toll.

\section{Events}
\subsection*{Harvest}
\label{anomaly:harvest}
\paragraph{Heralds}
The subject's \hyperref[boon:markofsacrifice]{Sacrificial Mark} will begin to glow an eerie green,
	then to ache,
	then to bleed.
Shortly before the event the world around the carrier will begin to notably warp.
This may be between days and minutes, depending on the case.
\paragraph{Description}
Eventually any branded mortal will be considered ripe by the forces that marked it.
They will then break into real space,
	veiling the environment into shades of hatred and hunger.
\paragraph{Effect}
When a carrier of the Sacrificial Mark reaches his Insight limit
	or spend time in an anomalous location,
	instead of going catatonic he will call for an incursion to consume his body and soul.
Other branded ones in the area will also be entangled,
	becoming marked for the Harvest.
There is no place to hide
	and very little chance to flee,
	as ever more demons break through the veil.
\\%
The event will end once the branded ones have died,
	or at the next break of dawn.
It may also end once the exact demon that caused the branding is banished or eradicated.
\subsection*{Pit Gate}
\paragraph{Heralds}
Muffles roars and screams can be heard from below.
The earth rumbles, more and more intense.
Glass shatters, asphalt breaks.
\paragraph{Description}
The ground breaks open.
The hole may be any size,
	usually between 3 and 12 meters in diameter.
\paragraph{Effects}
Below awaits an anomalous location.
Which exactly can usually not be determined from above.
\\%
At the center of the caverns below awaits a heart.
Its exact form usually depends on the anomaly.
\\%
Once the heart is destroyed,
	the location returns to normal.
Within the next day the caverns collapse,
	leaving a surprisingly small crater
	and a faint memory of what happened.
%\subsection*{Stolen Name}
%\paragraph{Description}
%A creature loses a part of his true name
%thereby his identity
%\paragraph{Effect}
\subsection*{Brain Meld}
%TODO
\paragraph{Heralds}
Two characters with an strong emotional bond (e.g. friends or rivals) pass out
	at roughly the same time
	in the same area
	due to too much Insight.
\paragraph{Description}
The two find themselves in a space beyond time.
They spend a while there together
	- they can't tell how long -
	all the while their memories play out around them.
\paragraph{Effects}
The two characters meld their emotions.
Whenever one of them feels strong emotion,
the other feels it as well.
\begin{exampleblock}
	\itshape
	If one of them feels fear,
	the other feels it as well.
	\\%
	Resisting Fear becomes a Combined Action between those two characters.
	If they suffer Shock, both suffer the same result at the same time.
\end{exampleblock}
All Insight gained is shared between the two of them.
\\%
Any character can only meld once.
