%\subsection*{name}
%\subsubsection*{Preparation}
%%what tribute? roughly how expensive?
%%tests? which? what penalty?
%\subsubsection*{Rites}
%%penalty on the test
%%duration
%\subsubsection*{Effects}
%%positive outcome
%%potential side effects
%
\subsection*{Summoning}
\label{ritual:summoning}
\subsubsection*{Preparation}
A summoning requires a piece of bait -
in this context that is an object of significant emotional weight to the participants.
Examples include a religious artifact, a piece of personal artwork, or a wedding ring.
\\%
An item that the participants are barely willing to part with may add a bonus up to +30.
\subsubsection*{Rites}
Calling for a creature from beyond - and waiting for an answer - takes a long time.
The ritual may take anywhere from two to six hours (D5+1, if in question).
\\%
After the time is up, the leader makes a test at a -20 penalty.
\subsubsection*{Effects}
A random demon (or group of demons) is summoned.
Their combined combat rating is equal to half the ritual's DoS.
\\%
If the ritual leader called a specific demon he is aware of
and that demon's combat rating is equal or less than the ritual's DoS,
that demon is summoned instead.

\subsection*{Binding}
\label{ritual:binding}
\subsubsection*{Preparation}
The vessel (a human or a weapon) needs to be fixed in place and a demon needs to be running free in the vicinity.
(See e.g. Summoning, p.\pageref{ritual:summoning})
\subsubsection*{Rites}
The ritual leader makes repeated Courage-based Philosophy tests
- as if he tried to possess the demon.
(See \ref{possession:force})
\\%
Whenever one of these opposed tests is successful,
the demon is forced to step closer to the vessel at the next opportunity.
\\%
Once the binding ritual starts, the demon will notice.
It becomes furious, attacking anyone on sight with a preference for the leader and any participants.
It will generally ignore the vessel, as it is of no threat.
\subsubsection*{Effects}
For the possession of creatures refer to \ref{possession:binding} (p. \pageref{possession:binding}).
For the possession of weapons refer to \ref{sec:possessedweapon} (p. \pageref{sec:possessedweapon}) instead.

\subsection*{Gift}
\subsubsection*{Preparation}
The vessel is anesthetized and presented to the void.
\subsubsection*{Rites}
Symbols are painted, burned or engraved on the vessel's natural body parts.
\\%
The process takes around two hours.
At the end the leader makes the Philosophy test.
\subsubsection*{Effects}
The target is blessed with a new mutation.
The random result may be adjusted not just by the vessel's
	but by the leader's Insight as well.
\\%
When determining the result,
	an additional mutation may not be prevented.

\subsection*{Intervention}
\subsubsection*{Preparation}
The leader etches or burns the request into his body.
Every letter costs 1 HP in a supernatural toll.
Depending on the length of the request,
another member may be required to cut the leader instead,
lest the pain may stop him from finishing this work.
\\%
The request may not be split between participants
	or left on another one's body but the ritual leader's.
It does however also not need to be coherently, humanly readable
	- the letters only need to appear somewhere.
\subsubsection*{Rites}
The participants ask the void beyond to fulfill their request.
\\%
The Philosophy test is at a penalty depending on the type of request.
It may range from -50 to +50
	- the more chaotic and strange the request,
	the easier it \emph{usually} is to ask.
\\%
\subsubsection*{Effects}
\emph{Since this is somewhat of a catchall ritual, the effect descriptions are vague...}
\par \vspace{-8mm}
On a successful test the request is fulfilled, at least partially.
However, there are caveats, namely how these responses are usually twisted.
\\%
A request for information is answered vaguely or through self-fulfilling prophecies.
A request for money may also awake sudden curiosity in the authorities or criminals.
A request for more physical strength may cause permanent pain,
 as the body begins to destroy itself.
\\%
The possibilities are endless, however -
Considering the request has to be very short,
any imprecision will lead to undesired side effects,
either immediately or some time down the line.
