	\section{Armor}
\subsection{Introduction}
Armor is wearable cover - very convenient for anyone not looking to die.\\
Every part of the body can be covered once, meaning that armor pieces which overlap or even cover the same locations altogether cannot be combined.
\subsection{Casual wear}
This section contains clothing that is slightly armored but looks inconspicuous.\par
\armor{Biker helmet}{3}{0}{0}{0}{head}{2 mods; -5 to sight-based perception, +5 to Drive(Bike) checks}{cr 26}{1,5kg}
\armor{Armored suit}{0}{4}{2}{3}{torso, arms, legs}{1 mod; inconspicuous}{cr 79}{2,0kg}
\armor{Tough coat}{0}{2}{1}{1}{torso, arms}{0 mods; }{cr 35}{2,0kg}
\armor{Flak jacket}{0}{5}{5}{1}{torso, arms}{1 mod; inconspicuous}{cr 96}{2,0kg}
\armor{Tough pants}{0}{0}{0}{2}{legs}{0 mods; inconspicuous}{cr 18}{1,5kg}
\subsection{Helmets}
A section on protective head wear, armoring the arguably most vulnerable body location.\par
\armor{Blast helmet}{14}{0}{0}{0}{head}{1 mod; -10 to sight-based perception}{cr 123}{8,0kg}
\armor{Improvised helmet}{5}{0}{0}{0}{head}{1 mod; -5 Ag, Improvised}{cr 44}{3,0kg}
\armor{Banshee helmet}{6}{1}{0}{0}{head}{2 mods; inbuilt spotter target assist system}{cr 61}{2,0kg}
\armor{Flak helmet}{8}{0}{0}{0}{head}{1 mod; -5 to sight-based perception}{cr 70}{1,5kg}
\armor{Ghost helmet}{6}{0}{0}{0}{head}{2 mods; hide-y stuff}{cr 53}{5,0kg}
\armor{EVA helmet}{5}{0}{0}{0}{head}{3 mods; vac-sealed}{cr 44}{2,0kg}
\armor{Argus helmet}{10}{0}{0}{0}{head}{2 mods; -10 to sight-based perception, inbuilt explosives detection assistant}{cr 88}{9,0kg}
\subsection{Body Armor}
Armor pieces below are about protecting the largest location of the human body.\par
\armor{EOD armor}{3}{20}{18}{2}{torso, arms}{2 mods; -2 movement speed, -10 Ag, -10 to Dex and shooting tests}{cr 376}{36,0kg}
\armor{Banshee suit}{0}{10}{7}{0}{torso, arms}{2 mods; inbuilt climbing gear}{cr 149}{4,0kg}
\armor{Improvised vest}{0}{9}{0}{0}{torso}{1 mod; -5 Ag, Improvised}{cr 79}{3,5kg}
\armor{Stab vest}{0}{9}{0}{0}{torso}{1 mod; -5 Ag, immune to piercing rule}{cr 79}{3,5kg}
\armor{Flak vest}{0}{12}{0}{0}{torso}{1 mod; -5 Ag}{cr 105}{4,0kg}
\armor{UA pauldrons}{0}{0}{10}{0}{arms}{2 mods; -5 Ag}{cr 88}{3,5kg}
\armor{Ghost suit}{0}{10}{7}{0}{torso, arms}{3 mods; does not stop a skin-close holoprojector, includes piezoelectric exo-frame}{cr 149}{12,0kg}
\armor{Node armor}{0}{14}{4}{0}{torso, arms}{3 mods; can carry AI\\
	includes piezoelectric exo-frame}{cr 158}{14,0kg}
\armor{Strike suit}{16}{24}{20}{20}{all}{? mods; has own chapter}{cr 1.200}{300,0kg}
\armor{EVA suit}{0}{3}{3}{3}{torso, arms, legs}{4 mods; vac-sealed}{cr 79}{2,5kg}
\subsection{Leg Armor}
This section is the result of a fine balance act between all-important movement and protection.
\armor{Blast greaves}{0}{1}{0}{18}{legs}{1 mod; -1 movement speed, -10 Ag}{cr 166}{10,0kg}
\armor{Banshee greaves}{0}{0}{0}{6}{legs}{2 mods; }{cr 53}{2,0kg}
\armor{Flak greaves}{0}{0}{0}{10}{legs}{2 mods; -5 Ag}{cr 88}{2,5kg}
\armor{Ghost greaves}{0}{0}{0}{6}{legs}{1 mod; halves penalties from noise on sneaking}{cr 53}{6,0kg}
\subsection{Mods}
In the following section there are lists for all the modifications that can be added to armor pieces. The amount of mods that can be added to any one armor piece or combination is given at the piece of armor itself.\par
\armormod{Ablative coating}{A heat dispersing coat, layered upon the armor, that increases armor against laser and other heat-based weaponry by 20\%.}{cr 40}{1}{N}{0,6 kg}
\armormod{Auto-injector}{On the press of a button, detection of a certain type of stress or a similar trigger, this mod introduces a prepared dosage of an injection-type chemical into the wearer's bloodstream. Can hold up to 3 cartridges.}{cr 24}{1}{N}{0,8 kg}
\armormod{Auto-loader}{A reload assistance system added to the outer thighs which halves reload times for pistols. When present on both legs, this will allow reloading both guns while dual wielding.}{cr 14}{1}{N}{1,2 kg}
\armormod{Booster Sheath}{A melee weapon can be draw from this sheath in a free action. When combined with Quick Draw a weapon draw from this sheath can be combined with one non-flurry attack as a free action. When the armor mod is also powered, this attack gains 4 damage.}{cr 24}{1}{N}{1,4 kg}
\armormod{Brace Assist}{The character may brace as a free action. Moving still stops bracing.}{cr 34}{2}{N}{2,6 kg}
\armormod{CBRN (Helmet)}{A hazard prevention system containing a CBRN unit, rebreather and redundancies for each subsystem.}{cr 112}{2}{N}{1,4 kg}
\armormod{Cigarette Lighter Adapter}{Adds an outlet to light cigarettes on. }{cr 3}{1}{Y}{0,0 kg}
\armormod{Deafen Suppressor}{Grants +20 to tests to resist deafening and disorientation. Grants -5 to auditory perception.}{cr 18}{1}{N}{0,2 kg}
\armormod{Discardable Plates}{Adds an outer layer that can be discarded easily. Useful when on fire or drenched in acid.}{cr 12}{1}{N}{1,4 kg}
\armormod{Energy Rotella}{Projects a small shield over the user's arm that can be used to cover one location in addition to the arm it's attached to. Has 12 armor and a threshold of 7.}{cr 50}{1}{Y}{1,1 kg}
\armormod{Faraday cage}{Reduces EMP duration by 8 rounds and grants +30 to resist electricity-related Stun rules.}{cr 62}{1}{N}{18,8 kg}
\armormod{Final hour chip}{Once the wearer's vital signs cease, the armor self-destructs violently, like a 40mm thermite grenade with a 6m Blast radius instead. Requires a vital monitor.}{cr 170}{0}{Y}{0,1 kg}
\armormod{Flare Launcher}{Turns Vehicle Lock-on bonuses into penalties. Has 3 flares and takes a minute to refill. }{cr 48}{3}{Y}{2,1 kg}
\armormod{Flash Visor}{Adds flash glass goggles to the helmet.}{cr 31}{1}{N}{0,6 kg}
\armormod{Flashlight}{Adds a flashlight and its related bonuses. Hitting the location the active flashlight is attached to is at no penalty for low light or location. }{cr 65}{1}{N}{1,1 kg}
\armormod{Ghillie}{Adds a Ghillie Cloak to the armor, offering a +20 Bonus to Camouflage when used in matching surroundings.}{cr 6}{0}{N}{1,5 kg}
\armormod{Grappling hook}{Adds a reusable grappling hook to the armor. Works like an integrated crossbow using grappling hook ammunition.\\
	This is a very niche upgrade, as the grappling hook requires power but can only hold up to 250 kg of weight.}{cr 55}{1}{Y}{5,9 kg}
\armormod{HUD}{Adds a heads up display to the helmet visor. Can be tied to display any device but has no input device included.}{cr 4}{1}{N}{0,8 kg}
\armormod{Inertia Dampeners}{A marvel of technology allowing rapid changes in velocity. Fall damage is reduced and the Trauma rule is ignored. Depending on the situation this may have other bonuses, e.g. in fast vehicles.}{cr 189}{3}{Y}{26,0 kg}
\armormod{Tacpad}{Adds a data pad the the armor's forearm.}{cr 22}{1}{N}{1,1 kg}
\armormod{Integrated Weapon}{Any one-handed melee or pistol type weapon can be affixed to an arm. Pistols now use Ranged Combat Training (Integrated Weaponry). One-handed melee weapons may use Melee Combat Training (Striking) or their normal skill depending on how they are installed.\\
	Removes the Inconspicuous rule.}{weapon + 10\%}{1}{N}{weapon +10\%}
\armormod{Intercom}{An inbuilt communication device using very strong encryption. Different intercoms need to be grouped at a computing device equipped for the task before being able to communicate among each other safely.}{cr 28}{1}{N}{0,2 kg}
\armormod{Jump pack}{A backpack like armor attachment containing boosters to increase jump height, leap length, allow some amount of control in the air or stop hitting the floor at a violently rapid pace. Requires Pilot (Jetpack) to steer.\\
	Height: increases the jump height by a factor of 3, reduced by 0.5 for every full 100 kg the wearer weighs, becoming useless at 400kg\\
	Control: can decrease fall damage by 4 dice, reduced by 1 for every full 100 kg the wearer weighs, becoming useless at 400kg\\
	Ground Slam: doubles fall damage but enables a Charge with a speed of 10 times meters fallen and Blast (1)}{cr 82}{2}{N}{32,0 kg}
\armormod{Medic Container}{Fits one pack of wound sealant foam or wound dressing, a field surgery or stitch kit, 5 doses of any medicine and a thermal blanket. Any equipment stored here can be drawn as a free action.}{cr 21}{1}{N}{1,2 kg}
\armormod{Medical HUD}{When a patient has an accessible vital monitor, this device gives much more detailed information, thereby improving medical tests by +20.}{cr 36}{2}{N}{0,8 kg}
\armormod{Nanomesh Undersuit}{The minimum armor the wearer can be reduced to by e.g. abilities is 8.}{cr 43}{2}{N}{2,3 kg}
\armormod{Night vision}{A night vision device included in the helmet.}{cr 14}{1}{N}{0,7 kg}
\armormod{Odysseus system}{A display that includes many forms of navigation systems, granting a +10 to driving and +20 to navigation tests.}{cr 28}{1}{N}{1,3 kg}
\armormod{Oversized Mag Holster}{Hooks to hold a taped or drum mag}{cr 16}{1}{N}{0,2 kg}
\armormod{Piezoelectric Exo-Frame}{carries the armor's weight\\
	When struck by an EMP, it grants a -20 penalty to all physical actions taken and deals D10+6 damage ignoring armor to all the wearer's locations every round.}{cr 190}{2}{Y}{18,0 kg}
\armormod{Power Pack}{Adds a generator to non-powered armor to accommodate armor mods requiring power.}{cr 45}{2}{N}{14,0 kg}
\armormod{Radar}{A small radar device detecting moving objects in the vicinity. Detecting someone sneaking around is at a +40 bonus. Has a range of 40m.}{cr 78}{2}{N}{11,0 kg}
\armormod{Reactive Shields}{Shield arms controlled by a small AI. Grants an additional block reaction at a target value of 45. If an attack is blocked with this shield, it triggers an explosion equal to a 20mm HE grenade directed outwards. The mod contains 6 shields, each can trigger once before having to be replaced for cr 15.}{cr 180}{3}{Y}{24,0 kg}
\armormod{Servo Exo-Frame}{A replacement for the more prevalent piezoelectric exo-frame. It is less potent, carrying only 3/4 of the armor's weight but won't harm the wearer in case of an EMP and instead just shut off.}{cr 8}{0}{Y}{18,0 kg}
\armormod{Spring Charge (arm)}{Increases Strength for quick tasks like punching or throwing by 20.}{cr 54}{1}{Y}{1,2 kg}
\armormod{Spring Charge (leg)}{Increases Strength for quick tasks like jumping or kicking by 20.}{cr 58}{1}{Y}{1,5 kg}
\armormod{Temperature regulators}{Tries to keep the armor's internals at around room temperature, preventing heat stroke and hypothermia in all but the harsh wastelands. }{cr 24}{1}{N}{0,8 kg}
\armormod{TROPHY Active Defense System}{Shoots projectiles out of the air that travel at least 5m/s, are between 2cm and 10cm across and within 10m of the wearer. Explosives are usually just destroyed while incendiaries still spill. Holds 6 cartridges of 11.8x45mm ammo and takes a minute to refill.}{cr 54}{4}{N}{2,1 kg}
\armormod{Up Armor}{Additional armor plates that increase the location's armor by 1.}{cr 22}{1}{N}{2,0 kg}
\armormod{Vacuum seal}{Seals the armor to prevent any gas leaking, like air flowing outside or hydrogen cyanide inside.}{cr 32}{0}{N}{1,1 kg}
\armormod{Vital monitor}{Tracks the wearer's vital data. A abbreviation can be made accessible over network.}{cr 8}{0}{N}{1,6 kg}
\section{PES}
\pes{Mk IIa PES Prototype}{6}{4}{cr 110}{1,9 kg}{}
\pes{Mk IIIa Retail-Ready PES}{11}{6}{cr 160}{1,2 kg}{}
\pes{Mk III Projected Armor}{18}{7}{cr 210}{2,6 kg}{}
\pes{Mk IV Heavy PES}{24}{8}{cr 230}{5,8 kg}{Cumbersome}
\pes{Projected Bunker Shielding}{48}{10}{cr 280}{350,0 kg}{incredibly large, 8m radius}
\pes{Assault / Rumble Energy Shielding}{12}{6}{cr 170}{1,4 kg}{triggers on melee attacks as well}
\pes{MagMA Heat Shield}{12}{6}{cr 170}{1,4 kg}{halves fire damage}
\pes{EOD Energy Shielding}{14}{7}{cr 180}{1,2 kg}{armor doubled against shotgun and explosive damage (all attacks with Scatter or Blast rules)}
\pes{Unstable PES}{18}{7}{cr 210}{0,7 kg}{shocks surroundings (excluding the wearer) when triggered: Blast (1), EMP, Stun (2)}
\pes{Energy Rotella}{10}{6}{cr 150}{1,1 kg}{}
\pes{Mk IVa Heavy Prototype}{22}{7}{cr 220}{1,2 kg}{blocks ranged attacks going out}
