\section{Ranged}
\subsection{Weapons}
\vspace{4mm}
\begin{multicols}{2}
\subsubsection{Pistol}
\vspace{2mm}
\rangedweapon{Obsidian Bull}{A hand cannon fed from a cylinder.}{Shots: 1; Damage: 2D10+8; AP: 1}{25m}{6 (11.8x45mm)}{6}{Reliable, Single Loader}{cr 50}{1.7 kg}
\rangedweapon{Wasteland Condor}{A powerful handgun with an extremely heavy cartridge.}{Shots: 1; Damage: 2D10+8; AP: 1}{25m}{7 (11.8x45mm)}{2}{}{cr 50}{1.9 kg}
\rangedweapon{Amber Bull}{A revolver made to fire low caliber rounds.}{Shots: 1; Damage: 2D10+3; AP: 0}{20m}{8 (7.2mm)}{8}{Reliable, Single Loader}{cr 30}{0.5 kg}
\rangedweapon{M10}{A small, low caliber, semiautomatic pistol. Very light and decently easy to conceal.}{Shots: 1; Damage: 2D10+3; AP: 0}{20m}{9 (7.2mm)}{1}{}{cr 30}{0.6 kg}
\rangedweapon{mOP-3}{A hand-sized 20mm grenade hind loader}{Shots: 1; Damage: ; AP: depending on ammo}{20m}{1 (20mm grenade)}{4}{minimum arming distance of 10m}{cr 40}{1.3 kg}
\rangedweapon{"Little Lucifer" Hand Flamer}{A one-handed flamethrower. While it holds "flame" in its name, it can be used for all fueled spray weapons.}{Shots: 5; Damage: 1D10+2; AP: 0}{12m}{5 (small fuel tank)}{8}{Flame, Scatter, Spray}{cr 80}{1.6 kg}
\rangedweapon{OH-VLS}{A small, adjustable laser pistol}{Shots: 2; Damage: 1D10+10; AP: 1}{35m}{16 (small fuel cell)}{4}{Adjustable}{cr 70}{0.6 kg}
\rangedweapon{Newton Pistol Mk5}{A forearm-sized magnetic accelerator shooting metal fragments}{Shots: 1; Damage: 1D10+2; AP: 12}{35m}{30 (small mass driver shard block)}{8}{}{cr 110}{2.6 kg}
\rangedweapon{Newton Pistol Mk2 }{The smallest mass drivers ever built. Shoots very small metal fragments}{Shots: 2; Damage: 1D10+2; AP: 8}{30m}{30 (small mass driver shard block)}{8}{}{cr 95}{2.1 kg}
\rangedweapon{Mk1 Shock pistol}{A modified taser. Very much lethal.}{Shots: 1; Damage: 2D5; AP: 0}{20m}{8 (small fuel cell)}{5}{EMP, Stun (4)}{cr 50}{0.4 kg}
\rangedweapon{Scattershock}{A one-handed Tesla gun}{Shots: 2; Damage: 3D5; AP: 0}{15m}{6 (small fuel cell)}{5}{Scatter, EMP, Stun (3)}{cr 80}{0.6 kg}
\end{multicols}

\pagebreak
\subsubsection{Short Rifle}
\vspace{8mm}
\begin{multicols}{2}
\rangedweapon{MS shotgun}{A double-barrel shotgun with shortened barrels to facilitate pellet spread}{Shots: 1; Damage: 2D10+3; AP: 1}{40m}{2 (12gauge)}{4}{Reliable, Scatter, Single loader}{cr 25}{3.0 kg}
\rangedweapon{short-barrel AR-22}{A rifle caliber fired from a short system. Warning: only buy this if you don't own a dog!}{Shots: 3; Damage: 2D10+2; AP: 6}{50m}{30 (6.3mm)}{4}{}{cr 110}{3.5 kg}
\rangedweapon{MP15}{A pistol caliber fired from a small rifle frame.}{Shots: 4; Damage: 2D10+3; AP: 1}{30m}{25 (7.2mm)}{3}{}{cr 65}{2.8 kg}
\rangedweapon{"Thumper"}{A small CQC grenade launcher meant for utility grenades. Exists as an under barrel version for rifles.}{Shots: 1; Damage: ; AP: depending on ammo}{20m}{1 (20mm grenade)}{4}{minimum arming distance of 10m}{cr 70}{4.8 kg}
\rangedweapon{OH-VLS conversion kit}{A conversion kit to turn an OH-VLS into a small laser carbine.}{Shots: 3; Damage: 1D10+12; AP: 1}{70m}{16 (medium fuel cell)}{5}{Adjustable, Flame, Upgrade (OH-VLS)}{cr 140}{2.8 kg}
\rangedweapon{Newton Pistol Repeater kit}{A conversion kit for low powered Newton Pistols to increase fire rate.}{Shots: 4; Damage: 1D10+3; AP: 12}{45m}{30 (small mass driver shard block)}{8}{Upgrade (Mk2 Newton Pistol)}{cr 140}{3.6 kg}
\rangedweapon{"Junk Jet" Mass Driver Shotgun}{A mass driver with increased bore to achieve shotgun-like ballistics}{Shots: 1; Damage: 2D10+2; AP: 8}{55m}{6 (small mass driver shard block)}{3}{Scatter}{cr 170}{4.2 kg}
\rangedweapon{Crossbow / Harpoon}{A very short bow with a trigger }{Shots: 1; Damage: 1D10+4; AP: 0}{50m}{1 (crossbow bolt)}{6}{Silenced, ignores shields}{cr 25}{3.0 kg}
\rangedweapon{Scattershock rifle conversion kit}{A conversion kit for the Scattershock to feed from larger fuel cells. Increases size, mag size and range.}{Shots: 2; Damage: 3D5; AP: 0}{45m}{30 (medium fuel cell)}{5}{Scatter, EMP, Stun (3), Upgrade (Scattershock)}{cr 125}{2.1 kg}
\end{multicols}

\subsubsection{Long Rifle}
\vspace{8mm}
\begin{multicols}{2}
\vspace{2mm}
\rangedweapon{AR-22}{A full sized rifle}{Shots: 3; Damage: 2D10+3; AP: 11}{120m}{30 (6.3mm)}{6}{}{cr 150}{3.8 kg}
\rangedweapon{M282 SSW}{A bulky, belt-fed fire support weapon with high ammunition capacity}{Shots: 6; Damage: 2D10+3; AP: 11}{120m}{120 (6.3mm)}{14}{Bulky}{cr 220}{7.0 kg}
\rangedweapon{Mk3 Tankgewehr}{An insanely high-caliber, long barrel rifle made to fight heavy armor. Carries a lot of energy of comparatively small distances.}{Shots: 1; Damage: 3D10+3; AP: 30}{250m}{1 (15x132mm)}{10}{}{cr 210}{16.6 kg}
\rangedweapon{A3R}{The "Makar Advanced Anti-Armor Rifle": A long range rifle made to take out high value targets or light armor. Not an overly clever name but don't tell the snipers.}{Shots: 1; Damage: 2D10+7; AP: 18}{800m}{5 (11.8x112mm)}{6}{}{cr 210}{12.0 kg}
\rangedweapon{M5 Shotgun}{A scatter gun firing multiple pellets}{Shots: 2; Damage: 4D5+6; AP: 4}{80m}{8 (12gauge)}{16}{Single Loader, Scatter}{cr 130}{3.8 kg}
\rangedweapon{OP-2}{A 20mm single shot grenade launcher with increased barrel length}{Shots: 1; Damage: -; AP: depending on ammo}{50m}{1 (20mm grenade)}{4}{minimum arming distance of 10m}{cr 60}{1.9 kg}
\rangedweapon{"Rathalos" Flamethrower}{A flame thrower with an integrated tank to profit from familiar, proven rifle ergonomics.}{Shots: 5; Damage: 2D10+4; AP: 0}{35m}{15 (medium fuel tank)}{8}{Flame, Scatter, Spray}{cr 120}{4.0 kg}
\rangedweapon{BR-56}{A semiautomatic laser rifle}{Shots: 2; Damage: 1D10+18; AP: 3}{500m}{10 (medium fuel cell)}{12}{Adjustable}{cr 230}{4.3 kg}
\rangedweapon{Incinerator Rifle}{A long range laser rifle. Instead of piercing armor it burns it away.}{Shots: 1; Damage: 2D5+30; AP: 4}{700m}{1 (large fuel cell)}{16}{Adjustable, Flame}{cr 220}{9.7 kg}
\rangedweapon{M4 "Silver Crow"}{A handheld, semi automatic mass driver}{Shots: 2; Damage: 2D10+4; AP: 22}{550m}{16 (large mass driver shard block)}{10}{}{cr 180}{11.2 kg}
\rangedweapon{R235 Squad Support Weapon}{A fully automatic mass driver}{Shots: 5; Damage: 2D10+4; AP: 16}{180m}{180 (large mass driver shard block)}{18}{}{cr 250}{15.6 kg}
\rangedweapon{R13 "Armor Cracker"}{A handheld, long range mass driver}{Shots: 1; Damage: 1D5+18; AP: 35}{1400m}{7 (large mass driver shard block)}{16}{}{cr 260}{23.9 kg}
\rangedweapon{FG-9}{A rifle firing high energetic, self-stabilized plasma that explodes on impact. The energy release is highly unpredictable}{Shots: 1; Damage: 4D10+6; AP: 1}{40m}{10 (large fuel cell)}{16}{Blast (3), EMP, Stun (2)}{cr 310}{6.3 kg}
\rangedweapon{Choke M3 Arc Rifle}{An arc rifle with little spread to increase range}{Shots: 2; Damage: 3D10; AP: 0}{60m}{10 (large fuel cell)}{12}{EMP, Stun (3), Scatter}{cr 180}{4.1 kg}
\rangedweapon{Choke F3 Arc Thrower}{An arc rifle with a large spread made for crowd suppression}{Shots: 2; Damage: 5D5; AP: 0}{30m}{10 (large fuel cell)}{10}{EMP, Stun (2), Spray}{cr 150}{3.9 kg}
\end{multicols}

\subsubsection{Heavy}
\vspace{8mm}
\begin{multicols}{2}
\rangedweapon{M2 Brass Storm}{A high-caliber machine gun with high fire-rate.}{Shots: 8; Damage: 2D10+4; AP: 10}{220m}{120 (11.8x112mm)}{18}{}{cr 280}{42.7 kg}
\rangedweapon{M36 Chain Cannon}{A heavy machine gun with an external cycler. Reduced fire rate when compared to the M2 but renowned for unrivaled reliability. It is extremely heavy and cannot reasonably be called portable.}{Shots: 5; Damage: 2D10+4; AP: 10}{240m}{120 (11.8x112mm)}{18}{Reliable}{cr 295}{69.2 kg}
\rangedweapon{RM4 Chain Shotgun}{An automatic, belt fed shotgun known for its high maintenance need.}{Shots: 4; Damage: 4D5+6; AP: 4}{80m}{80 (12 gauge)}{18}{Scatter}{cr 280}{28.4 kg}
\rangedweapon{"Forge Fire" Heavy Flamer}{A large flamethrower made for vehicles and emplacements}{Shots: 5; Damage: 3D10+3; AP: 0}{50m}{30 (large fuel tank)}{40}{Flame, Scatter, Spray}{cr 220}{35.4 kg}
\rangedweapon{"Slicer" Laser Cannon}{A vehicle laser cannon, powerful enough to break bunker doors. Requires a massive power source to equalize its needs and is overly affected by refraction, limiting its range.}{Shots: 1; Damage: 5D10+20; AP: 8}{40m}{5 (vehicle power cell)}{40}{Powered}{cr 450}{231.0 kg}
\rangedweapon{Model 6 "Gladiator"}{A heavy mass driver sporting 5 rotating accelerators to prevent overheating and increase fire rate}{Shots: 12; Damage: 3D10+8; AP: 12}{500m}{500 (vehicle mass driver shard block)}{40}{Powered}{cr 420}{169.0 kg}
\rangedweapon{Mag Rail Cannon}{A massive mass driver built for anti armor LAVs in the days of war}{Shots: 1; Damage: 3D10+18; AP: 40}{6000m}{20 (vehicle mass driver shard block)}{40}{Powered}{cr 450}{143.0 kg}
\rangedweapon{"Zeushammer"}{Also referred to as the "Ball Lightning Cannon" this weapon is a long range Tesla cannon firing arcing ball lightnings.}{Shots: 1; Damage: 9D10-4; AP: }{150m}{5 (vehicle power cell)}{40}{Blast (6), EMP, Stun (5), Spray, Powered}{cr 410}{197.0 kg}
\end{multicols}

\subsubsection{Launcher}
\vspace{8mm}
\begin{multicols}{2}
\rangedweapon{MML-4}{A multi rocket launcher built for vehicles}{Shots: 2; Damage: -; AP: depending on ammo}{350m}{6 (rocket propelled grenade)}{40}{Powered, Backblast (4)}{cr 220}{36.9 kg}
\rangedweapon{WTFBRR}{A massive recoilless rifle made for giant loads to be fired from vehicles}{Shots: 1; Damage: -; AP: depending on ammo}{700m}{1 (large rocket propelled grenade)}{20}{Backblast (8)}{cr 360}{45.7 kg}
\rangedweapon{Hail Fire}{A micro missile launcher firing multiple rockets on multiple targets simultaneously}{Shots: 4; Damage: 3D10+2; AP: 4}{250m}{4 (micro missile packs)}{40}{Powered, Multitargeting, Backblast (2)}{cr 200}{26.7 kg}
\rangedweapon{M64}{A 40mm rotary grenade launcher}{Shots: 1; Damage: -; AP: depending on ammo}{100m}{6 (40mm grenade)}{36}{Single Loader, minimum arming distance of 15m}{cr 180}{5.4 kg}
\rangedweapon{ERPG}{A rocket propelled grenade launcher}{Shots: 1; Damage: -; AP: depending on ammo}{400m}{1 (rocket propelled grenade)}{6}{Backblast (4)}{cr 210}{6.2 kg}
\rangedweapon{OP-4}{A 40mm single shot grenade launcher}{Shots: 1; Damage: -; AP: depending on ammo}{70m}{1 (40mm grenade)}{6}{minimum arming distance of 15m}{cr 90}{2.2 kg}
\rangedweapon{"Thunderstrike" Grenade Launcher}{A grenade launcher fed from a belt. Very useful for crowd control but complete overkill in most situations. It is also extremely cumbersome due to the massive belt or belt box, much too large to be used on foot.}{Shots: 4; Damage: -; AP: -}{100m}{30 (40mm grenade)}{9}{minimum arming distance of 15m}{cr 136}{14.2 kg}
\end{multicols}

\pagebreak
\subsubsection{Bow}
\vspace{8mm}
\begin{multicols}{2}
\rangedweapon{Collapsible Bow}{A bow that can be collapsed to fit small cases for transportation and concealment.}{Shots: 1; Damage: 1D10+3; AP: 1}{50m}{1 (arrow)}{1}{Silenced}{cr 25}{1.5 kg}
\rangedweapon{Recurve Bow}{A full-sized bow with heavy draw.}{Shots: 1; Damage: 1D10+4; AP: 2}{75m}{1 (arrow)}{1}{Silenced, -10 to hit per StrB below 4}{cr 20}{3.2 kg}
\end{multicols}

\subsubsection{Throwing}
\vspace{8mm}
\begin{multicols}{2}
\rangedweapon{Asphyxiation Grenade}{A chemical weapon that burns away oxygen in a living room sized area. This reaction is not strongly exothermic, making it hard to detect before it's too late.}{Does not deal damage but causes suffocation.}{15m}{1 (Grenade)}{1}{Blast (5)}{cr 31}{0.3 kg}
\rangedweapon{EMP grenade}{Very expensive and very rare, this new type of explosive stuns or even damages unshielded electronics. It also causes piezoelectric exoskeletons to spasm and hurt the wearer.}{Shots: 1; Damage: 0; AP: 0}{15m}{1 (Grenade)}{1}{Blast (6), EMP}{cr 28}{0.1 kg}
\rangedweapon{Flashbang}{Popular among law enforcement personnel this non-lethal grenade blinds and deafens anyone not wearing appropriate protective gear with a loud and bright flash.}{Shots: 1; Damage: 0; AP: 0}{15m}{1 (Grenade)}{1}{Blast (12), Flash}{cr 14}{0.1 kg}
\rangedweapon{Frag grenade}{An explosive that spreads a large amount of shrapnel in a decently large area. Used against groups of hostiles and to clear rooms since the dawn of gunpowder.}{Shots: 1; Damage: 2D10+2; AP: 2}{15m}{1 (Grenade)}{1}{Blast (6)}{cr 22}{0.1 kg}
\rangedweapon{Incendiary grenade}{A fire-based explosive known to be easy and cheap to improvise and to cause a lot of collateral damage. Less useful against energy shielding and metal constructions.}{Shots: 1; Damage: 1D10+2; AP: 0}{15m}{1 (Grenade)}{1}{Blast (8), ignites flammable surfaces in the area}{cr 22}{0.1 kg}
\rangedweapon{Riot Foam}{A canister of sticky foam that heavily impairs movement of everyone caught up in it. Can safely but slowly be burnt away at low temperatures.}{Shots: 1; Damage: 0; AP: 0}{15m}{1 (Grenade)}{1}{Blast (12), Sticky}{cr 12}{0.1 kg}
\rangedweapon{Smoke grenade}{Favored in open places this non-lethal grenade grants a large amount of artificial concealment to otherwise clear lines of fire.}{Shots: 1; Damage: 0; AP: 0}{15m}{1 (Grenade)}{1}{Blast (8), Smoke}{cr 14}{0.1 kg}
\rangedweapon{Tear gas grenade}{Non-lethal irritant grenades usually employed to stop riots}{Shots: 1; Damage: 0; AP: 0}{15m}{1 (Grenade)}{1}{Blast (8), Smoke, Stun (0), Stun is applied every round in the Smoke}{cr 16}{0.1 kg}
\rangedweapon{Blunt throwing weapon}{Blunt instruments like rocks and bottles being thrown. Very common when nothing else is at hand.}{Shots: 1; Damage: 1D5+7; AP: 6}{15m}{1 (Blunt instruments)}{1}{Trauma, Piercing, Improvised}{Rocks are free}{1.0 kg}
\rangedweapon{Throwing axe}{Sharp, heavy, bladed weapon weighted for throwing}{Shots: 1; Damage: 1D10+3; AP: 0}{15m}{1 (Axes)}{1}{}{cr 12}{1.1 kg}
\rangedweapon{Throwing knives}{Sharp, bladed weapons weighted for throwing}{Shots: 1; Damage: 1D5+3; AP: 3}{15m}{1 (Knives)}{1}{}{cr 10}{0.4 kg}
\end{multicols}

\subsubsection{Traps}
\vspace{8mm}
\begin{multicols}{2}
\rangedweapon{Bear trap}{A strong, spring loaded clamp made to injure legs and stop creatures from fleeing or approaching.}{Shots: 1; Damage: 2D10+12}{0.3m}{-}{10}{}{cr 8}{1.1 kg}
\rangedweapon{C-7}{A block of plastic explosives. Usually made to be set up but can the thrown in a pinch}{Shots: 1; Damage: 2D10+18; AP: 16}{5m}{1 (C-7)}{2}{Blast (6)}{cr 22}{0.2 kg}
\rangedweapon{Cloak Mine}{A landmine with an integrated cloaking field. Makes an obvious noise when stepped upon and takes a decent amount of time to arm for safety reasons.}{Shots: 1; Damage: 2D10+5; AP: 4}{-}{1 (Mine)}{10}{Blast (3); detecting the noise when stepped upon takes a +0 Perception test}{cr 33}{1.2 kg}
\rangedweapon{Exploding Fuel Cell, Small}{A small fuel cell, usually built very sturdily, may be rigged as an improvised explosive device. Unstable cells however may explode when handled too roughly in high temperatures.}{Shots: 1; Damage: 2D10+4; AP: 6}{15m}{1 (small fuel cell)}{1}{Blast (1)}{cr 9}{0.3 kg}
\rangedweapon{Exploding Fuel Cell, Medium}{A fuel cell, usually built very sturdily, may be rigged as an improvised explosive device. Unstable cells however may explode when handled too roughly in high temperatures.}{Shots: 1; Damage: 3D10+6; AP: 9}{15m}{1 (medium fuel cell)}{1}{Blast (1)}{cr 15}{0.8 kg}
\rangedweapon{Exploding Fuel Cell, Large}{A large fuel cell, usually built very sturdily, may be rigged as an improvised explosive device. Unstable cells however may explode when handled too roughly in high temperatures.}{Shots: 1; Damage: 4D10+8; AP: 12}{15m}{1 (large fuel cell)}{1}{Blast (2)}{cr 21}{1.5 kg}
\end{multicols}

\pagebreak %quick fix
\subsection{Mods}
\subsubsection{Constraints}
Ranged weapons have a limited number of mod slots which can each only be used once - at some point the weapon becomes unwieldy or the space is simply used up. When in question, apply common sense.\par\vspace{10mm}

\begin{multicols}{2}
Pistols:
\vspace{-8mm}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item Upper Rail
	\item Lower Rail
	\item Barrel
	\item Muzzle
	\item Core
\end{enumerate}

Rifle:
\vspace{-8mm}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item Upper Rail
	\item Lower Rail
	\item Two Side Rails
	\item Barrel
	\item Muzzle
	\item Core
\end{enumerate}

Heavy Weapon / Launcher:
\vspace{-8mm}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item Upper Rail
	\item Lower Rail
	\item Lower Rail (restricted to bipod / tripod)
	\item Two Side Rails
	\item Barrel
	\item Muzzle
	\item Core
\end{enumerate}

Bow:
\vspace{-8mm}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item Upper Rail
	\item Core
\end{enumerate}
\end{multicols}

\subsubsection{Optics}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Reflex Sight}{A simple 1x scope with good eye relief, barely obstructing peripheral vision.}{Upper Rail}{cr 5}{0.15 kg}
\weaponmod{Holographic Sight}{A non-magnifying 1x sight that is only projected when the character makes an Aim action. Only takes up minimal space on the rail it is mounted, allowing for another item to be mounted without taking this sight off.}{Upper Rail}{cr 7}{0.2 kg}
\weaponmod{Flip-Up Magnifier}{A 3x magnifier to be used in conjunction with a non-magnifying sight.}{Upper Rail}{cr 7}{0.32 kg}
\weaponmod{AOG}{A common, analog 4x combat scope.}{Upper Rail}{cr 12}{0.35 kg}
\weaponmod{TEGS}{The Tactical Electronic Gun Sight is a common variable 4-6x combat scope. Due to using electronic magnification it is vulnerable to EMP.}{Upper Rail}{cr 32}{0.38 kg}
\weaponmod{LoRa Sight}{An 8x scope - the cheapest long range sight but usually absolutely sufficient.}{Upper Rail}{cr 16}{0.4 kg}
\weaponmod{LS-Marksman Scope}{A massive 14x scope used for the longest ranges.}{Upper Rail}{cr 28}{0.42 kg}
\weaponmod{Oculus Marksman System}{A variable 8-14x electronic scope. Like other electronic magnifiers it is vulnerable to EMP.}{Upper Rail}{cr 51}{0.43 kg}
\weaponmod{TS-CQC}{A non-magnifying thermal imaging sight with a sleek profile created for CQC.}{Upper Rail}{cr 42}{0.52 kg}
\weaponmod{TS-BR}{A 5x battle rifle scope with thermal imaging capabilities.}{Upper Rail}{cr 68}{0.67 kg}
\weaponmod{TS-M}{A 10x marksman scope with thermal imaging capabilities.}{Upper Rail}{cr 78}{0.67 kg}
\weaponmod{Canted Irons}{A 45-degree offset rail mount is added to the top of the weapon for the use of a secondary Iron sight/Optic/Light.}{-}{cr 8}{0.1 kg}
\end{multicols}

\subsubsection{Lights}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Laser Module}{Gives a +5 bonus to hit when not using aim actions. A target spotting the dot with a -10 Perception test cannot be surprised.}{Any rail}{cr 14}{0.1 kg}
\weaponmod{Infrared Laser Module}{Works like a laser module but it can only be seen with thermal imaging.}{Any rail}{cr 28}{0.2 kg}
\weaponmod{Flashlight}{A flashlight is attached to the weapon, able to light wherever the wielder is aiming.}{Any rail}{cr 6}{0.26 kg}
\end{multicols}

\pagebreak %remove when it becomes unnecessary
\subsubsection{Muzzles}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Muzzle Brake}{Reduces recoil, thereby halving penalties from Burst actions.}{Muzzle}{cr 20}{0.2 kg}
\weaponmod{Flash Suppressor}{Reduces muzzle flash, inferring a -30 penalty to visual perception checks to spot the weapon firing.}{Muzzle}{cr 22}{0.2 kg}
\weaponmod{Sound Suppressor}{Reduces both noise and muzzle flash, granting a -30 penalty to all visual perception checks to spot the weapon firing and -10 to hearing based tests; can be combined with cold load ammunition}{Muzzle}{cr 28}{0.2 kg}
\weaponmod{Shotgun Choke, wide}{Reduces pellet spread on shotguns somewhat. Scatter rule only gives a hit bonus from normal range onward. Range is increased by 50\%.}{Muzzle}{cr 12}{0.2 kg}
\weaponmod{Shotgun Choke, narrow}{Reduces pellet spread on shotguns a lot. Scatter rule only gives a hit bonus from long range onward. Range is increased by 100\%.}{Muzzle}{cr 12}{0.2 kg}
\end{multicols}

\subsubsection{Underslung Weapons}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Skeleton Key}{Adds an underslung MS shotgun with half range. Due to increased weight at the front this infers a -5 to hit when using aim actions without a rest.}{Lower Rail}{cr 28}{2.8 kg}
\weaponmod{Underslung "Thumper"}{Adds an underslung "Thumper" CQC Grenade Launcher with half range. Due to increased weight at the front this infers a -5 to hit when using aim actions without a rest.}{Lower Rail}{cr 70}{3.2 kg}
\end{multicols}

\subsubsection{Braces / Grips}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Angled Grip}{A fast-pull grip that grants +2 initiative when using both hands and no rest.}{Lower Rail}{cr 8}{0.1 kg}
\weaponmod{Pistol Grip}{A stable grip that increases aim bonus by 5 when using both hands and no rest.}{Lower Rail}{cr 8}{0.1 kg}
\weaponmod{Bipod/Tripod}{A stable rest that increases aim bonus by 10 when deployed. A bipod is short and to be used over cover or while prone. Tripods are large and to be used while standing.}{Lower Rail}{cr 10}{0.15 kg}
\end{multicols}

\subsubsection{Barrel}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Extended Barrel}{A longer barrel that increases optimum range and armor penetration by 25\%. Such a long weapon may be difficult to use in confined spaces.}{Barrel}{cr 23}{0.2 kg}
\weaponmod{Heavy Barrel}{A heavy, more stable barrel. It halves penalties from shooting while on the move but decreases aim bonus by 10 when not using a rest.}{Barrel}{cr 11}{0.2 kg}
\end{multicols}

\subsubsection{Ammunition}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Magazine}{A simple magazine for a ballistic weapon. It holds ammunition in the gun.}{Ballistic Magazine}{cr 12}{-}
\weaponmod{Extended-Mag/Belt}{A larger magazine that doubles mag size but is more prone to error, causing jams on 96 and above.}{Ballistic Magazine}{cr 26}{-}
\weaponmod{Drum-Mag}{A massive spiral magazine that triples mag size but jams on 96+ and also doesn't fit in normal mag pouches, therefore need to be carried in backpacks.}{Ballistic Magazine}{cr 34}{-}
\weaponmod{Dual-Mag}{Taped magazines make swapping from one to the other take half as long, however it doesn't fit in mag pouches anymore. Can easily be improvised with 2 magazines and some duct tape.}{Ballistic Magazine}{-}{-}
\weaponmod{Shell Holder}{A clip attached to a rail holding up to 8 shotgun shells. Very useful for special ammunition.}{Any Rail}{cr 2}{-}
\weaponmod{Bolt Holder}{A container holding up to 8 bolts attached below a crossbow.}{Core}{cr 3}{-}
\end{multicols}

\pagebreak %quick fix
\subsubsection{Misc}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Camouflage Paint}{If the pattern matches the environment, grants a -20 penalty to visually perceive the weapon. However if the pattern doesn't match, it grants a +5 to visually perceive the weapon instead.}{Paint}{cr 3}{0 kg}
\weaponmod{Ghillie Cover}{If the pattern matches the environment, grants a -30 penalty to visually perceive the weapon. However if the pattern doesn't match, it grants a +10 to visually perceive the weapon instead.\\
	Unlike with camouflage paint patterns only exist for desert and forest.}{Paint}{cr 4}{0.15 kg}
\end{multicols}

\subsubsection{Core}
\vspace{8mm}
\begin{multicols}{2}
\weaponmod{Offload Cycler}{A technological marvel increasing a weapon's fire rate by 50\%, rounded down, if it already has a fire rate of 2 or more.}{Core}{80\%}{0.9 kg}
\weaponmod{Multi Barrel}{Adds an additional barrel feeding from the same magazine to double the amount of hits and ammo spent at an additional -10 penalty to hit. Only works if the weapon has a capacity of at least 2.}{Core}{60\%}{0.55 kg}
\weaponmod{Heatsink}{A heat sink removing the drawbacks from the Adjustable rule. It increases the weapon's weight by 20\%.}{Core}{40\%}{20\%}
\weaponmod{Backblast Refunneling}{It halves the Backblast range to increase the weapon's range by 50\%. The additional rumble gives a penalty equal to half of the user's strength difference to 70.}{Core}{60\%}{0.4 kg}
\weaponmod{Gim-barrel}{A self-stabilizing barrel halves penalties from shooting while moving as well as Burst actions. It doubles the weapon's weight and decreases aim bonus by 5 when not using a rest.}{Core, Barrel}{80\%}{100\%}
\weaponmod{Biocoding}{A trigger lock reading biometric data of the user. The weapon can only be used when wielded by a user who was registered during building of the weapon. It cannot be removed or reprogrammed without destroying the weapon.}{none}{cr 20}{0.24 kg}
\weaponmod{Vehicle Lock-on}{Adds vehicle lock-on to a Launcher or Heavy weapon; grants +30 to hitting vehicles and powered armor when taking at least one round to aim. Flares don't disrupt targeting but static smoke will.}{Core}{80\%}{3.4 kg}
\weaponmod{Heat Seeker}{Adds heat-based targeting assistance systems, thereby granting +15 to shoot targets warmer than their surroundings but -15 to shoot targets colder than their surroundings.}{Core}{cr 280}{2.3 kg}
\weaponmod{Energy Shield}{Adds a directional PES that covers the user's head and torso. Covers the whole user instead if used with a tripod.\\
	Armor: 15 / Threshold: 4}{Core}{cr 180}{3.8 kg}
\weaponmod{Smart Gun}{Sophisticated aiming assistance takes care of all the hard work. The gun always uses a target value of 65 when taking shots, regardless of modifiers or the shooter. It still requires to be pointed in roughly the right direction though and will completely fail under EMP.}{Core}{cr 190}{6.9kg}
\end{multicols}

\subsection{Ammunition}
In the following section ammo types are given in this format:\\
First, in bold, there is the type designation. This is little more than an identifier.\\
Secondly after the colon you find the effect. These are all changes this type of ammunition has as opposed to the basic weapon profile.\\
The price is the price per box off ammunition; every box contains an amount of ammunition equal to the value given at "Unit of sale". For ballistic ammo a single unit is one bullet, for others it is one full load of the weapon.\\
Weight and bulk are given in the weight that one "standard magazine" - as used in storage capacities - weighs.
%	Pistols
\subsubsection{7.2mm}
\vspace{8mm}
\begin{multicols}{2}
\ammo{FMJ}{-}{cr 2}{30}{4g}{40}
\ammo{AP}{-1 dmg, +4 AP}{cr 3}{30}{4g}{40}
\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 4}{30}{4g}{40}
\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 6}{30}{4g}{40}
\ammo{JSP}{+2 dmg, -3 AP}{cr 3}{30}{4g}{40}
\ammo{JHP}{+4 dmg, -6 AP}{cr 4}{30}{4g}{40}
\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 6}{30}{4g}{40}
\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 3}{30}{4g}{40}
\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{4g}{40}
\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{4g}{40}
\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{30}{4g}{40}
\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 3}{30}{4g}{40}
\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 4}{30}{4g}{40}
\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 2}{30}{4g}{40}
\end{multicols}
\subsubsection{11.8x45mm}
\vspace{8mm}
\begin{multicols}{2}
\ammo{FMJ}{-}{cr 3}{20}{22g}{40}
\ammo{AP}{-1 dmg, +4 AP}{cr 5}{20}{22g}{40}
\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 6}{20}{22g}{40}
\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 9}{20}{22g}{40}
\ammo{JSP}{+2 dmg, -3 AP}{cr 5}{20}{22g}{40}
\ammo{JHP}{+4 dmg, -6 AP}{cr 6}{20}{22g}{40}
\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 9}{20}{22g}{40}
\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 5}{20}{22g}{40}
\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 6}{20}{22g}{40}
\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{20}{22g}{40}
\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 9}{20}{22g}{40}
\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 5}{20}{22g}{40}
\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 6}{20}{22g}{40}
\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 3}{20}{22g}{40}
\end{multicols}

%	Rifles
\subsubsection{6.3mm}
\vspace{8mm}
\begin{multicols}{2}
\ammo{FMJ}{-}{cr 2}{30}{8.6g}{30}
\ammo{AP}{-1 dmg, +4 AP}{cr 3}{30}{8.6g}{30}
\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 4}{30}{8.6g}{30}
\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 6}{30}{8.6g}{30}
\ammo{JSP}{+2 dmg, -3 AP}{cr 3}{30}{8.6g}{30}
\ammo{JHP}{+4 dmg, -6 AP}{cr 4}{30}{8.6g}{30}
\ammo{Shield Breaker}{-3 dmg, Disrupt}{cr 5}{30}{8.6g}{30}
\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 6}{30}{8.6g}{30}
\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 3}{30}{8.6g}{30}
\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{8.6g}{30}
\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 4}{30}{8.6g}{30}
\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{30}{8.6g}{30}
\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 3}{30}{8.6g}{30}
\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 4}{30}{8.6g}{30}
\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 2}{30}{8.6g}{30}
\end{multicols}
\subsubsection{11.8x112mm}
\vspace{8mm}
\begin{multicols}{2}
\ammo{FMJ}{-}{cr 4}{20}{50g}{5}
\ammo{AP}{-1 dmg, +4 AP}{cr 6}{20}{50g}{5}
\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 8}{20}{50g}{5}
\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 12}{20}{50g}{5}
\ammo{JSP}{+2 dmg, -3 AP}{cr 6}{20}{50g}{5}
\ammo{JHP}{+4 dmg, -6 AP}{cr 8}{20}{50g}{5}
\ammo{Shield Breaker}{-3 dmg, Disrupt}{cr 8}{20}{50g}{5}
\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 12}{20}{50g}{5}
\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 6}{20}{50g}{5}
\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 8}{20}{50g}{5}
\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 8}{20}{50g}{5}
\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 12}{20}{50g}{5}
\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 6}{20}{50g}{5}
\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 8}{20}{50g}{5}
\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 4}{20}{50g}{5}
\end{multicols}
\subsubsection{15x132mm}
\vspace{8mm}
\begin{multicols}{2}
\ammo{FMJ}{-}{cr 5}{5}{85g}{4}
\ammo{AP}{-1 dmg, +4 AP}{cr 8}{5}{85g}{4}
\ammo{Hot Load}{+1 dmg, +4 AP, +15 on hearing checks to identify the shooter's position}{cr 10}{5}{85g}{4}
\ammo{Hot AP}{+10 AP, +15 on hearing checks to identify the shooter's position}{cr 15}{5}{85g}{4}
\ammo{JSP}{+2 dmg, -3 AP}{cr 8}{5}{85g}{4}
\ammo{JHP}{+4 dmg, -6 AP}{cr 10}{5}{85g}{4}
\ammo{Shock}{-4 dmg, -5 AP, Stun (4), EMP}{cr 15}{5}{85g}{4}
\ammo{Cold Load}{-3 dmg, -3 AP, -15 on hearing checks to identify the shooter's position}{cr 8}{5}{85g}{4}
\ammo{Cold AP}{-4 dmg, -15 on hearing checks to identify the shooter's position}{cr 10}{5}{85g}{4}
\ammo{Cold JSP}{-6 AP, -15 on hearing checks to identify the shooter's position}{cr 10}{5}{85g}{4}
\ammo{Cold JHP}{+2 dmg, -8 AP, -15 on hearing checks to identify the shooter's position}{cr 15}{5}{85g}{4}
\ammo{Incendiary}{-2 AP, will ignite flammable materials hit}{cr 8}{5}{85g}{4}
\ammo{Tracer}{grants a +10 bonus to hit for others aiming at the same target during this turn}{cr 10}{5}{85g}{4}
\ammo{Rubber Rounds}{-10 dmg, 0 AP, Stun (2), every hit against the target's head reduces it's initiative by D5-1}{cr 5}{5}{85g}{4}
\end{multicols}

%	Shotgun
\subsubsection{12gauge}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Buckshot}{-}{cr 3}{24}{42g}{8}
\ammo{Birdshot}{halves damage, ignores all negative size modifiers}{cr 2}{24}{42g}{8}
\ammo{Incendiary}{-2 dmg, -4 AP, ignites flammable materials hit}{cr 3}{24}{42g}{8}
\ammo{Breaching Round}{+3 dmg, +4 AP, halved range}{cr 5}{24}{42g}{8}
\ammo{Slug}{+2 AP, removes Scatter, doubles range}{cr 3}{24}{42g}{8}
\ammo{Fragmentation Slug}{removes Scatter but adds Blast (2) rule, doubles range}{cr 6}{24}{42g}{8}
\ammo{Incendiary Slug}{+1 AP, removes Scatter, doubles range, ignites flammable objects hit}{cr 4}{24}{42g}{8}
\ammo{EMP Slug}{-2 dmg, EMP, removes Scatter, doubles range}{cr 9}{24}{42g}{8}
\ammo{Rubber Slug}{-2 dmg, -6 AP, removes Scatter, doubles range, Stun (2)}{cr 3}{24}{42g}{8}
\end{multicols}

%	Fuel Tank
\subsubsection{Small Fuel Tanks}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Napalm}{ignites flammable surfaces and sticks even to non-flammable ones}{cr 32}{1}{10kg}{}
\ammo{White Phosphorus}{halves range, burns for a D5 minutes, ignites flammable surfaces and sticks even to non-flammable ones, cannot be extinguished by water}{cr 64}{1}{20kg}{}
\ammo{Water}{1 dmg, 0 AP, Trauma, Stun (*the original amount of damage dice)}{cr 8}{1}{13kg}{}
\ammo{Liquid Helium}{halves range, causes D5 exhaustion per hit}{cr 64}{1}{13kg}{}
\end{multicols}

\subsubsection{Medium Fuel Tanks}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Napalm}{ignites flammable surfaces}{cr 61}{1}{20kg}{}
\ammo{White Phosphorus}{halves range, burns for a D5 minutes, ignites flammable surfaces and sticks even to non-flammable ones}{cr 122}{1}{40kg}{}
\ammo{Water}{1 dmg, 0 AP, Trauma, Stun (*the original amount of damage dice)}{cr 17}{1}{25kg}{}
\ammo{Liquid Helium}{halves range, causes D5 exhaustion per hit}{cr 122}{1}{25kg}{}
\end{multicols}

\subsubsection{Large Fuel Tanks}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Napalm}{ignites flammable surfaces}{cr 150}{1}{50kg}{}
\ammo{White Phosphorus}{halves range, burns for a D5 minutes, ignites flammable surfaces and sticks even to non-flammable ones}{cr 300}{1}{100kg}{}
\ammo{Water}{1 dmg, 0 AP, Trauma, Stun (*the original amount of damage dice)}{cr 32}{1}{62.5kg}{}
\ammo{Liquid Helium}{halves range, causes D10 exhaustion per hit}{cr 300}{1}{62.5kg}{}
\end{multicols}

%	Fuel Cells
\subsubsection{Small Fuel Cells}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Standard Issue}{-}{cr 9}{1}{250g}{2}
\ammo{Unstable}{On a hit roll above 95 causes the weapon's damage with Blast (1) around the shooter.}{cr 5}{1}{250g}{2}
\end{multicols}
\pagebreak %remove if it becomes unnecessary
\subsubsection{Medium Fuel Cells}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Standard Issue}{-}{cr 15}{1}{750g}{}
\ammo{Unstable}{On a hit roll above 95 causes the weapon's damage with Blast (1) around the shooter.}{cr 8}{1}{750g}{}
\end{multicols}
\subsubsection{Large Fuel Cells}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Standard Issue}{-}{cr 21}{1}{1.5kg}{0.5}
\ammo{Unstable}{On a hit roll above 95 causes the weapon's damage with Blast (1) around the shooter.}{cr 11}{1}{1.5kg}{0.5}
\end{multicols}

%	Mass Driver Blocks
\subsubsection{Small Shard Blocks}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Standard Issue}{-}{cr 2}{1}{300g}{1}
\ammo{Crude}{-50\% mag size, jams on 91 and above}{cr 1}{2}{300g}{1}
\end{multicols}
\subsubsection{Large Shard Blocks}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Standard Issue}{-}{cr 5}{1}{1.8kg}{0.5}
\ammo{Crude}{-50\% mag size, jams on 91 and above}{cr 2}{2}{1.8kg}{0.5}
\ammo{Osmium Alloy}{+4 damage, -2 AP}{cr 10}{1}{3.6kg}{0.5}
\end{multicols}
\pagebreak %remove if it becomes unnecessary
\subsubsection{Vehicle Shard Blocks}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Standard Issue}{-}{cr 11}{1}{3.2kg}{0.2}
\ammo{Crude}{-50\% mag size, jams on 91 and above}{cr 5}{2}{3.2kg}{0.2}
\ammo{Osmium Alloy}{+4 damage, -2 AP}{cr 21}{2}{6.2kg}{0.5}
\end{multicols}

%	Grenades
\subsubsection{20mm grenades}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Fragmentation}{2D10+2 | 2 AP | Blast (6)}{cr 60}{1}{120g}{0.5}
\ammo{High Explosive}{2D10+6 | 5 AP | Blast (2)}{cr 60}{1}{120g}{0.5}
\ammo{Thermobaric}{3D10 | 2 AP | Blast (10) | heat-based, ignores all cover and non-vacuum-sealed or natural armor}{cr 96}{1}{120g}{0.5}
\ammo{Incendiary}{D10+2 | 0 AP | Blast (8) | ignites all flammable objects in the radius}{cr 60}{1}{120g}{0.5}
\ammo{Buckshot Canister}{2D10+3 | 5 AP | Scatter}{cr 75}{1}{120g}{0.5}
\ammo{Slug}{2D5+8 | 8 AP}{cr 75}{1}{120g}{0.5}
\ammo{Smoke}{0 | 0 AP | Blast (8), Smoke}{cr 45}{1}{120g}{0.5}
\ammo{Flashbang}{0 | 0 AP | Blast (12), Flash}{cr 45}{1}{120g}{0.5}
\ammo{EMP}{0 | 0 AP | Blast (6), EMP}{cr 80}{1}{120g}{0.5}
\ammo{Tear Gas}{0 | 0 AP | Blast (6), Smoke, Stun (0), ignores cover and non-vacuum-sealed armor, Stun is applied every round in the Smoke}{cr 45}{1}{120g}{0.5}
\ammo{Rubber Slug}{1D10+3 | 2 AP | Stun (5), hits to the head cause 2D5 initiative loss}{cr 50}{1}{120g}{0.5}
\ammo{Riot Foam}{0 | 0 AP | Blast (12), Sticky}{cr 20}{1}{120g}{0.5}
\ammo{Signal Smoke}{0 | 0 AP | Blast (4) | a smoke spewer to signal allies; comes in various colors}{cr 38}{1}{120g}{0.5}
\ammo{Parachute Flare}{D5 | 0 AP | a signal flare that burns for 3 minutes and falls at 1 meter per 3 seconds (or 1 round)}{cr 40}{1}{120g}{0.5}
\ammo{Infrared Illuminator}{1 | 0 AP | a large chemlight that emits infrared light in a very large area}{cr 42}{1}{120g}{0.5}
\end{multicols}
\subsubsection{40mm grenades}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Fragmentation}{2D10+7 | 2 AP | Blast (9)}{cr 78}{1}{230g}{1}
\ammo{High Explosive}{3D10+6 | 5 AP | Blast (3)}{cr 78}{1}{230g}{1}
\ammo{Thermobaric}{4D10 | 2 AP | Blast (15) | heat-based, ignores all cover and non-vacuum-sealed armor}{cr 125}{1}{230g}{1}
\ammo{Incendiary}{D10+3 | 0 AP | Blast (12) | ignites all flammable objects in the radius}{cr 78}{1}{230g}{1}
\ammo{Buckshot Canister}{3D10+3 | 5 AP | Scatter}{cr 98}{1}{230g}{1}
\ammo{Slug}{2D10+9 | 9 AP}{cr 98}{1}{230g}{1}
\ammo{Smoke}{0 | 0 AP | Blast (12), Smoke}{cr 59}{1}{230g}{1}
\ammo{Flashbang}{0 | 0 AP | Blast (18), Flash}{cr 59}{1}{230g}{1}
\ammo{EMP}{0 | 0 AP | Blast (9), EMP}{cr 104}{1}{230g}{1}
\ammo{Tear Gas}{0 | 0 AP | Blast (8), Smoke, Stun (0), ignores cover and non-vacuum-sealed armor, Stun is applied every round in the Smoke}{cr 59}{1}{230g}{1}
\ammo{Rubber Slug}{2D10+3 | 2 AP | Stun (7), hits to the head cause 2D10 initiative loss}{cr 65}{1}{230g}{1}
\ammo{Signal Smoke}{0 | 0 AP | Blast (4) | a smoke spewer to signal allies that lasts for a few minutes; comes in various colors}{cr 49}{1}{230g}{1}
\ammo{Parachute Flare}{D5+1 | 0 AP | a signal flare that burns for 5 minutes and falls at 1 meter per 3 seconds (or 1 round)}{cr 52}{1}{230g}{1}
\ammo{Thermite}{6D10+10 | 25 AP | Blast (3) | takes two rounds to get going, then burns for one minute dealing its damage every round; sticks to rough surfaces}{cr 156}{1}{230g}{1}
\end{multicols}

%	Rockets
\subsubsection{Micro Missiles}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Fragmentation}{-}{cr 84}{4}{1kg}{0.5}
\ammo{High Explosive}{-1D10 dmg | +8 AP}{cr 88}{4}{1kg}{0.5}
\ammo{Incendiary}{-3 dmg | -3 AP | ignites flammable objects}{cr 76}{4}{1kg}{0.5}
\end{multicols}
\subsubsection{Small Rockets}
\vspace{8mm}
\begin{multicols}{2}
\ammo{HEAT}{4D10+5 dmg | 6 AP | Blast (5)}{cr 124}{1}{2kg}{0.5}
\ammo{High Explosive}{4D10+2 dmg | 3 AP | Blast (6)}{cr 99}{1}{2kg}{0.5}
\ammo{Fragmentation}{3D10+8 dmg | 2 AP | Blast (8)}{cr 99}{1}{2kg}{0.5}
\ammo{Incendiary}{2D10+5 dmg | 2 AP | Blast (6) | ignites flammable objects}{cr 112}{1}{2kg}{0.5}
\ammo{Incendiary Fragmentation}{3D10+5 dmg | 2 AP | Blast (8) | ignites flammable objects}{cr 134}{1}{2kg}{0.5}
\ammo{Thermobaric}{4D10+8 dmg | 3 AP | Blast (12) | heat-based, ignores all cover and non-vacuum-sealed armor}{cr 201}{1}{2kg}{0.5}
\ammo{Thermite}{6D10+10 | 25 AP | Blast (4) | takes two rounds to get going, then burns for one minute dealing its damage every round; sticks to rough surfaces}{cr 179}{1}{2kg}{0.5}
\ammo{Kinetic Penetrator}{4D10+5 dmg | 14 AP}{cr 201}{1}{2kg}{0.5}
\end{multicols}
\subsubsection{Large Rockets}
\vspace{8mm}
\begin{multicols}{2}
\ammo{HEAT}{4D10+6 dmg | 8 AP | Blast (6)}{cr 168}{1}{3.5kg}{0.25}
\ammo{High Explosive}{4D10+4 dmg | 5 AP | Blast (8)}{cr 134}{1}{3.5kg}{0.25}
\ammo{Fragmentation}{3D10+11 dmg | 3 AP | Blast (10)}{cr 134}{1}{3.5kg}{0.25}
\ammo{Incendiary}{2D10+8 dmg | 2 AP | Blast (8) | ignites flammable objects}{cr 151}{1}{3.5kg}{0.25}
\ammo{Incendiary Fragmentation}{3D10+8 dmg | 3 AP | Blast (10) | ignites flammable objects}{cr 181}{1}{3.5kg}{0.25}
\ammo{Thermobaric}{5D10+10 dmg | 5 AP | Blast (18) | heat-based, ignores all cover and non-vacuum-sealed armor}{cr 272}{1}{3.5kg}{0.25}
\ammo{Thermite}{6D10+10 | 25 AP | Blast (6) | takes two rounds to get going, then burns for one minute dealing its damage every round; sticks to rough surfaces}{cr 242}{1}{3.5kg}{0.25}
\ammo{Kinetic Penetrator}{4D10+8 dmg | 18 AP}{cr 272}{1}{3.5kg}{0.25}
\end{multicols}

%	Arrows / Bolts
\subsubsection{Arrows}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Broadhead}{-}{cr 1}{25}{30g}{10}
\ammo{AP}{-1 dmg, +3 AP}{cr 1}{25}{30g}{10}
\ammo{Shield Breaker}{-1 dmg, Disrupt}{cr 2}{25}{30g}{10}
\ammo{Syringer}{-3 dmg, +1 AP, contains an empty vial to be filled with poisons or other injections that are released into a biological target when hit}{cr 3}{25}{30g}{10}
\ammo{Grapple}{-4 dmg, 0 AP, half range; the mechanized grapple attaches to a rope and holds on most surfaces but e.g. very sturdy metals or fragile materials like glass}{cr 6}{1}{30g}{10}
\end{multicols}
\subsubsection{Bolts}
\vspace{8mm}
\begin{multicols}{2}
\ammo{Broadhead}{-}{cr 1}{25}{30g}{10}
\ammo{AP}{-1 dmg, +3 AP}{cr 1}{25}{30g}{10}
\ammo{Shield Breaker}{-1 dmg, Disrupt}{cr 2}{25}{30g}{10}
\ammo{Syringer}{-3 dmg, +1 AP, contains an empty vial to be filled with poisons or other injections that are released into a biological target when hit}{cr 3}{25}{30g}{10}
\ammo{Grapple}{-4 dmg, 0 AP, half range; the mechanized grapple attaches to a rope and holds on most surfaces but e.g. very sturdy metals or fragile materials like glass}{cr 6}{1}{30g}{10}
\end{multicols}
