\section{Services}
\vspace{10mm}
\begin{multicols}{2}
%Manpower
\service{Goon}{Hire a simple goon.}{cr 18}{day}
\service{Bodyguard}{Hire a trained bodyguard.}{cr 32}{day}
\service{Fire Team}{Employ a fire team of mercenaries.}{cr 100}{soldier}
\service{Strike Team}{Employ a strike team.}{cr 700}{soldier}
\service{Spec Ops}{Call in a special operations team.}{cr 320}{soldier}

%Fire support
\service{CAS}{Call in close air-support on a marked location.
	Very effective against infantry, less against fortifications and armor.}{cr 200}{run}
\service{Bombing Run}{Call in a bombing run on a marked target.
	Very effective against infantry, high risk of collateral damage.}{cr 250}{run}
\service{MAC Strike}{Call in a rail cannon strike on a marked target.
	Relatively small area of effect, massive effect against armor.}{cr 400}{strike}

%Assassination
\service{Hitman (Simple target)}{Set a hitman on a rather simple target like a former soldier.}{cr 250}{target}
\service{Hitman (Advanced Target)}{Set a hitman on a difficult target like an active general.}{at least cR 1200}{target}

%Medical
\service{Back Alley Doc}{The character is healed D5+1 wounds from medical attention and no word is lost about where those injuries came from.}{cr 25}{session}
\service{Back Alley Surgery}{One of:\\
	a) Install an augment, no questions asked. Recovery time is doubled.\\
	b) The character undergoes facial reassembly,
	becoming unrecognizable from sight alone.}{cr 45}{session}
\service{Hospital}{One of:\\
	a) The character is healed 4D5+2 wounds from medical attention.\\
	b) Install an augment.}{cr 155}{session}
\service{Medical Tank}{The character is put into a medical tank.
	He doesn't bleed, poisons stop and he is granted one natural regeneration phase per hour.
	Since the setup and post-regeneration cleanup are the difficult and time consuming things,
	no time frame under 24 hours is usually at offer.}{cr 380}{24 hours}

%Transportation
\service{Taxi (Safe Area)}{The character is taken to a desired location. The ride goes through only safe neighborhoods.}{cr 7}{10 km}
\service{Taxi (Dangerous Area)}{The character is taken to a desired location. The ride goes through a dangerous neighborhood.}{cr 4}{km}
\service{VTOL Ride}{The character is taken to a desired location by a VTOL aircraft, like a helicopter.}{cr 40}{10 km}
\service{Orbital Drop}{Drop from low orbit onto a desired location. This can obviously not be taken for inside underground complexes but may dig through a bunker's ceiling and trash buildings.}{cr 375}{jump}
\end{multicols}
