	\section{Supply}
\subsection{Communication}
\vspace{10mm}
\begin{multicols}{2}
\supply{EC-Comm}
    {Two-way communicator that fits in the ear.
        There are variants for all types of trans-species widely available.
        Vat-grown are assumed to have normal human proportions.}
    {18}
    {0,01}
\supply{Emergency Location Beacon}
    {An emergency beacon used for creating distress signals.
        Able to send an emergency signal on multiple open channels up to 15 kilometers instantly,
        potentially more with some delay.}
    {5}
    {0,03}
\supply{Marker/Transmitter}
    {Small tracking device and location transmitter.
        Can be tethered to almost and tracked by almost any smart device, such as phones.}
    {22}
    {0,005}
\end{multicols}

%\vspace{5mm} %adjusts page break
\subsection{Cyberware}
\vspace{10mm}
\begin{multicols}{2}
    \supply{AI Docking Station}{By itself this device does nothing, but it fulfills the requirements to hold strong AI.\\
	Integrity: 15\\
	Firewall: 6\\
	Processing Power: +25}
    {512}
    {12}
\supply{Business/Lab Server}{A large device with a lot of processing power and storage but without an inbuilt user interface; either needs a direct connection or access via a network.\\
	Integrity: 40\\
	Firewall: 6\\
	Processing Power: +30}
    {420}
    {26}
\supply{Cell Phone}{A communication device small enough to fit into one's pocket.\\
	Integrity: 5\\
	Firewall: 1\\
	Processing power: 0}
    {18}
    {0,6}
\supply{Cheap Router/Switch}{A connection device to create or scale networks.\\
	Integrity: 11\\
	Firewall: 2 (may work for connected devices, if the attack passes through)\\
	Processing Power: +5}
    {12}
    {0,7}
\supply{Cracker}{An expensive machine with incredible processing power.\\
	Integrity: 40\\
	Firewall: 8\\
	Processing Power: +30}
    {690}{9}
\supply{Portable AI Docking Station}{By itself this device does nothing but it has the requirements to hold an AI. It's small enough to be carried around.\\
	Integrity: 15\\
	Firewall: 5\\
	Processing Power: +20}
    {896}
    {5}
\supply{Secure Router/Switch}{A connection device to create or scale networks. Comes with a few security measures and proper configuration.\\
	Integrity: 25\\
	Firewall: 8 (may work for connected devices, if the attack passes through)\\
	Processing Power: +10}
    {50}
    {0,8}
\supply{Smart Fridge}{Barely anyone needs a fridge anymore. But those who do tend to pay extra for completely unnecessary features.\\
	Integrity: 5\\
	Firewall: 0\\
	Processing Power: -5}
    {333}
    {170}
\supply{Tablet}{A portable data processing device with a touch screen.\\
	Integrity: 7\\
	Firewall: 2\\
	Processing Power: +5}
    {23}
    {1,2}
\supply{Military Data Pad}{A tablet that's has 6 armor against both damage and EMP. Resilient enough for Joe to kick.\\
	Integrity: 8\\
	Firewall: 4\\
	Processing Power: +5}
    {35}
    {2,2}
\supply{Workstation}{A personal computer made to work found in many white collar office stalls.\\
	Integrity: 20\\
	Firewall: 4\\
	Processing Power: +10}
    {43}
    {8}
\end{multicols}

\pagebreak %quick fix
\subsection{Eyewear}
\vspace{5mm}
\begin{exampleblock}
	All eyewear also exists as armor mods (see \pageref{subsec:armormod}).
	They require 1 mod point in the helmet
	(thus obviously also requiring a helmet...),
	cost the same as standalone equipment,
	and don't require power.
\end{exampleblock}
\vspace{5mm}
\begin{multicols}{2}
\supply{Flash Glass Goggles}
    {Made from special glass, these goggles normalize incoming light.
        This removes all bright-light based penalties
        and makes the wearer immune to the Flash rule
        but the user is colorblind while under such effects.}
    {42}
    {0,45}
\supply{Infrared Goggles}{Goggles that give the ability to see in infrared, allowing to see heat signatures and infrared devices such as lasers.\\
	This gives the user a +15 bonus to oppose visual Stealth tests. Infrared Goggles also halve all penalties from darkness.}
    {32}
    {0,45}
\supply{Night Vision Goggles}
    {Grants \emph{Boon: Night Vision} but doubles all penalties to resist being blinded by bright light.}
    {18}
    {0,6}
\supply{Sun Glasses}
    {Pair of goggles that halve any penalties from bright lights
        but increases low-light penalties by 10 and darkness penalties by 20.}
    {2}
    {0,15}
\end{multicols}

\subsection{Hazards}
\vspace{10mm}
\begin{multicols}{2}
\supply{Parachute}
    {Standard issue parachute.
        Maneuvering uses \emph{Pilot: Air}
        but anyone can decent moderately safely using this.}
    {10}
    {9,5}
\supply{CBRN Unit}
    {A detector that gives information on chemicals and radioactive material in the vicinity,
	or any other airborne or grounded contaminant.
	}{12}
    {0,9}
\supply{Climbing Kit}
    {A climbing harness kit that, when worn, stops deep falls when failing to climb.
        Can hold up to 500kg of weight.}
    {37}
    {5,5}
\supply{Earplugs}
    {A set of top-grade earplugs that allow characters
        to ignore the hearing-based penalties given by flashbangs or other loud noises.\\
        Gives a -20 penalty to hearing-based Investigation and Perception tests.}
    {2}
    {0,004}
\supply{Explosives Detection Assistant}
    {A pioneer support device assisting in detecting known explosive compounds.
        Grants a +30 bonus to detecting and identifying explosives.}
    {24}
    {3,4}
\supply{Fire Extinguisher}
    {Puts out any fire using foamed dry chemicals. Has 10 uses.}
    {23}
    {15}
\supply{Metal Detector}
    {A metal detection unit that is a small metallic plate on an adjustable pole.
        The Metal Detector has a screen at the top of the pole
        that displays the types of metal found underneath,
        within 3 Meters underground,
        and how far underground the object is.}
    {9}
    {8}
\supply{Proximity Detonator}
    {An expensive proximity trigger mechanism.
        A specialist can rig most explosives with this trigger,
        causing it to go off when a human or vehicles passes
        1 to 3 meters depending on configuration.}
    {12}
    {0,25}
\supply{Remote Detonator}
    {A small hand-held device that can be synced up to various explosives.
        Has a range of 400 Meters.
        At the press of a button or an input of an up to 16 digit pass code,
        the chosen synced explosives will detonate.
        Can also be set to timed detonation.
        Often times the trigger is biocoded.}
    {5}
    {0,45}
\supply{Sound Filter Plugs}
    {Small speakers, a microphone array and an equalizer,
        in a small enough package to fit a person's ear.
        Ignore all hearing based-penalties.\\
        When broken down, infers a -30 to hearing based tests
        but still protects from loud sounds.}
    {18}
    {0,01}
\supply{Tripwire Kit}
    {A kit containing all necessary components to rig a grenade
        into an IED triggered by a tripwire.}
    {4}
    {0,7}
\end{multicols}

\subsection{Medical}
\vspace{10mm}
\begin{multicols}{2}
\supply{Field Surgery Kit}
    {A kit containing scalpels, syringes and other equipment to do basic field surgery
        like removing bullets or even remove augments from corpses provided the necessary expertise.\\
        Grants +10 to medical tests.}
    {34}
    {5,6}
\supply{Field Surgery Tent}
    {A very simple, packaged tent that can be used as a near sterile field surgery room.
        Does not protect from the elements much.\\
        Grants +10 to medical tests.}
    {35}
    {1,5}
\supply{Splint}
    {When applied this reduces penalties from cracked and broken bones to a quarter.}
    {3}
    {0,01}
\supply{Stitch Kit}
    {A more elaborate needle and thread that will close wounds for good.
        Takes a minute (20 combat rounds) and a Medication check +20 for light bleeding
        or two minutes and an unmodified Medication check for heavy bleeding.
        Generally cannot be applied by the bleeding character on his own.}
    {22}
    {0,6}
\supply{Thermal Blanket}
    {Prevents hypothermia or overheating.}
    {2}
    {0,9}
\supply{Wound Dressing}
    {Will stop bleeding when applied.
        Takes 6 seconds (2 combat rounds)
        but already stops the target from bleeding out when started.
        Cannot be applied by the bleeding character on his own.
        Comes in a pack of 20.}
    {5}
    {0,2}
\supply{Wound Sealant Foam}
    {Will stop bleeding.
        Takes about 12 seconds (4 combat rounds) to use,
        6 of which are the application,
        while the other 6 are hardening.
        Natural healing of the given zone is stopped until the foam is removed by a physician.
        Comes in packs of 5.}
    {16}
    {0,8}
\end{multicols}

\subsection{Navigation}
\vspace{10mm}
\begin{multicols}{2}
\supply{Compass}
    {A standard magnetic compass
        that is not effected by EMP or any other sort of digital or electrical attack.}
    {1}
    {0,2}
\supply{Roadware}
    {Weak AI based GPS-reading software that assists drivers at high speeds and off-roads.
        The unit gives a +20 Bonus to high-speed Drive tests.}
    {14}
    {4,8}
\end{multicols}

\subsection{Protection}
\vspace{10mm}
\begin{multicols}{2}
\supply{Balaclava}
    {Face mask for face protection from harsh winds or being identified.}
    {1}
    {0,3}
\supply{Clothing, Simple}
    {Simple clothing to blend into ghettos.}
    {6}
    {1,1}
\supply{Clothing, Gaudy}
    {Expensive \emph{looking} clothes of poor quality.
        Experts will notice but most other people will be impressed by the display of decadence.}
    {34}
    {2}
\supply{Clothing, Expensive}
    {Expensive clothing to blend into high society.}
    {140}
    {1,1}
\supply{Cover Foam Canister}
    {A cylindrical 2 liter canister holding pressurized, quick hardening foam.
        When primed and thrown the foam will escape and expand to roughly one cubic meter.
        Within a minute it will harden to something akin to shale rock and while it hardens it may be molded.
        It does not gain any mass, of course, only volume.}
    {28}
    {4,2}
\supply{Flotation Vest}
    {An adjustable flotation vest that allows an unarmored adult to drift above water.}
    {2}
    {1}
\supply{Gas Mask}
    {Allows to breathe in toxic environments.}
    {18}
    {1,1}
\supply{Gas Mask Filters}
    {A disposable filter to be used in gas masks.
        Lasts up to 24 hours.}
    {2}
    {0.1}
\supply{Ghillie Cloak}
    {The Ghillie Cloak offers a +20 Bonus to visual Stealth when used in believably matching surroundings.
        Otherwise the user suffers -20 instead.}
    {6}
    {2,4}
\supply{Handcuffs}
    {Used to bind an individual’s hands or ankles.
        To escape, a character must roll a -40 Sleight of Hand test or a -60 Strength test.
        Dealing 30 damage through 10 points of armor will break the cuffs.}
    {12}
    {0,5}
\supply{Rain Poncho}
    {Protects the user from rain.}
    {2}
    {0,8}
\supply{Rape Whistle}
    {A small, loud whistle. Reportedly used by some "special" forces alongside foam swords.}
    {1}
    {0,05}
\supply{Riot Shield}
    {The Anti-Ballistics Riot Shield acts as mobile cover for a character.
        It is made of durable polymer with a hardened window to see through.\\
        It covers normal-sized or smaller peoples' full bodies,
        while large people must crouch to cover their whole body.\\
        The riot shield functions like a piece of cover worth 22 armor points.
    	It is also a
    		\emph{One-Handed},
    		\emph{Improvised},
    		\emph{Protective}
    		blunt melee weapon
    		(using \emph{Striking}).
	}
    {28}
    {5,9}
\end{multicols}

\subsection{Software}
\vspace{10mm}
\begin{multicols}{2}
\supply{Security Measures}
    {Decreases a device's processing power by 10 but increases its firewall by 3.
        Can be deactivated if required for some reason.}
    {75}
    {-}
\end{multicols}

\subsection{Storage}
\vspace{10mm}
\begin{multicols}{2}
\supply{Ammunition Bandolier}
    {A bandolier that is worn over armor/clothing that can hold one of the following:
        \begin{itemize}
        \item 100 shotgun shells
		\item 150 rifle or pistol rounds
        \item 50 sniper rounds
        \item 10 Grenades, mass driver blocks, filled magazines, or 40mm Grenades
    	\end{itemize}
	}
    {7}
    {0,3}
\supply{Ammunition Pouch}
    {Ammunition pouch.
        Carries 8 magazines, grenades or anything of equivalent size.}
    {5}
    {0,35}
\supply{Blast-proof Clear Casing}
    {Blast-proof casing.
        Can hold up to 5 magazines, grenades or size equivalents
        but is generally used for portable electronic devices.
        Offers 18 points of cover that also blocks damage from the EMP special rule to devices on the inside.
        Damage from EMP cannot damage the case.}
    {21}
    {2,8}
\supply{Duffle Bag}
    {Soft bagged carrying device like a sports- or backpack.
        Carries 25 magazines, grenades or size equivalent.}
    {9}
    {2,9}
\supply{Ergonomic Weapon Holster}
    {Holds weapons in completely over-engineered ways.
        Time to draw is reduced by one action to a free action minimum.}
    {16}
    {0,35}
\supply{Hardcase/Tactical Hardcase}
    {An armored carrying device the size of
        a small backpack / lunchbox that can be placed virtually anywhere on the body.
        Capable of carrying up to 14/5 magazines, grenades, or anything of equivalent size.\\
        The hardcase has an armor rating of 10 protecting
        both itself and its content
        but can only take 30 damage before it's so broken down
        that it won't hold anything anymore.}
    {30/18}
    {1,2 / 0,7}
\supply{Softcase/Tactical Softcase}
    {Soft bagged carrying device the size of
        a small backpack / lunchbox that can be placed on virtually anywhere on the body.
        Carries 20/7 magazines or grenades, or anything of equivalent size.\\
        The softcase has no armor protecting itself or its content,
        and can take 25 damage before it's so broken down
        that it won't hold anything anymore.}
    {25/13}
    {0,9 / 0,5}
\supply{Thigh Rig}
    {Small, thigh-rigged casing.
        Carries 3 magazines or grenades, or anything of equivalent size.}
    {9}
    {0,2}
\supply{Weapon Holster}
    {Holds a small weapon.
        Legally bought or issued weapons are generally assumed to come with a proper holster.}
    {5}
    {0,3}
\supply{Weapon Sling}
    {Holds a larger weapon to keep the hands free.}
    {5}
    {0,4}
\end{multicols}

\subsection{Survival}
\vspace{10mm}
\begin{multicols}{2}
\supply{Area Heater}
    {A small heater that can heat an area powerful enough to keep a dome tent warm.}
    {24}
    {2,3}
\supply{Camping Stool}
    {A small folding stool.}
    {6}
    {1,5}
\supply{Fishing Kit}
    {A fishing kit that contains
        a folding fishing rod,
        ten hooks and bobbers,
        a spool of 50 meters of fishing line
        that can withstand up to 6 kg of tension,
        50 pieces of bait,
        a fishing net that can hold up to 6 kg of weight
        and a fitting hat.}
    {47}
    {5,8}
\supply{MRE / Nutrient solution}
    {Disgusting nutrient solution that never goes bad
        - or \textit{worse}, anyway... \\
        One tube is enough to sustain normal people for a day
        and one tube is government issued to all registered civilians each day.}
    {1}
    {0,3}
\supply{Multi-Tool Kit}
    {A briefcase sized kit of tools for repair and building.}
    {19}
    {8}
\supply{Portable Electricity Generator}
    {A portable generator that is capable of
        powering equipment and structures
        who either don't have their own or whose generators have broken down.}
    {42}
    {26}
\supply{Portable Food Stove}
    {A small stove that can prepare food.
        Since the advent of large scale nutrient solution supply
        this piece of equipment has become very rare.}
    {64}
    {3,5}
\supply{Prepared Meal}
    {A luxury only very few people choose to afford.
        Generally a waste of biomass
        and more of a decadent treat than survival equipment.}
    {120}{0,5}
\supply{Proper Meal Ingredients}
    {Expensive ingredients that have short shelf life,
        need the time, skill and installations to be cooked
        and don't always offer all nutrients a person needs
        but if prepared correctly can be a rare, tasty treat.}
    {34}
    {0,6}
\supply{Singles/Large/Dome Tent}
    {A weather resistant tent for one/five/ten people to fit in.}
    {8/22/40}
    {1,2 / 6 / 12}
\supply{Sleep Cot}
    {A small cot bed for a single person.}
    {12}
    {4,5}
\supply{Sleeping Bag}
    {A wind-proof sleeping bag.}
    {10}
    {1,2}
\supply{Survival Blanket}
    {A wind and water-proof blanket that uses a thermal lining
        to keep the user in a more livable temperature,
        closer to their body's.}
    {10}
    {1,1}
\supply{Water Canteen}
    {A leak-proof survival canteen with a lock top and 2-liter capacity.}
    {4}
    {0,6}
\supply{Water Purification System}
    {A portable water purification system, favored by wastelanders.
        It can process 1 liter of water every two hours.
        Must be cleaned after each use.}
    {32}
    {24}
\end{multicols}

\subsection{Tools}
\vspace{10mm}
\begin{multicols}{2}
\supply{Blowtorch}
    {A blowtorch that can be used in any atmosphere and underwater.
        This blowtorch is plasma based
        and will sear through basically any material,
        given enough time.\\
        For every 2 points of cover,
        it takes 1 action to cut through a small portion of of the material.}
    {18}
    {1,8}
\supply{Bolt Cutters}
    {Powerful bolt cutters.
        Strong enough to cut through all common metal sheets and locks.
        Pincers may need to be replaced after heavy duty as determined by the GM.}
    {12}
    {1,1}
\supply{Crowbar}
    {A proven tool from ages past.
        Grants a +30 bonus to strength based tests to pry open containers.}
    {8}
    {2,6}
\supply{Duct Tape}
    {A simple, strong water-proof tape.
        A thousand years don't change everything.}
    {1}
    {0,3}
\supply{Entrenching Tool}
    {A compact package functioning as
        a shovel,
        an axe
        or a crowbar.
        It is much more convenient than carrying three equipment pieces
        but does none quite as well as the the real thing:\\
	The crowbar end only grants +20 bonus.\\
	The axe head's damage is reduced by 3.\\
	Digging with the small shovel takes 10\% longer.}
    {25}
    {2,5}
\supply{Fire Starter}{Small dark-green cubes that when cracked open, begin to spark and get hot.
	After 8 seconds (3 rounds) it begins to burn.
	Works in wind and in rain.}
    {8}
    {0,1}
\supply{Gun Swivel}{A swivel arm that holds the gun.
	It reduces recoil but is rather cumbersome;
	it halves both sprint speed,
	as well as the \emph{Burst} penalty.
	It is not an exoskeleton and does not allow the use of heavier guns.}
    {42}
    {1,4}
\supply{Lighter}{A lighter with a flip-off top that is able to produce flame.
	Has enough fuel for 500 cigarettes.}
    {12}
    {0,1}
\supply{Omnidirectional Wave Emitter}
    {Small but heavy piece of hardware that generates and plays synthwave.
        It’s a fancy music box.}
    {12}
    {6}
\supply{Rope}
    {A sturdy carbon fiber rope. Just generally very useful.}
    {2 per meter}
    {4,2}
\supply{Shovel}
    {A simple shovel or spade for general purpose uses.
        Folds down to the size of the shovel’s head.
        Rust-proof, sturdy and reliable.}
    {7}
    {1,4}
\supply{SOS Knife Kit}
    {A multi-tool knife.
        Includes a variety of small blades and various other useful equipment
        that can be used in a pinch.
        It's not nearly as effective as a proper, dedicated toolbox.}
    {6}
    {0,2}
\supply{Weapon Cleaning Kit}
    {A kit that can be used to clean weapons and perform maintenance
        to remove any adverse penalties gained from the weapon being dirty.}
    {2}
    {0,7}
\end{multicols}

\subsection{Vision \& Detection}
\vspace{10mm}
\begin{multicols}{2}
\supply{Binoculars}
    {Simple electronic binoculars.
        Its magnification ranges from 2x to 20x.}
    {4}
    {0,8}
\supply{Chemical Light Sticks}{A chemical light stick is a bendable tube, that when bent, begins to glow.
	Gives a +10 in any dark scenarios.
	Lasts for an hour.
	Comes in packs of 5.}
    {12}
    {0,2}
\supply{Fiber Optic Probe}
    {A small camera on the end of a 4-meter wire.}
    {42}
    {0,6}
\supply{Flare Gun}
    {A small firearm that fires a 40mm Parachute Flare up to 150 meters}
    {30}
    {0,9}
\supply{Flashlight}
    {Helps to see in the dark.
        Lowers any low-light penalties by up to 30
        but makes it impossible to hide.}
    {5}
    {0,6}
\supply{Helmet Recorder}
    {Records every instance of what happens.
        Able to store 80 hours of higher quality footage.}
    {16}
    {0,4}
\supply{Signal Flare}{A bright flare that is activated by snapping the top off.
	Can be seen from about 2 KM away and lasts up to 1 hour.}
    {3}
    {0,35}
\supply{Spotter Target System}
    {A scoped spotting system that has multiple zoom variants.
        It includes various scopes and advanced ballistics simulation
        that allow a spotter to assist a sniper in extreme-ranged combat.}
    {25}
    {1,1}
\supply{Stationary Motion Tracker}{Scans movement of the environment up to 250 meters and sends it to tethered display devices. \\
    	Must be stationary for 1 minute (20 rounds) to calibrate and work.
        If moved, the Stationary Motion Tracker must be re-calibrated again.
        Until then data may be inaccurate at longer ranges.}
    {88}
    {29}
\end{multicols}
