\section{Chemical}
\label{sec:chems}

\subsection{Effects}
Every chem provides one or more benefits and detriments.
They last for a given time before the effects run out.
\\%
Kicking back multiple doses increases the effects.
After the given duration, only one dose runs out.
\par%
\begin{exampleblock}
	Mei hits 3 doses of liquid armor.
	For 3 hours she has 3D10 natural armor,
	her Ranged Base, Dex and Ag are reduced by 3D10,
	and she suffers an additional load of 6 MT.
	\\%
	After 3 hours the bonuses and penalties are reduced to 2D10 and the load to 4 MT, and so forth.
\end{exampleblock}
Like more permanent augmentation chems also put a load on the body, using the same metrics (RI and MT).
This load normalizes quickly once the effects subside.

\subsection{Risks}
\subsubsection*{Overdose}
Every chem produces load - just like implants
	- for the time of its effect.
A user who surpasses his RI or MT using chems,
	will risk long term side effects (see below).
\\%
A user surpassing his RI or MT by more than 2 suffers overdose effects
	of all chems currently active in his system.
Some chems may not have any - these are safe.
\subsubsection*{Long Term Side Effects}
When a user risks long term side effects,
	he rolls a D10.
If the result is
	less than or equal to
	his current RI or MT load
		(whichever one is higher and above his limit),
	that value will permanently be reduced by \emph{0.1}.
\\%
This effect can occur once for every dose of any chem he takes.

\subsection{Substances}
\luaimport{equipment/chems.csv}{chem.tpl}{augs/chem}
