\section{Philosophies}
%	TODO: add proper introduction
%	To understand the conflict about augmentation, one has to understand two standpoints.
\paragraph{Transhumanists} support augmentation of the human body. Science is a human aspect, evolution alone can only limit them. Extremists will try to exchange every part of their body with some form of cybernetic or biotechnological replacement even if only for vanity.\\
\paragraph{Body purists} believe that too many augments makes a person lose his humanity. Others fear that nerve load might be higher than initially expected, crippling some, driving others insane. The reliance on technology makes humans vulnerable to failure of even just one of those systems.
%	TODO: neither philosophy is
%	Body purism is no monolith; supporters might believe one or multiple of these things or even something else entirely.
\section{Cybernetics}
Cybernetic augmentation is widespread. Missing or deformed limbs are replaced or existing body parts enhanced to help with work or social life. They don’t naturally regenerate anymore, they are expensive and create a huge load on the patient’s nervous system, as indicated by Rayleigh index values. However they are generally more resilient than most human limbs and most of them offer additional special features. Obviously it takes very invasive surgery to install.
\section{Biotech}
Biotechnological engineering has come a long way and engineered body parts are rather common. Vat-grown clones of original human body parts or extra dexterous arms; slim, fine legs or extremely dense back muscle implants; whatever it may be, it falls into this category.\\
While assuring compatibility with the host's nervous system is easier, fitting it to the rest of a human host body is even harder to assure using this younger technology than it is with cybernetic implants, so biotech implants put a great amount of stress on the rest of the body, as indicated by medical toughness.
\section{Chemicals}
Chemical augmentation is a powerful way to enhance one’s abilities for a short period of time. It is common among thugs that cannot afford proper bionics but also among military and mercenary personnel that need to surpass human peak performance. Chemical augmentation comes with a temporary benefit and some sort of drawback when it runs out. Overuse and overdose can be harmless or extremely dangerous depending heavily on the substance at hand.