\documentclass[12pt,a4paper,openany]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Cosmic Horrors}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}
	
	\chapter{Introduction}
	Out there, in the void between the stars, there are things beyond comprehension, beyond reason. And the oldest and strongest emotion of mankind is fear, and the oldest and strongest kind of fear is fear of the unknown...
	%TODO: intro is very short, need to add a filler

	\chapter{Perils From Beyond}
	When the world beyond touches ours, mortals in the vicinity suffer - of three things specifically.
	\par
	\textbf{Insight} is the effect on the mind when someone tries to understand the dark beyond.
	It is usually temporary
		but so much out there will attempt to break your mind.
	\\
	\textbf{Corruption} is the effect on the body,
		setting in after extended exposure to the Dark
		or being watched by entities from beyond.
	\\
	\textbf{Powerful creatures} live beyond, attracted by strong emotion.
	%TODO: Horrors and Demons are not really distinguished in the bestiary
	First in line are the \emph{Demons} - wicked and malevolent beings from outside our perceived reality.
	\emph{Horrors}, on the other hand, only get their name due to their attraction to nightmares
		- concepts like malevolence do not apply to them.
	
	\section{Insight}
	\subsection{Gaining Insight}
	Characters gain Insight whenever they perceive horrors from beyond with any sense they were given naturally
		- i.e. hearing, seeing, smelling, tasting or touching.
	The feeling is generally unpleasant.
	\\
	Perceiving any creature with the DEMONIC tag will cause D5 Insight.
	Particularly powerful beings or groups may cause D10.
	\subsection{Reducing Insight}
	Characters may reduce their Insight by resting,
		secluded from such anomalies.
	It then reduces by 6 every day.
	\subsection{Effects of Insight}
	Every point of Insight reduces a character's Courage by 1.
	When Courage reaches 0 due to Insight,
		the character goes catatonic for at least a week and gains D10 corruption.
	After said week his Insight reduces back to 0,
		which often goes hand in hand with shallow memory loss,
		as the body sheds the remains of that experience.
	
	\section{Corruption}
	\subsection{Gaining Corruption}
	Corruption is gained when the dark powers try to enter a mortal body.
	\vspace{-8mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item In areas with a lot of presence characters gain up to 1 corruption per hour.
		\item Participating in or crashing rituals, which ask for some outer entity's favor, will cause D5 corruption.
	\end{itemize}
	\subsection{Reducing Corruption}
	Corruption is basically permanent.
	It reduces by 1 per 2 years without contact to the Eldritch.
	Considering that high corruption attracts them, this is very hard to do.
	\subsection{Effects of Corruption}
	A character can accrue up to 100 corruption, at which point he will transform
		- sometimes into an entity from Beyond,
		but much more likely into
		a puddle of goo on the floor
		or a pile of ash scattered in the winds.
		\\%
	While that transformation may be sudden and violent,
		the point of ascension is not reached subtly.
	His body will slowly mutate as corruption accumulates.
	Every full 10 points of corruption will cause a mutation (see Chapter \ref{ch:mutation}).
	
	\chapter{Mutation}
	\label{ch:mutation}
	Every now and then a character may be forced to mutate.
	Roll a D100, divide by 2 and consult the table below.
	The result may be modified by a tenth of the character's insight at the time of mutation.
	\begin{exampleblock}
		Most mutations are clearly visible and make social interactions much, much harder.
	\end{exampleblock}
	\begin{multicols}{2}
		\begin{enumerate}
			\setlength\itemsep{-10mm}
			\luaimport{components/mutations.csv}{mutation-tableentry.tpl}{muttable}
		\end{enumerate}
	\end{multicols}
	
	\section*{Mutations}
	\vspace{4mm}
	\begin{multicols}{2}
		\newcounter{mutations} %fixes hyperref links
		\luaimport{components/mutations.csv}{mutation.tpl}{mutations}
	\end{multicols}
	
	\chapter{Rituals}
	\label{ch:rituals}
	Rituals take a long time, are expensive and a lot of work to set up. They are however the prime way to ask the Great Ones for favor and protection in exchange for a tribute.
	\section{The Tribute}
	Great Ones respond well to unique things and strong emotions. The more personal to the participants this tribute is, the more likely the Great One will respond well - but nothing is guaranteed.
	\par
	\begin{center}
	\begin{tabular}{lr}
		\textbf{Live sacrifice} & \\
		Your lover or first born & +50 \\
		Your nemesis or rival & +30 \\
		A close family member or best friend & +20 \\
		A member of your species & +0 \\
		An animal & -10 \\
		\hline
		\textbf{Inanimate Objects} & \\
		A piece of fine craftsmanship & -10 \\
		Rare materials, valuables & -30 \\
		Dirt, literal dirt & -80
	\end{tabular}
	\end{center}
	\section{The Request}
	Their power is boundless and they offer many gifts. Almost everything may be requested but very few requests are actually fulfilled.
	\\
	The more selfish and direct the request, the higher the chances generally.
	Also, the more convoluted and needlessly complex and outright strange, the higher the chances generally.
	\\
	For many requests the leading character needs a very firm understanding of the infinite void and its inhabitants. 
	Some creatures may be very willing to fulfill even the strangest or most mundane requests
		- but if one does not know, who they are asking,
		the ritual may be doomed from the start.
	\par
	Examples of common requests include:
	\begin{sitemize}
		\item Learn about the Great Beyond, its inhabitants, its powers.
		\item Permanently meld minds with a willing participant to allow telepathic communication.
		\item Ask to mutate.
		\item Subjugate an unwilling participant.
		\item Summon a creature into real space or become possessed.
	\end{sitemize}
	\section{The Ritual}
	When preparation is done, the ritual then takes a few hours and a Philosophy test. The test may be modified by the tribute, potentially by the request and the leading character's Insight (one-to-one).
	\par
	During the performance of the ritual the participants will slowly unravel a small portion of the great Beyond, gaining them 2D10 Insight.\\
	If the ritual is successful, all participants are touched by untethered blasphemy, gaining D5 corruption.
	\section{The Outcome}
	A "successful" ritual does not necessarily mean the desired outcome. Instead the GM secretly rolls a D5 and consults the table below.\\
	For every 3 full DoS the ritual succeeded with, one option may be excluded by the leading character. If an excluded option is rolled, the leading character may choose the outcome instead.
	\par
	\vspace{-5mm}
	\begin{enumerate}
		\raggedright
		\setlength\itemsep{-8mm}
		\item The ritual succeeds without further incident.
		\item The ritual fizzles, nothing happens. Participants' corruption gain is reduced by 3, to a minimum of 0.
		\item The ritual succeeds. A demon attempts possession of the ritual leader.
		\item The ritual succeeds. A demon is summoned and manifests.
		\item The ritual succeeds. A random participant mutates (see p.\pageref{ch:mutation}), immediately and violently.
		The resulting mutation may not be adjusted using Insight.
		The leading character may have a higher chance to be chosen.
	\end{enumerate}
	\section{The Reward}
	If the ritual succeeds, the creature who answers will provide something close to the desired outcome - functionally the same.
	Depending on the specific creature, the effect may take a different shape however.
	\section{Examples}
	\input{components/examplerituals.tex}
	
	\chapter{Possession}
	\input{components/possessedcreatures.tex}
	\input{components/possessedweapons.tex}
	
	\chapter{Anomalies}
	\input{components/anomalies.tex}
	
	\chapter{Additional Content}
	\input{components/addcontent.tex}
	
	\chapter{Psionics Patch}
	When using both this and the Psionics Addon, you may want to use the following addendum to glue them together: 
	Insight increases the psionic target value one-to-one. However, the cost now not only deals damage to the caster but will also cause the same amount of corruption.\\
	By GM discretion some casters may use this new and some may use the old way of casting.
	
	\chapter{Credits}
	\input{components/credits.tex}
\end{document}
