\documentclass[12pt,a4paper,openany,usenames,dvipsnames]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Base Building}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}

	\chapter{Introduction}
	Any proper organization will require a base of operations to act from.
	These can take many different forms, shapes and sizes and fulfill many different roles.
	\par
	These rules are intended as guidelines to reduce bookkeeping and streamline function.
	Only use the parts that you believe will benefit your game.
	\par
	If you intend to have the base invaded, please also take note:
	These rules are mainly built for \emph{Theater of the Mind}, as they do not care for layout.
	You can however still use these rules as guidelines, e.g. when using \emph{Floor Plans or Battle Maps}.

	\chapter{Considerations}
	\vspace*{-10mm}
	Building a base means juggling the following 4 variables.\par
	\textbf{Size} is the total size at the location to be filled with assets.
		If Size is used up, no more facilities can be added.\par
	\textbf{Concealment} represents how suspicious the safe house is.
		If this is exhausted, the wrong people will know what purpose this location actually serves and it will be at risk.
		When actively trying to pass the location off as something else,
			the character gains a +5 per Concealment above 0 to relevant tests.\par
	\textbf{Defensibility} determines how easy the location is to defend.
		The simplified rules work as follows:\\
		For every Defensibility above 0 the defending party may reroll one of their tests during an assault,
			so long as any facility helps them achieve their goal.\\
		Likewise, for every Defensibility below 0,
			the attacking party may reroll one of their tests during an assault,
			exploiting security flaws.\par
	\textbf{Cost} - for rather obvious reasons.
		Money doesn't exactly grow on trees.
		Accessibility and social standing may greatly affect their prices.\par
	Theoretically \textbf{time} may be an important factor as well but it will be ignored from this point forward.
		Should you need to measure time, you will have to estimate.

	\chapter{Building}
	The first step to creating a safe house is to settle on a location.
	Locations range from a single room apartment,
		over trucks and boats,
		up to massive facilities like old military bases or entire cave systems.
	Each of them have different \emph{Costs}, \emph{Sizes},
		as well as basic \emph{Concealment} and \emph{Defensibility} values.\\
	Depending on the circumstances, the previous owners may also require advanced persuasion to give up their land.
	\par
	Then the free space may be used to build facilities and add assets.
	A selection can be found in the section below.\\
	\begin{exampleblock}
			Said list, as per usual, is not exhaustive.
			Feel free to offer your players additional options beyond the ones given.
	\end{exampleblock}

	\chapter{Components}
	\section{Special Rules} \vspace{8mm}
	\begin{multicols}{2}
	\specialrule{Harsh}{Technology is under stress here and has a constant risk of breaking down. Before an engagement at the base roll a D100 for every technological asset. On a 96+ the asset is unavailable and needs to be repaired.}
	\specialrule{Leftovers}{Some core components are left from the previous owner which makes it much easier to build certain facilities, halving the price of said facility.}
	\specialrule{Mobile}{The base can be moved to different places, making it possible to bring the base to a mission or avoid dangers.}
	\end{multicols}

	\section{Locations} \vspace{5mm}
	\begin{multicols}{2}
	\baselocation{Wasteland}{150}{12}{4}{2}{Harsh}
	\baselocation{Inner City Apartment}{480}{2}{2}{-1}{R\&R included by default}
	\baselocation{Truck / Boat}{480}{1}{2}{0}{Mobile}
	\baselocation{Nomad Camp}{1,300}{6}{3}{-1}{Mobile}
	\baselocation{Underground}{11,500}{6}{8}{2}{Harsh}
	\baselocation{Old Warehouse / Factory}{13,000}{4}{2}{1}{Leftovers (Forge or any storage)}
	\baselocation{Old Military Base}{22,000}{12}{0}{3}{Leftovers (Defense)}
	\end{multicols}

	\section{Facilities/Assets}
	\vspace{5mm}
	\begin{multicols}{2}
	\subsection{Basic}
	\vspace{-2mm}
	\baseasset{Extension / Additional Story}{Increases size capacity by 4.
		It may be built multiple times but generally at most double the starting base size.
		Its cost is similarly limited to be the location's original cost at most.
		}{-}{-2}{-1}{5,000}

	\subsection{Concealment}
	\vspace{-2mm}
%	\begin{multicols}{2}
	\baseasset{Facade}{Increase concealment by masking the base's true purpose.}{2}{2}{0}{300}
	\end{multicols}

	\subsection{Crafting} \vspace{5mm}
	\begin{multicols}{2}
	\baseasset{Fabrication Plant}{Produces a certain type of synthetic components automatically. Produces a net value of roughly cR 100 daily, given it is continuously supplied.}{4}{-1}{-2}{160,000}
	\baseasset{Forge}{Enables Forge crafting. The Size and Cost depends on the forge's size.}{1 / 2 / 4}{-2}{-2}{120 / 1,600 / 13,800}
	\baseasset{Lab}{Enables Chemical crafting. The Size and Cost depends on the lab's size.}{1 / 2 / 4}{-2}{-2}{120 / 1,600 / 13,800}
	\baseasset{Plantation}{Produces a certain type of natural components automatically. Produces a net value of roughly cR 100 daily, given it is continuously supplied.}{4}{-1}{-2}{160,000}
	\baseasset{Vehicle Bay}{Enables Vehicle repairs and modification.}{4}{-2}{-1}{860}
	\end{multicols}

	\subsection{Defense} \vspace{5mm}
	\begin{multicols}{2}
	\baseasset{EMI Dynamo}{Allows EM pulses in defense situations.}{1}{-3}{+1}{2,800}
	\baseasset{Life Support Systems}{Removes dependency on the outside world for clean water, food and air.}{1}{-1}{+1}{400 per location's Size point}
	\baseasset{Hidden Pathways}{Allows circling around or escaping from the enemy in defense situations.}{0}{0}{+1}{320}
	\baseasset{Surveillance System}{Prevents being infiltrated.}{1}{-1}{+1}{2,600}
	\baseasset{Turret Grid}{Adds allied turrets in defense situations.}{1}{-3}{+2}{3,800}
	\end{multicols}

	\subsection{Preparation} \vspace{5mm}
	\begin{multicols}{2}
	\baseasset{Comms Network}{Allows safe communication during preparation, internally and externally. Anyone trying to break encryption takes an additional -20 penalty.}{1}{0}{+1}{1,250}
	\baseasset{Data Center}{Allows advanced data mining.}{1}{-1}{-1}{750}
	\baseasset{Equipment Stash}{Allows safe storage of various types of equipment.}{2}{0}{+1}{40}
	\baseasset{Hidden Stash}{Allows safe storage of items that won't easily be found by a search.}{0}{0}{+1}{80}
	\baseasset{Holding Facility}{Allows safe storage of prisoners and people of interest; 2 cells each.}{1}{-2}{-1}{400}
	\baseasset{Living Quarters / R\&R}{Improves recovery through relaxation. All natural healing tests gain +10 and recovery time is reduced by half.}{1}{+2}{-1}{100}
	\baseasset{Medical Facilities}{Increases regeneration of health. All medical attention tests to regenerate HP gain +10.}{1}{-1}{-1}{900}
	\baseasset{MedEvac / ER}{If during a mission a character is mortally wounded, he may be extracted and survive the encounter. He will however be traumatized and gain a Bane worth roughly 4 GP.}{4}{-3}{+1}{4,600}
	\baseasset{Aug Surgery}{Allows implantation surgery.}{2}{-2}{-1}{1,600}
	\end{multicols}

\end{document}
