\def\pfcname{Doc Jones}
\subsection{\pfcname}
\subsubsection{Basic Questions}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item I'm a scientist and I wear it on my sleeve. Because I'm only biologically 22, I had to dye my hair gray and my beard white, and I comb my hair up so onlookers would immediately understand my brilliance.
	\item I've been called mad scientist, which of course is preposterous. Curious and engaged perhaps, but I digress.
	\item I was grown and educated in a vat. They say I didn't come out right but I'll show 'em... I'll show 'em all!
	\item I... never really saw people outside the corp. And most patients didn't make it.
		\\%
		As for people currently - I met Wire, when she looked for more supplies.
		And I met the Pack Man when I was looking for supplies myself.
	\item This is the best way to make a name for myself. Also, they need my help.
	\item My lab and the ER, really nothing past it. I DID however visit a lecture hall once!
	\item Very useful, very useful indeed. Considering I was purpose-made in the first place, why would I not aug every part I can?
	\item Makes you work longer and more efficient. But my opinion as a medical professional should be clear, right?
	\item No, no, no. The medic dies last, that's just common sense.
	\item I'd love to have my own lab. Like, my \textit{own} own.
	\item I have a bad feeling about Golotov. He wouldn't just let me go, that's not the type of man he is. He probably has some control mechanism left in place and the feeling won't let me go.
	\item Yes, yes, it's always about morals. But what are morals really if not your upbringing imprinting on your mind? So I'm not evil - I'm just different and your argument is invalid.
	\item Strangers usually want something from me. At best I will be professional, at worst dismissive. Depends on how much cash they bring.
	\item I swore an oath to preserve... \textit{however} there is a lot to be learned people suffering and dying and who would let that go to waste?
	\item I love animals. They are premium test subjects.
	\item Beauty is such a strange concept, so superficial. So let's say health to get it over with.
	\item Only the most elegant. Like... hot dogs and cheap wine. Or tap water.
	\item I- I'm not good with these flowery mumbo jumbo. It's just a nice feeling.
	\item I've grown up in a vat. What do you think? I didn't have the time for a dark secret.
	\item I'm a proud medical scientist, a bit too invested into surgery. I'm also born to be compliant and don't like spending money.
\end{enumerate}

\luaimport{prefabs/prefab-stats-\pfcname.csvin}{prefabchar.tpl}{\pfcname}
