\def\pfcname{The Pack Man}
\subsection{\pfcname}
\subsubsection{Basic Questions}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item I'm a small guy. Chinese decent. Short dark hair. Really hate fluttering coats, prefer something tighter.
	\item Usually I like not to leave an impression. Most people would probably call me shady.
	\item Grew up in the city sprawl. Liked climbing, mainly into abandoned buildings. Never got caught.
	\item Had to break most ties. Would like to see some of my old gang again. Maybe some day. The one tie I would like to break but can't is to "Rust" Golotov. Owe him a whole bunch of dough.
	\item Stellar people. They make up for the little things I'm missing. Ideal support.
	\item Didn't come around much. Saw my fair share of the city though.
	\item Love myself some chrome. Too expensive though and stolen goods don't scratch that itch.
	\item Took a bunch when I was younger. Trying to stay clean now, shit breaks you.
	\item This is where I'd say I love my life. But time again I almost kick it just for the rush.
	\item Would love to pay off my debt one day, leave my past behind.
	\item Golotov will poison me one day, I just know it. Or murk me in my sleep. Can't run, can't hide. Really got me by the balls.
	\item I'm flexible. Gotta do what it takes to do the right thing.
	\item Can't be too careful or you get bitten. Takes a while to earn my trust.
	\item You take it as easy as you give it. What's the big deal?
	\item Annoying things. They see you, they smell you - they make my job that much harder.
	\item I mean... girls? Tech'd up. Proud.... kinda like Wire.
	\item Anything works, really. But I still like my booze.
	\item I just know it ends in the morning.
	\item People like me don't live through dark secrets.
	\item A bit secretive perhaps. Careful with people, but not myself cuz I don't have to be.
\end{enumerate}

\luaimport{prefabs/prefab-stats-\pfcname.csv}{prefabchar.tpl}
