\def\pfcname{Wire}
\subsection{\pfcname}
\subsubsection{Basic Questions}
\begin{enumerate}
	\setlength\itemsep{-8mm}
	\item Well... guess you'd call me a cat girl. The small ears, soft and light hair, the tail. I have very light skin, pronouncing the permanent rings under my eyes.
	\item People will probably think me a common girl who can't really think ahead. You know... the cat parts and all.
	\item I grew up in the middle of the city. Went to a tech collage, got myself some good side gigs but... on one job I got blown up. Still don't know where the blast came from. I just know that I needed most of my cash to pay for fix ups.
	\item Well, yeah. 2 of them in fact - Doc and CJ. I've worked with them before and I will again for as long as I can.
	\item Doc Jones patched be back together when... you know... anyway, CJ has my back now and I finally feel safe. I can't really read that courier guy but he seems decently chill when it's just us.
	\item I've seen... server rooms? Very little to actually talk about. I saw as many places as security measures.
	\item Gotta love my new parts. I don't like chrome for the augs' sake. But the things I got are just amazing.
	\item They have great effect, could kick it all day... and sometimes I do... I just work better that way, okay?
	\item I wouldn't risk my life willingly, however... sometimes I don't think to the very end, when my curiosity gets the better of me.
	\item I wanna break into a mega-corp for no reason other than to see what's going on in there. Just to prove I can.
	\item The unknown depths below. I hate deep, dark holes.
	\item I don't want to hurt anyone! But, you know, sometimes people are bad and leave you with no choice. Better be safe than sorry.
	\item I like meeting new people, seeing new ways. Each brings some different tragedy.
	\item Again, I don't want to hurt anyone. I prefer not getting into conflict in the first place. If I have to, I want to cause as little damage as necessary.
	\item Pets are cute but anything else is either disgusting or dangerous.
	\item I like machines. I like things with purpose. Also, brains in a guy are neat.
	\item Energy drinks and crystal for breakfast.
	\item It's like trying to decrypt complex code and all you got is a rain-soaked circuit board. But it's the most pleasant glitch I know.
	\item I don't work right without my juice, you know? I don't like it but I sure as hell won't change it.
	\item I'm a smart but physically weak body modder. Knowledge is power and I want it all.
\end{enumerate}

\luaimport{prefabs/prefab-stats-\pfcname.csv}{prefabchar.tpl}
