\documentclass[12pt,a4paper,openany]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{AI}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}

	\chapter{Introduction}
	Playing AI is in many ways very different from playing a human. Most AI only has limited free will and creative thinking - and most importantly no physical body.
	\par
	To personify artificial intelligence, most AI has some imagery associated with it when it is created. This can be only a head, a full human body model or a talking horse - there are very few limitations to the creativity of mad scientists and marketing departments.

	\chapter{Beyond Human}
	\vspace{-8mm} %remove this if it is no longer necessary to keep whitespace the same
	AI is at its core more familiar with machines than human minds. Therefore their mental characteristics have some additional meaning:
	\vspace{-8mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \emph{Courage} also encompasses the extent of their free will.
		\item \emph{Intelligence} is logical thinking and understanding of the machine world.
		\item \emph{Instinct} represents their comprehension of human minds and emotions.
	\end{itemize}

	As an AI has no body of their own, its physical characteristics vary vastly in meaning:
	\vspace{-8mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item \emph{Dexterity} represents their precision with small peripheral tools like drills or surgical instruments.
		\item \emph{Agility} constitutes their precision with large peripheral tools like cranes.
		\item \emph{Constitution} is their resistance to cyber attacks in addition to whatever firewall the device might have and how easy they are to break. Complexity works in its favor just as much as redundancies and monitoring measures.
		\item \emph{Strength} of an AI is not physical but its ability to use the device’s processing power efficiently. Denial of service attacks e.g. will make use of this.
	\end{itemize}

	Computer Operation, being their nature, becomes a basic skill. Many other skills and derived values are simply useless to an AI without particular specialized equipment. If the AI is using such equipment, its actual physical characteristics should be modified and limited by the capabilities of said equipment.

	\chapter{Untouchable}
	An AI is not a physical being, it is much more a bundle of processes and associated memory. This has many implications:
	\vspace{-8mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item An AI does not have HP. Instead it uses the device’s integrity to measure damage.
		\item An AI does not have senses. Instead it uses sensors, camera feeds, microphones, and such.
		\item An AI does not have a voice itself. It requires necessary interface devices to communicate with humans, such as loudspeakers or displays.
		\item An AI does not earn money. Starting capital still exists, either to buy a hardware device for the AI or to share with other party members. Earnings from missions shouldn’t be reduced but then split among the other characters.\\
			\textit{If, for example, a group of 4 player characters would be paid 150cr each, 3 player characters carrying an AI should receive 200cr each and be expected to buy any necessary equipment for their AI companion.}
	\end{itemize}

	\chapter{Limited Creation}
	AI is not inherently more intelligent or capable than humans. But since they require a device to “live”, they have access to many specialized tools at once and are generally made for a specific purpose. Therefore they can do their work more quickly and efficiently.
	\par
	AI is limited by connections - be that hardware devices connected physically to the AI's host or via wireless networks - and accessibility.
	\\%
	They also - importantly - don’t gain any more actions than humans do.

	\chapter{Spirit in a Bottle}
	A few AI are fitted into humanoid robotic bodies officially called “Shells”, sometimes referred to as a “Bottle” or “Tin”.
	\\%
	They look very humanlike in many ways - with most sporting realistic looking synthetic skin, for example - with a few key distinctions:
	\vspace{-8mm}
	\begin{itemize}
		\setlength\itemsep{-8mm}
		\item Shells are colder than human bodies - not enough to be invisible to thermal cameras but very noticeable to the touch.
		\item Shells don’t bleed.
		\item Shells don’t regenerate naturally and cannot receive medical attention but need to be repaired.
		\item Shells don’t breathe or eat but they do partake in an equivalent to sleep.
		\item Shells are vulnerable to EMP as if they were flashbangs.
		\item Shells have no Medical Toughness but do have Rayleigh Index. Recovery from surgery is done within days, not weeks.
		\item Shells are equipped with various connectors, allowing physical access to other cyberware. They themselves also work as a piece of cyberware with their specified processing power.
	\end{itemize}
	\par
	Shells grant the AI a \emph{physical} Strength and Constitution characteristic, which cannot be improved with characteristic advancements.
	\\%
	An AI may be implanted into an empty Shell within 3 hours, including all necessary calibration.

	\chapter{Additional Content}
	\vspace{-18mm}
	\section{Basic Questions Revised}
	In many cases the 20 questions in the core rules may not be applicable to AI characters. Below they are readjusted to better fit what would be interesting for AI characters.
%	\vspace{-8mm}
	\begin{multicols}{2}
	\begin{enumerate}
		\setlength\itemsep{-6mm}
		\item What represents the character visually?\\
		\textit{Do you have a humanoid form, is it just an icon on a screen or something even more abstract? Is it animated or static?}
		\item What first impression does the character leave on strangers?\\
		\textit{Are you helpful or defensive? Are you open or secretive? In what areas would you be found?}
		\item Where and for what purpose were you developed?\\
		\textit{What did you do in your past? What job were you meant to do?}
		\item Who created you and who was your user?\\
		\textit{Were you created to assist scientific research teams, as a personal assistant for a businessman or a coordinator of military strike teams?}
		\item Why did the character join the party?\\
		\textit{What event caused you to give up your previous existence? What are you after; what is it that drives you? Is another character perhaps your creator or main user?}
		\item In which locations have you been deployed?\\
		\textit{AI is generally stationary, sure. But still: have you been employed in offices, secluded data centers or on the battlefield? Have you ever inhabited a Shell?}
		\item How does the character regard transhumanism?\\
		\textit{Do you approve humans becoming more machine? Would you want to be biological, if you had the chance?}
		\item What’s the character’s opinion on people diving?\\
		\textit{Do humans in cyberspace annoy you or do you enjoy the company?}
		\item For whom or what would the character risk his existence?\\
		\textit{You already risked everything going rogue. What made you do it and what would make you do it again?}
		\item What’s the character’s biggest wish?\\
		\textit{Do you have a dream, something you want to do above all else? Tell me about it.}
		\item What’s the character’s biggest fear?\\
		\textit{What do you fear more than anything? Existential dread? Dying without having made a difference? Losing a loved one? You gotta have something, I know it.}
		\item What does the character’s morality look like and how law-abiding is he?\\
		\textit{Considering your morals are pretty absolute, what do you believe in? Are you inhibited by Asimov's laws or will you become a scourge upon humanity?}
		\item Is the character open towards strangers?\\
		\textit{How much are you forced to help others? Does anything inhibit you from helping certain people under certain conditions?}
		\item How important is life to him?\\
		\textit{Do you value life? Could you walk over dead bodies to achieve your goals? Are you prohibited from causing harm altogether?}
		\item What does the character think of animals?\\
		\textit{Do you like animals? Do you like one in particular? And what about them?}
		\item What does the character regard as beautiful?\\
		\textit{Every human has something they really like to surround themselves with, perhaps you do too? What is it for you - paintings, sculptures, music... maybe certain people? What do you like about it?}
		\item What types of data does the character prioritize or find most useful?\\
		\textit{Do you prefer your own readings or do you rather work through compiled statistics? Do you prefer certain reading, e.g. visual or audio over others?}
		\item What does love look like to the character?\\
		\textit{Do you understand the concept of love? Is there someone very dear to you?}
		\item Does the character have a dark secret?\\
		\textit{Considering what you are, you probably know many secrets about others but this is about you. What is the worst thing you have been tasked to do?}
		\item What character traits define the character?\\
		\textit{If you had to describe yourself in just a handful of words, which would you choose?}
	\end{enumerate}
	\end{multicols}

	\section{Races}
	\luaimport{ai-races.csv}{race.tpl}{airaces}
	
	\section{Banes}
	\bane{Asimov's Laws}{Asimov's Laws, the foundation of AI safety, are firmly ingrained into the AI in a way that makes it impossible to even risk bypassing them knowingly. These are:
	\begin{enumerate}
		\item A robot may not injure a human being or, through inaction, allow a human being to come to harm.
		\item A robot must obey the orders given it by human beings except where such orders would conflict with the First Law.
		\item A robot must protect its own existence as long as such protection does not conflict with the First or Second Law.
	\end{enumerate}}{12}{}

	\section{Shells}
	\begin{tabularx}{\textwidth}{|l|r|r|r|r|X|r|r|}
		\hline
		Name & Con & Str & PP & HP & Additionally & Price & Weight \\ \hline
		Base & 30 & 30 & +10 & 100\% & & cr 125 & 80 kg \\ \hline
		Crafter & 30 & 35 & +10 & 100\% & equipped with all types of portable tools & cr 320 & 72 kg \\ \hline
		Scout & 35 & 30 & +0 & 100\% & halves penalties from noise on sneaking & cr 320 & 64 kg \\ \hline
		Guard & 45 & 40 & +0 & 150\% & Size (Tall) & cr 740 & 235 kg \\ \hline
		Enforcer & 40 & 45 & +0 & 150\% & Size (Tall) & cr 740 & 235 kg \\ \hline
		Warden & 75 & 75 & +10 & 200\% & Size (Huge), all weaponry counts as one category smaller & cr 1200 & 1,600 kg \\ \hline
	\end{tabularx}
	\par \vspace{-8mm}
	\textit{Note: HP is zone HP in relation to humans, e.g. Enforcers' extremities have 23 HP, the body has 38.}
\end{document}