\documentclass[12pt,a4paper,openany]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Mission} %TODO: name

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}
	
	\chapter{GM Notes}
		The following mission is split into acts focusing on different aspects of the game -
		A short GM notice in the beginning will tell you exactly what that is.
		\\
		Doing one thing after the other may feel contrived but helps to learn the game mechanics.
		\\
		Those parts are also meant to last for about 4 hours of play. Feel free to use them as parts of your own missions.
	
	\chapter{Introduction}
	\section{Summary}
		\texttt{A corp is liquidated out of the blue. A strict curfew is passed and economy slows down. A bunch of goons start a street war with the Millicents. Rain on Thursday.}
		\par
		Our protagonists return from a job, relaxing in their safe house. Their door is breached and they manage to barely escape. They are then chased as they look for refuge in the deeper, darker parts of the city's heart.
		\par
		
	\section{Player Characters}
		This mission was created with the archetype characters in mind.
		In case the player want to create their own characters, make sure the following conditions are met.
		\par
		All player characters know each other and have worked with each other before. They are also willing to work together again.
		\par
		At the start of this mission they share a safe house - this may be permanently or just for a few hours.
		\par
		They also have all - individually or collectively - worked with Gol-Tech on one or more dirty jobs before. \\
		\emph{This was on such a matter that Golotov will view them as loose ends that need tying up.}
	
	\section{NPCs}
		\subsection{Roswald "Rust" Golotov}
		\textbf{CEO of Gol-Tech.}
		He is a ruthless man, like most business men. In his past he has passed many efficient but unethical tasks to less than reputable figures - allegedly, as this is something the law could never prove to this point.
	
	\chapter{Act I: The Beginning}
	\textit{Focus lies on movement, exploration and stealth.}
	\par
	
%	player characters hang out in a safehouse, watching the news
%	news reporter: "Gol-Tech, Incorporated has been disbanded. After an undisclosed incident the once biggest manufacturer of cybernetics in the country has been liquidated yesterday. We will release more details as they become known."
%	shortly after a big group of goons walks up and breaches the door
%	group may react by fleeing through the window or fortifying
%	> chase %TODO: needs map
%	> fortify %TODO: needs map
%	regardless whether they stood and fought or fled, they will not stay at the safehouse for fear of reinforcements %TODO: what happens when a goon is captured
	
\end{document}