\documentclass[12pt,a4paper,openany]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Neon Nexus}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}
	
	\chapter{GM Briefing}
	\section{Mission Summary}
	An entry level mission split into three acts.
	\par
		\hyperref[ch:act1]{Act I} focuses on social interaction.\\
		The party is tasked with gathering information on a new prototype brain implant codenamed \emph{Project Starstruck} built by controversial developer OmniTech.
		That means talking to the right people and possibly breaking into corpo buildings
		- all the while staying unnoticed for as long as possible.
	\par
		In \hyperref[ch:act2]{Act II} the focus lies primarily on exploration, movement and stealth.\\
		Armed with the information obtained in Act 1 the players need to execute a daring data heist to access OmniTech's secure servers and uncover the true purpose of Project Quantum.
	\par
		Lastly \hyperref[ch:act3]{Act III} forces the players to make difficult decisions.\\
		Starstruck is nothing but a control mechanism
		- yet perhaps control and an escape is exactly what the people might need.
		Will the party choose freedom, the status quo or personal gain?
	\section{Player Characters}
	It is built for the core rule prefab characters but any group of player characters may work.
	Just make sure that the party is decently diverse in skills and all characters are willing to work together.
	
	\chapter{Act I: Shadows of the Megacorp}
	\label{ch:act1}
%	TODO: exploration; movement, stealth
%	characters are contacted (by who?)
%	party gathers info on OmniTech and Project Starstruck
	
	\chapter{Act II: The Data Heist}
	\label{ch:act2}
%	TODO: social interaction
%	party breaks into OmniTech data center
%	hacker steals data
%	rest protects hacker
%	party escapes
	
	\chapter{Act III: City of Revolt}
	\label{ch:act3}
%	TODO: combat
%	party decides what to do with the data
%	- original contractor pays tons of money, will use Starstruck to control population
%	- return to OmniTech, will release into the free market for people to choose
%	- approach a competitor, potentially get a fat cut
%	- publish the story, ruin OmniTech
	
	\chapter{Index}
	\section{Named NPCs}
	\section{NPC Bestiary}
	\section{Location}
	
\end{document}

%Starstruck is an implant inspired by Rimworld's joywire:
%Make people happy, make people obedient.
