\documentclass[12pt,a4paper,openany,usenames,dvipsnames]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Crafting}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}

	\chapter{Introduction}
	Crafting comes up again and again, so it may need some rules. We will follow the steps below to go from nothing to a completed item.\\
	First we prepare the blueprint and tooling, then we gather the necessary materials, and finally assemble the piece.
	\par
	\begin{exampleblock}
		The rules on the following pages go pretty in depth,
		are rather heavy on mechanics and very "numbery".
		It is only advised to use them if that is desired for one reason or another.
		Don't add them just to make creating objects more tedious
			and only use them if there is a consequence to failure.
	\end{exampleblock}

	\chapter{Preparation}
	Two things are required to create a more complex object: a blueprint and the required tools.
	A blueprint can be something as simple as a drawing or something as elaborate as binary information only comprehensible by specialized AI. Blueprints have qualities ranging from 0 to 10, granting a bonus to the subsequent crafting test equal to 3 times its quality. Two-dimensional blueprints are limited to quality 4.\\
	Buying a blueprint costs roughly \fbox{$(2Q+6)/20 * P$},
		where Q is the blueprint’s quality and P is the market price of the end product.
	(If an alternative simpler formula is required, use \fbox{$Q*P/7$}.)\par
	Skilled craftsmen can create their own blueprints. The character makes an intelligence based test on his crafting skill. The test is at a penalty depending on the required tool grade given below (Grade 1=+10, Grade 2=+0, Grade 3=-10…). The quality is the DoS, limited to 10. If the character doesn’t have the required materials at his disposal, the penalty is doubled, at least to -15.\par
	Second step of preparation is tools.
	There are two groups of tools
		- laboratories for biological or chemical and workshops for mechanical crafting,
		structured into different grades of tools:
	\par
	\begin{tabularx}{\columnwidth}{r|XX}
		Grade & Laboratory & Workshop \\
		\hline
		I & None or improvised & None or improvised \\
		II & Campfire & Multitool kit \\
		III & Kitchen & Garage \\
		IV & Distillery & Smithy \\
		V & Industrial Lab & Industrial Forge
	\end{tabularx}
	\par
	Creating an object with tools two grades lower than required is completely impossible as the necessary specialized tools are simply missing. A single grade lower is possible, though it infers a -20 penalty. A grade above the required tools grants +10 bonus, while two grades above grant +30 bonus and halve the required time. Any more than that will grant no more benefits as the construction is so simple that the powerful tooling is simply not applicable.\\
	Objects’ tool requirements are largely up to GM discretion, though a list of examples is given below:
	\begin{sitemize}[8]
		\item \textbf{External firearm mods} require \emph{tool grade I}.
		\item If something has the \textbf{Improvised} rule, it requires \emph{tool grade II}.
		\item \textbf{Bows, crossbows, non-powered armor} and \textbf{natural drugs} require \emph{tool grade III}.
		\item \textbf{Synthetic drugs, powered armor, PES, firearms} and \textbf{firearm core mods} require \emph{tool grade IV}.
		\item \textbf{Strike Suits and implants} require \emph{tool grade V}.
		\hrule
		\item \textbf{Repairing} requires \emph{one tool grade lower} than creating anew.
		\item \textbf{Ammo} requires \emph{one tool grade lower} than the weapon.
	\end{sitemize}

	\chapter{Material acquisition}
	Acquiring materials without really good connections or your own production facilities needs two things: money and time.\\
	To buy materials, the character collects a point pool of 25 DoS through \emph{Commerce} checks.
	Every successful check adds points into the pool equal to its DoS.
	Every check, successful or not,
		takes at least 4 hours to usually one day,
		and costs 5\% of the finished item’s listed cost.\\
	Markets can be limited; depending where the character is, multiple checks in the same area and general time may be limited or completely prohibited as per GM discretion. \par
	Alternatively - when materials are of simple, natural origin - the character may gather instead of buy them.
	Again the character needs to collect a point pool of 25,
		but instead uses Survival while in a suitable environment.
	Every check takes 4 hours and causes 1D5 exhaustion.\\
	Nature is usually limited; depending where the character is, multiple checks in the same area should be limited or prohibited per GM discretion.
	\par
	When looking for repair parts rather than a complete set,
	the point pool should be reduced to the damage parts.
	\begin{exampleblock}
		When looking to repair a set of EOD body armor
		that has two damaged arms (2 of 3 locations),
		the point pool would be 17 ($25 / 3 * 2 = 16.\overline{6} \approx 17$).
	\end{exampleblock}

	\chapter{Processing}
	\vspace{-10mm}%quickfix, otherwise there's one line on the last page
	Finally the actual crafting process begins.
	The character makes a Dexterity-based test against his crafting skill at a given penalty.
	Every test takes one day of work.
	Every successful test collects points equal to its DoS.
	Critical successes add at least half of the initially required DoS.
	\\%
	When a given pool size is reached, work is finished.\par
	The penalty to the crafting test and size of the point pool vary greatly depending on the object that’s being created. The table below shows the formulas for penalty first and point pool second:
	\par
	\begin{tabularx}{\columnwidth}{X|ll}
		Category & Penalty & Pool Size \\ \hline
		Weapons & 4 * damage dice & flat DMG + half AP \\
		Ammo & price per bullet & 10 * unit of sale \\
		Armor & 3 * Mod points (+15 if powered) & 2 * avg armor \\
		PES & 2 * dmg threshold & 2 * armor \\
%		Chemicals & 3 * duration in hours & price (per dosage) \\ %TODO: add after chemical rework
		Augments & 6 * (original RI+MT) & price (after mods) / 10 \\
		Misc & - & price / 5
	\end{tabularx}\par
	Lastly, failure can have debilitating effects.
	A slight mishap up to 2 degrees of failure simply wastes the day.
	Failing by 3 or more degrees removes D10 points that have been collected previously from the pool.
	Severe mistakes - or just many of them - of 5 degrees of failure or by simply falling below 0 points in the pool cause half of the material to be lost, e.g. as clippings or filings.
	Failing critically causes loss of all material in as spectacular a fashion as befitting of the character, tools and the materials were lost.
\end{document}
