\documentclass[12pt,a4paper,openany,usenames,dvipsnames]{book}
\input{../core-rulebook/config/news.tex}
\input{../core-rulebook/config/packages.tex}

\def\subtitle{Armor of Fate}

\begin{document}
	\input{../core-rulebook/config/frontpages.tex}
	%TODO: cover image is ugly

	\chapter{Introduction}
	Neon is a very lethal game. Since we don't want our protagonists to die to a stray bullet, they may need to be protected by fate themselves. 
	This may be represented by luck, unnatural determination and willpower or supernatural intervention as per GM discretion and game world.

	\chapter{Mechanics}
	\section{Resource}
	At character creation every player character gains \emph{Resilience tokens} - the amount can range from
	\begin{itemize}
		\item \textbf{1} for a slightly less punishing experience, over
		\item \textbf{2} for heroic protagonists, to
		\item \textbf{4} for an absolute cakewalk.
	\end{itemize}
	Once used they are lost and can only be restored by performing heroic acts, taking the key role in the players' immaculate plan, finishing their character arc or other such occasions.

	\pagebreak
	\section{Uses}
	\emph{Resilience tokens} can be used as follows:
	\par
	\begin{tabularx}{\columnwidth}{rX}
		1 token & When the character takes a hit, he takes no damage from said hit. \\
		1 token & When the character dies, he is stable but comatose instead. It is up to GM discretion how long it takes for him to regain consciousness. \\
		1 token & The character automatically passes a Restraint test to suppress all deterioration as a free action. \\
		2 tokens & The character becomes immune to pain, fear and getting stunned for the rest of the encounter.
	\end{tabularx}
	\par
	All of these are subject to GM discretion - he may exclude some options, add other ones or adjust the cost if the campaign in question deems that necessary.
\end{document}